### 2020-08-21 doc/paper.tex
doc initialized

\documentclass[runningheads,a4paper]{llncs}
% vim: tw=0 wm=0

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{bbm}
\usepackage{environ}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
%\usepackage{algorithmic}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
%\usepackage{enumite}
%\usepackage{cleveref}
%\usepackage{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
%\bibliographystyle{plainnat}
\usepackage{siunitx}
\usepackage{color}

\usepackage[draft,nomargin,inline]{fixme}
\fxsetface{inline}{\itshape}
\fxsetface{env}{\itshape}
%\fxuselayouts{margin}
%\fxuselayouts{inline}
\fxusetheme{color}

\usepackage{url}
\urldef{\mailsa}\path|{djukanovic, raidl}@ac.tuwien.ac.at,|
\urldef{\mailsb}\path|christian.blum@iiia.csic.es|
\newcommand{\keywords}[1]{\par\aDSvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\usepackage{tikz}
\usetikzlibrary{positioning}
\definecolor{canaryyellow}{rgb}{1.0, 0.94, 0.0}
\definecolor{brightgreen}{rgb}{0.4, 1.0, 0.0}
\definecolor{jazzberryjam}{rgb}{0.65, 0.04, 0.37}

%defining of command

\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}
\newcommand\str[1]{\texttt{#1}}
\newcommand\pL[1][]{\ensuremath{p^{\mathrm{L}#1}}}
\newcommand\pR[1][]{\ensuremath{p^{\mathrm{R}#1}}}
\newcommand\qL{\ensuremath{q^\mathrm{L}}}
\newcommand\qR{\ensuremath{q^\mathrm{R}}}
\newcommand\pLH{\ensuremath{\hat{p}^\mathrm{L}}}
\newcommand\pRH{\ensuremath{\hat{p}^\mathrm{R}}}
\newcommand{\Vext}{\ensuremath{V_\mathrm{{ext}}}}
\newcommand\UB{\ensuremath{\mathrm{UB}}}
\newcommand\Sigmand{\ensuremath{\Sigma^\mathrm{nd}}}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
\setlength{\leftmarginii}{1.8ex}
\raggedbottom
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}

% scaling factor for tables
\newcommand\tabscale{0.8}

\begin{document}

    %\setlength{\parindent}{0pt}  % disallow indentations
    %\numberwithin{table}{1}
    \mainmatter  % start of an individual contribution

    % first the title is needed
    \title{Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem}

    %
    \author{--}
    %

    \institute{%$^1$Institute of Logic and Computation, TU Wien,
    %Vienna, Austria,\\
    %	       $^2$ Artificial Intelligence Research Institute (IIIA-CSIC),\\ \normalsize Campus UAB, Bellaterra, Spain \\
    %\institute{Springer-Verlag, Computer Science Editorial,\\
    %Tiergartenstr. 17, 69121 Heidelberg, Germany\\
    %\mailsa\\
    %\mailsb\\
    %\mailsc\\
    %\url{http://www.springer.com/lncs}
    }

    \maketitle

    \section{Introduction}\label{sec:introduction}
     \emph{The Orthogonal Art Gallery Problem} (OAGP) is one of many variants of Art Gallery Problem (AGP). AGP asks for a set of points $G$ of minimal cardinality on some polygon $P$ such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.  Set $P$ is called guard set of $P$, and the points from $G$ as guards. The orthogonal AGP consider on arbitrary polygon but whose angles are $90^{\deg}$ and $270^{\deg}$. This problem is stated by Victor  Klee in 1973.~\cite{o1987art}. The problem is motivated from installing the cameras in a building (or gallery) such that a maximal surface is covered (possibly all areas are covered). Orthogonality comes that most of the walls are orthogonal to some other in a building. A variant of the OAGP for which we are interested in this studies allows only that guards are positioned at the edges of polygon $P$. It is known to be NP--hard~\cite{devadoss2011discrete}.

     Since then, many approaches have been proposed to solve the problem.
     \fxnote{TODO: work on literature approaches}
     \section{Preliminaries}

     \section{Algorithmic Approaches}

     \section{Computational Results}

     \section{Conclusions and Future Work}

    \bibliographystyle{abbrv}
    \bibliography{bib}

\end{document}

### 2020-08-24 doc/paper.tex
paper exapdend

@@
 It is known to be NP--hard~\cite{devadoss2011discrete}.
+Let su denote set $V$ as a set of all vertices of polygon $P$.
 
@@
      \section{Preliminaries}
+     Solvers which are able to solve MIP modelf for OAGP problem are one of the most efficient techniques to approach this problem.
+It is known that the problem is related to the known Minimal-Set-Cover (MSC) problem.
+
+     Let us suppose we are given a discretization $D(P)$ of the polygon $P$ (with a family of rectangles). Then we relate the OAGP with the known MSC problem.  
+     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $p_i$.
+Note that set $S_i$ includes a point $p_i$ but can also include some other guard $p_j$, $i \neq j$.
+So, the task of OAPG becomes in finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
+     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ Since the Integer Programming model for the Set Cover problem is know, it follows that 
+     \begin{align}
+        &\sum_{i=1}^n x_i \longrightarrow \min \\
+        &\mbox{s.t.} \\
+        &\sum_{j} a_{ij}x_j \geq 1\ (\forall p_i,1,...,n) \label{eq:const-3}\\
+        & x_j \in \{0,1\},  \in V,
+     \end{align}
+     where 
+     $a_{ij} = \begin{cases}
+          1, j \in V(j), \\
+          0, \mbox{otherwise} 
+     \end{cases}$ 
+     and $x_i = \begin{cases}
+     	 1, \mbox{ if } p_i \in \mathcal{C},\\
+     	 0, \mbox{otherwise},
+     \end{cases}$ \\
+      is a MIP model to solve OAGP. 
+     $V(j)$ is a set of all points from $D(P)$ that are visible from vertex $p_j$. Set $Z = \{j \in V\mid x_i=1\}$
+     Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
+
+     If we want to add weights into the OAGP problem such that all guard have no equal weight (of 1), we obtained the WOAGP problem.
+This can be augmented that the prices of cameras do not need to be equal.
+Let us suppose that for any guard $p_i$ we assign a price $w_i$, $i=1,...,n$.
+Then, the above model is trivially extended to the weighted version where only the objective function has to be changed to
+     $$ \sum_{i} x_i w_i,$$
+      and all other constraints remain the same.
 

### 2020-08-24 doc/paper.tex
todo added
comments

@@
 
-     If we want to add weights into the OAGP problem such that all guard have no equal weight (of 1), we obtained the WOAGP problem.
+     If we want to add weights into the OAGP problem such that all guard have no equal weight (of 1), we obtained the weighted variant of OAGP, that is the WOAGP problem.
 This can be augmented that the prices of cameras do not need to be equal.
@@
       and all other constraints remain the same.
-
-     \section{Algorithmic Approaches}
+      \fxnote{We should think about adding ranges for cameras?
+MDJ: Mislim da ovo ne utice na algoritme, jer bi se u svakom slucaju skupovi $S_i$ dobili u pre-procesing koraku bez obzira postojao ili ne domen vidljivosti kamere.
+Da li se slazete?
+}
+     \section{Algorithmic Approaches for WOAGP}
 

### 2020-08-25 doc/paper.tex
greedy heuristic proposed

@@
 }
+      In order to solve this model, we used general purpose solver \textsc{Cplex}. 
      \section{Algorithmic Approaches for WOAGP}
+          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to so solve WSCP is an enhanced greedy heuristic, our idea is to apply greedy algorithms to solve WOAGP.
+These algorithms produce a solution of reasonable quality within a short interval of time.
+Efficient of greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, that is partial) solution to complete one.
+Among all candidates ( solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value etc.
+until the solution is complete (i.e., cover all regions of the polygon).
+          Pseudocode of Greedy heuristic is given in Algorithm~\ref{alg:greedy}
 
+          \begin{algorithm}[!t] 
+          	\caption{Greedy Heuristic}\label{alg:greedy}
+          	\begin{algorithmic}[1]
+          		\State \textbf{Input:} an instance of a problem
+          		\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
+          		\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
+          		\While{$\text{Extend}(s^{P}) \neq \emptyset$}
+          		\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
+          		\State Extend $s^{P}$ by $e$
+          		\EndWhile
+          	\end{algorithmic}
+          \end{algorithm}
+      \subsection{Greedy Heuristic based on Price-per-Unit}
+       Our greedy criterion to expand current partial solution $s^P$  is based on the WOAGP characteristics, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$.
+For each not yet considered guards $p_i$, we assign the region he is able to see by $S_{p_i}$.
+As the next candidate to extend $s^P$, we choose not-yet-considered guard $p^*$ which is able to cover his part $S_{p_i}$ by smallest price per unit, among the other not considered guards.
+More precisely, greedy criterion $g$ is given as:
+       \begin{align}
+            g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
+       \end{align}
+       and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
+       Afterwards the region $S_{p^*}$ is further then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and update $s^p= s^p \cup \{p^*\}$.
+These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (it is covered by the guards from $s^P$).
+        \subsection{An Alternative Greedy Heuristic}
+        \fxnote{TODO}
      \section{Computational Results}

### 2020-08-25 doc/paper.tex
some fixes

@@
      Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $p_i$.
-Note that set $S_i$ includes a point $p_i$ but can also include some other guard $p_j$, $i \neq j$.
-So, the task of OAPG becomes in finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
+Note that set $S_i$ includes a point $p_i$ which can also include some other guard $p_j$, $i \neq j$.
+So, the task of OAPG becomes finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
      $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ Since the Integer Programming model for the Set Cover problem is know, it follows that 
@@
         &\mbox{s.t.} \\
-        &\sum_{j} a_{ij}x_j \geq 1\ (\forall p_i,1,...,n) \label{eq:const-3}\\
-        & x_j \in \{0,1\},  \in V,
+        &\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
+        & x_j \in \{0,1\}, j \in V,
      \end{align}
@@
      $a_{ij} = \begin{cases}
-          1, j \in V(j), \\
+          1, p_i \in V(j), \\
           0, \mbox{otherwise} 
@@
      and $x_i = \begin{cases}
-     	 1, \mbox{ if } p_i \in \mathcal{C},\\
+     	 1, \mbox{ if } \mbox{ the point } i \in \mathcal{C},\\
      	 0, \mbox{otherwise},
      \end{cases}$ \\
-      is a MIP model to solve OAGP. 
+      is a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
      $V(j)$ is a set of all points from $D(P)$ that are visible from vertex $p_j$. Set $Z = \{j \in V\mid x_i=1\}$

### 2020-08-26 doc/paper.tex
minor fix
added fxnotes

@@
        Afterwards the region $S_{p^*}$ is further then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and update $s^p= s^p \cup \{p^*\}$.
-These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (it is covered by the guards from $s^P$).
+These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (polygon $P$ is covered by the guards from $s^P$).
         \subsection{An Alternative Greedy Heuristic}
-        \fxnote{TODO}
+        \fxnote{TODO: work in progress...} Greedy criterion: 
+          \begin{itemize}
+          	\item prefer those guards with a smaller cost $w_i$; 
+          	\item If there are more guards with the smallest cost, 
+          	prefer one with the largest $S_{p_i}$.
+          \end{itemize}
      \section{Computational Results}
-
+     \fxnote{to generate larger instances; practical instances...}
      \section{Conclusions and Future Work}

### 2020-08-26 doc/paper.tex
update from meeting on 26.8.2020

@@
 This problem is stated by Victor  Klee in 1973.~\cite{o1987art}.
-The problem is motivated from installing the cameras in a building (or gallery) such that a maximal surface is covered (possibly all areas are covered).
-Orthogonality comes that most of the walls are orthogonal to some other in a building.
+The problem is motivated from installing the cameras in a building (or gallery) such that the whole surface of the building is covered.
+Orthogonality comes out from the walls which are orthogonal to some other wall in a building.
 A variant of the OAGP for which we are interested in this studies allows only that guards are positioned at the edges of polygon $P$.
-It is known to be NP--hard~\cite{devadoss2011discrete}.
+This problem is known to be NP--hard~\cite{devadoss2011discrete}.
 Let su denote set $V$ as a set of all vertices of polygon $P$.
@@
      \section{Preliminaries}
-     Solvers which are able to solve MIP modelf for OAGP problem are one of the most efficient techniques to approach this problem.
+     Solvers which solves IP model for OAGP problem are one of the most efficient techniques to approach this problem.
 It is known that the problem is related to the known Minimal-Set-Cover (MSC) problem.
@@
      Let us suppose we are given a discretization $D(P)$ of the polygon $P$ (with a family of rectangles). Then we relate the OAGP with the known MSC problem.  
-     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $p_i$.
-Note that set $S_i$ includes a point $p_i$ which can also include some other guard $p_j$, $i \neq j$.
+     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $i\in V$.
+Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $j\in V$, $i \neq j$.
 So, the task of OAPG becomes finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
-     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ Since the Integer Programming model for the Set Cover problem is know, it follows that 
+     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ The Integer Programming model for the Set Cover problem is known, and is as follows: 
      \begin{align}
@@
      \end{cases}$ \\
-      is a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
-     $V(j)$ is a set of all points from $D(P)$ that are visible from vertex $p_j$. Set $Z = \{j \in V\mid x_i=1\}$
+      presents a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
+     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem. 
      Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
@@
      If we want to add weights into the OAGP problem such that all guard have no equal weight (of 1), we obtained the weighted variant of OAGP, that is the WOAGP problem.
-This can be augmented that the prices of cameras do not need to be equal.
+This can be augmented that the prices of cameras do not need to be equal and these prices might be different due to the quality (of the range) of the cameras that are installed at some specific corners.
 Let us suppose that for any guard $p_i$ we assign a price $w_i$, $i=1,...,n$.
-Then, the above model is trivially extended to the weighted version where only the objective function has to be changed to
+Then, the above model is may be extended to its weighted version where the objective function has to be replaced by
      $$ \sum_{i} x_i w_i,$$
       and all other constraints remain the same.
-      \fxnote{We should think about adding ranges for cameras?
-MDJ: Mislim da ovo ne utice na algoritme, jer bi se u svakom slucaju skupovi $S_i$ dobili u pre-procesing koraku bez obzira postojao ili ne domen vidljivosti kamere.
-Da li se slazete?
-}
-      In order to solve this model, we used general purpose solver \textsc{Cplex}. 
+
+      In order to solve this model, we propose to use a general purpose solver \textsc{Cplex}. 
      \section{Algorithmic Approaches for WOAGP}
-          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to so solve WSCP is an enhanced greedy heuristic, our idea is to apply greedy algorithms to solve WOAGP.
+          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to apply greedy algorithms to solve WOAGP.
 These algorithms produce a solution of reasonable quality within a short interval of time.
@@
      \section{Computational Results}
-     \fxnote{to generate larger instances; practical instances...}
+       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
+       \begin{itemize}
+       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{1, n/8\}$ as its weight;
+       	  \item \emph{topological-type benchmarks}.
+For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$.
+Then, $w_i := \frac{l_i + l_{i+1}}{2}$.
+This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$.
+This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
+       	  \item    ...
+       \end{itemize}
      \section{Conclusions and Future Work}

### 2020-08-26 doc/paper.tex
update

@@
           \end{itemize}
+      \subsection{An improvement of Greedy Solution}
+      Local search and Large Neighborhood search \fxnote{TODO...}
      \section{Computational Results}
@@
        \begin{itemize}
-       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{1, n/8\}$ as its weight;
+       	  \item \emph{random benchmarks}.
+For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK?
+} as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
        	  \item \emph{topological-type benchmarks}.

### 2020-08-27 doc/paper.tex
Dragan dodao prijedlog za greedy

@@
           \end{itemize}
+		\fxnote{TODO: work in progress...} Another approach DRAGAN:
+           \begin{itemize}
+			\item introduce a penalty function
+          	\item introduce a term ``incorrect vertex''. A vertex is incorrect if it is not covered by any guard.
+			\item let $incorrect_{total}$ be the total number of incorrect vertices
+			\item let $w_{total}$ be the total sum of all weights among all verteces
+			\item involve the penalty function in the objective function
+				$$obj = \sum_{i \in Sol.} w_i+ incorrect_{total}$$ or
+				$$obj = \frac{\sum_{i \in Sol.} w_i}{w_{total}}+ incorrect_{total}$$
+			\item start Greedy with empty solution
+			\item in each iteration add such a vertex for which the obj value is minimal
+			\item end when $incorrect_{total}$ becomes 0
+          \end{itemize}
       \subsection{An improvement of Greedy Solution}

### 2020-08-27 doc/paper.tex
changes

@@
 			\item introduce a penalty function
-          	\item introduce a term ``incorrect vertex''. A vertex is incorrect if it is not covered by any guard.
-			\item let $incorrect_{total}$ be the total number of incorrect vertices
+          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
+			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
 			\item let $w_{total}$ be the total sum of all weights among all verteces
@@
 			\item start Greedy with empty solution
-			\item in each iteration add such a vertex for which the obj value is minimal
+			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
 			\item end when $incorrect_{total}$ becomes 0

### 2020-08-27 doc/paper.tex
changes
dalje ideje

--- 2020-08-26 doc/paper.tex
@@
           \end{itemize}
+		\fxnote{TODO: work in progress...} Another approach DRAGAN:
+           \begin{itemize}
+			\item introduce a penalty function
+          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
+			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
+			\item let $w_{total}$ be the total sum of all weights among all verteces
+			\item involve the penalty function in the objective function
+				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
+				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
+			\item start Greedy with empty solution
+			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
+			\item end when $incorrect_{total}$ becomes 0
+          \end{itemize}
       \subsection{An improvement of Greedy Solution}
       Local search and Large Neighborhood search \fxnote{TODO...}
+      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards. 
+      The first configuration of neighbourhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t.
+value $obj(;)$.
+
+      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$.
+Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$.
      \section{Computational Results}

### 2020-08-29 doc/software/cplex_lcis1.cpp
model 1 implemented in CPLEX + reading instances random + added weights in the program

@@ -1,0 +1,593 @@
+/* the CPLEX modes for a specific 2-LCIPS problem */
+/* before compilation makes sure that CPLEX software path is correct */
+
+#ifdef HAVE_CONFIG_H
+#include <config.h>
+#endif
+#include "Timer.h"
+#include <vector>
+#include <string>
+#include <stdio.h>
+#include <stdlib.h>
+#include <iostream>
+#include <string.h>
+#include <fstream>
+#include <sstream>
+#include <cmath>
+#include <cstdlib>
+#include <cstring>
+#include <sstream>
+#include <vector>
+#include <set>
+#include <limits>
+#include <unordered_map>
+#include <map>
+
+// the following "include" is necessary for the correct working/compilation of CPLEX. You should adapt this path to your installation of CPLEX
+#include "/home/djukanovic/Desktop/projects/LCAPS_software/cplex-12.5/include/ilcplex/ilocplex.h"
+
+ILOSTLBEGIN
+
+// global variables concerning the random number generator
+time_t t;
+
+// vector for keeping the names of the input files
+vector<string> inputFile;  
+int iter = 0; 
+int line_number = 0;
+int sigma = 0;
+int alg = 0; // type of the algorithm (0: MIP; 1: DP)
+// time limit for CPLEX (can be changed at run time via the -t comand line parameter)
+double time_limit = 900.0;
+string outdir="/home/djukanovic/Desktop/projects/rflcsp/MIP-RFLCS-2d/CP-instances/"; // the directory where .out files will be saved
+
+/** preprocessing structures **/
+int n_len; int n_of_sequences; int alphabet_size = 0; // lenght of the largest input string
+std::vector<std::vector<std::vector<int16_t>>> occurance_positions; ///< structure for reading the number of occurrences of letter <a> of some string i<=m, starting from pl to the end of string
+std::vector<std::vector<int16_t>> M;
+std::vector<std::vector<int16_t>> M_revs;
+int primal_sol = 20;
+int primal_sol_time = 0; // time of BS execution
+
+/* two input strings */
+int m = 2; // number of strings in input
+vector<int> s1;
+vector<int> s2; 
+
+
+
+// structures for keys of Hash-mapwhich will store binary variables of the 2-LCPS model
+
[…]

### 2020-08-29 doc/software/cplex_woagp.cpp

@@ -1,0 +1,257 @@
+/* the CPLEX modes for a specific 2-LCIPS problem */
+/* before compilation makes sure that CPLEX software path is correct */
+
+#ifdef HAVE_CONFIG_H
+#include <config.h>
+#endif
+#include "Timer.h"
+#include <vector>
+#include <string>
+#include <stdio.h>
+#include <stdlib.h>
+#include <iostream>
+#include <string.h>
+#include <fstream>
+#include <sstream>
+#include <cmath>
+#include <cstdlib>
+#include <cstring>
+#include <sstream>
+#include <vector>
+#include <set>
+#include <limits>
+#include <unordered_map>
+#include <map>
+
+// the following "include" is necessary for the correct working/compilation of CPLEX. You should adapt this path to your installation of CPLEX
+#include "/home/djukanovic/Desktop/projects/LCAPS_software/cplex-12.5/include/ilcplex/ilocplex.h"
+
+ILOSTLBEGIN
+
+// global variables concerning the random number generator
+time_t t;
+
+// vector for keeping the names of the input files
+vector<string> inputFile;
+int sigma = 0;
+// time limit for CPLEX (can be changed at run time via the -t comand line parameter)
+double time_limit = 900.0;
+string outdir="/home/djukanovic/Desktop/projects/rflcsp/MIP-RFLCS-2d/CP-instances/"; // the directory where .out files will be saved
+int m = 0; // number of sets
+int n = 0; // cardnality of X, i.e., |X|
+
+inline int stoi(string &s) {
+
+       return atoi(s.c_str());
+}
+
+inline double stof(string &s) {
+
+       return atof(s.c_str());
+}
+
+void read_parameters(int argc, char **argv) {
+
+    int iarg = 1;
+
+    while (iarg < argc) {
+        if (strcmp(argv[iarg],"-i")==0) inputFile.push_back(argv[++iarg]);
+        else if (strcmp(argv[iarg],"-t")==0) time_limit = atof(argv[++iarg]);
+        iarg++;
+    }
+}
+
+// write during the CPLEX call
+ILOMIPINFOCALLBACK6(loggingCallback,
+                    Timer&, timer,
+                    vector<double>&, times,
+                    vector<double>&, results,
+                    vector<double>&, gaps,
+                    int, iter,
+                    IloNum,         lastIncumbent) {
+
+    IloNum nv = getIncumbentObjValue();
+    double newTime = timer.elapsed_time(Timer::VIRTUAL);
+    double newGap = 100.0*getMIPRelativeGap();
[…]

### 2020-08-29 doc/software/cplex_woagp.cpp
Greedy for MSC problem

@@ -26,6 +26,8 @@
 // the following "include" is necessary for the correct working/compilation of CPLEX. You should adapt this path to your installation of CPLEX
 #include "/home/djukanovic/Desktop/projects/LCAPS_software/cplex-12.5/include/ilcplex/ilocplex.h"
 
+using namespace std; 
+
 ILOSTLBEGIN
 
 // global variables concerning the random number generator
@@ -82,6 +84,106 @@ ILOMIPINFOCALLBACK6(loggingCallback,
     lastIncumbent = nv;
 }
 
+int f(vector<set<int>>& C)
+{
+       std::set<int> d;
+       for(set<int> di : C){
+     
+           for (int dii: di){
+               //cout << "dii" << dii << endl;
+               d.insert(dii);
+           }
+        
+       }
+       //cout <<"D" << d.size() << endl; 
+       //for(int diii: d)
+       //  cout << diii << "\t" <<endl;
+
+       return (int)d.size();
+}
+
+int f_minus(vector<set<int>>& C, set<int>& ss ) // f(C u {s}) - f(S)
+{
+    int count = 0; // ako i \in ss nije niti u jednom od skupova u S, onda count++;
+    if(C.empty())
+       return ss.size();
+
+    for(int i: ss) 
+    {
+        bool presented = false;
+        for(set<int>& di : C){
+            if(di.count(i) > 0){
+               presented = true;
+               break; 
+            }
+        }
+        if(presented) 
+           count++;
+    }
+    return ss.size() - count; 
+}
+
+float greedy_criterion(vector<int>& Cost, vector<set<int>>& S, int i, vector<set<int>>& C) // take s_i from S
+{     
+    set<int> s = S[i];
+    int f_m = f_minus(C, s);  //cout << "f_m: " << f_m << endl;
+    if(f_m == 0)
+       return 100000;
+
+    float val = ((float)Cost[i]) / (f_minus(C, s));     //cout << "val: " << val << endl; 
+    return val;
+}
+
+bool findA(vector<int>& s, int a)
+{
+
+     for(int si : s)
+         if(si == a)
+            return true;
+
+      return false;  
+}
+
+int min_greedy(vector<int>& Cost, vector<set<int>>& S, vector<set<int>>& C, vector<int>& indeks)
+{         //cout << "min_greedy" << endl;
+          float g_m = 10000000; int dodaj;
[…]

### 2020-08-30 doc/software/cplex_woagp.cpp
parametri programa + ReadMe

@@ -41,6 +41,7 @@ double time_limit = 900.0;
 string outdir="/home/djukanovic/Desktop/projects/rflcsp/MIP-RFLCS-2d/CP-instances/"; // the directory where .out files will be saved
 int m = 0; // number of sets
 int n = 0; // cardnality of X, i.e., |X|
+int alg = 0; // koji algoritam pozivamo 0: CPLEX (WSC); 1: Greedy (WSC)
 
 inline int stoi(string &s) {
 
@@ -59,6 +60,7 @@ void read_parameters(int argc, char **argv) {
     while (iarg < argc) {
         if (strcmp(argv[iarg],"-i")==0) inputFile.push_back(argv[++iarg]);
         else if (strcmp(argv[iarg],"-t")==0) time_limit = atof(argv[++iarg]);
+        else if (strcmp(argv[iarg],"-alg")==0) alg = atof(argv[++iarg]);
         iarg++;
     }
 }
@@ -76,7 +78,7 @@ ILOMIPINFOCALLBACK6(loggingCallback,
     double newTime = timer.elapsed_time(Timer::VIRTUAL);
     double newGap = 100.0*getMIPRelativeGap();
     if (nv < lastIncumbent) {
-        cout << "value " << nv << "\ttime " << newTime <<  "\tgap " << newGap << endl;
+        cout << "CPLEX sol: " << nv << "\ttime " << newTime <<  "\tgap " << newGap << endl;
         results[iter] = nv;
         times[iter] = newTime;
         gaps[iter] = newGap;
@@ -170,7 +172,7 @@ float greedy_procedure(vector<set<int>>& S, vector<int>& Cost)
            int index_set = min_greedy( Cost, S, C, indeks);  
            
            if(!findA(indeks, index_set)){ //jos nije dodan
-               C.push_back(S[index_set]);cout << "dodaj----> " << index_set << endl;
+               C.push_back(S[index_set]);cout << "dodaj ----> " << index_set << endl;
               indeks.push_back(index_set);
            } 
            f_C = f(C); 
@@ -234,7 +236,7 @@ void run_cplex(vector<int>& C, vector<set<int>>& S){
    // tell CPLEX to make use of the function 'loggingCallback' for writing out information to the screen
    //cplex.use(loggingCallback(env, timer, times, results, gaps, iter, lastObjVal));
    cout << "CPLEX pokrenut" << endl;
-   cplex.exportModel("ws.lp");
+   // cplex.exportModel("ws.lp");
    cplex.solve();
   
[…]

### 2020-08-30 doc/paper.tex
LS pseudocode added

@@
 Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$.
+
+       \begin{algorithm}[!t] 
+      	\caption{Local Search}\label{alg:local-search}
+      	\begin{algorithmic}[1]
+      		\State \textbf{Input:} a (partial) solution $s_{greedy}=\{v_1,...,v_k\}$, $iter_{allow}>0.$
+      		\State \textbf{Output:} and improved solution $s$
+      		\While{$iter < iter_{allow}$}
+      		     \State $D(P)_s$ the number of points covered by $s_{greedy}$
+      		      \If{$|D(P)_s| == |D(P)|$} // a complete solution 
+      		          \State return $s_{greedy}$
+      		      \EndIf
+      		     \State choose random vertex $v_{i'}$ from $s_{greedy}$
+      		     \State $v_{i''} \gets$ consider neighbor vertices of vertex  $v_{i'}$ (two are possible) and choose one of them
+      		     \State $s^1_{greedy} \gets$ $s_{greedy} \cup \{v_{i''} \} \setminus \{v_{i'}\}$
+      		      \If{$s_{greedy}$ do not improve  $D(P)_s$}
+      		           \State $v_{i'''} \gets$ take the second neighbor vertex of $v_{i'}$
+      		           \State $s^2_{greedy} \gets$ swap $v_{i'''}$ with  $v_{v'}$ in  $s_{greedy}$
+      		           \If{$s^2_{greedy}$ do not improve $D(P)_s$}
+      		                  \If{$s^1_{greedy} \vee s^2_{greedy}$ cover the same number of points as $D(P)_s$}
+      		                     \State with random probability  0.5, choose the right for a new $s_{greedy}$
+      		                \Else
+
+      		                     \State \emph{goto} line 4
+      		                \EndIf
+      		           \EndIf
+      		      \EndIf
+
+      		     \State $iter \gets iter +1 $
+      		\EndWhile
+      	\end{algorithmic}
+      \end{algorithm}
+
      \section{Computational Results}

### 2020-08-31 doc/paper.tex
LS pseudocode: error fix
LS pseudocode: completed
pseudocode update
dopunjen LS
hyrid added

--- 2020-08-27 doc/paper.tex
@@
       Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$.
-Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$.
+Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.
+
+      \subsection{Hybrid of the Greed Heuristic and Local Search}
+
+       In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method. 
+       The pseudocode is given in Algorithm~\ref{alg: hybrid-ls-greedy}.
+        \begin{algorithm}[!t]
+       	\caption{Local Search}\label{alg:hybrid-ls-greedy}
+       	\begin{algorithmic}
+       		   	\State \textbf{Input:} and Instance of the problem; $pct$:percentage
+       		    \State \textbf{Output:} a complete solution $s$
+       		    \State $s_{greedy} \gets \emptyset$
+       		    \While{ $s_{greedy}$ is not complete}
+       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot p \rfloor$ guards 
+       		        \State $s_{greedy} \gets$ LS($s^P$)
+       		    \EndWhile
+       \end{algorithmic}
+       \end{algorithm}
+
+       \begin{algorithm}[!t]
+      	\caption{Local Search}\label{alg:local-search}
+      	\begin{algorithmic}[1]
+      		\State \textbf{Input:} a (partial) solution $s_{greedy}=\{v_1,...,v_k\}$, $iter_{allow}>0., $ probability $p$ 
+      		\State \textbf{Output:} and improved solution $s$
+      		\While{$iter < iter_{allow}$}
+      		     \State $D(P)_s$ the number of points covered by $s_{greedy}$
+      		      \If{$|D(P)_s| == |D(P)|$} // a complete solution
+      		          \State return $s_{greedy}$
+      		      \EndIf
+      		     \State choose random vertex $v_{i'}$ from $s_{greedy}$
+      		     \State $v_{i''},v_{i'''} \gets$ two neighbor vertices of vertex  $v_{i'}$
+      		     \State $s^1_{greedy} \gets$ $s_{greedy} \cup \{v_{i''} \} \setminus \{v_{i'}\}$
+                 \State $s^2_{greedy} \gets$ $s_{greedy} \cup \{v_{i'''} \} \setminus \{v_{i'}\}$
+      		      \If{$|D(P)_{s^1_{greedy}}|>|D(P)_{s_{greedy}}|$ }
+                        \State $s_{greedy} \gets s^1_{greedy}$
+      \EndIf
+                    \If {$|D(P)_{s^1_{greedy}}|==|D(P)_{s_{greedy}}|$ }
+                        \State $s_{greedy} \gets s^1_{greedy}$ with probability $p$
+
+      		      \EndIf     
+      		       \If{$|D(P)_{s^2_{greedy}}|>|D(P)_{s_{greedy}}|$ }
+                        \State $s_{greedy} \gets s^2_{greedy}$
+      		      \EndIf
+
+            \If {$|D(P)_{s^2_{greedy}}|==|D(P)_{s_{greedy}}|$ }
+                        \State $s_{greedy} \gets s^2_{greedy}$ with probability $p$
+                    \EndIf
+      		     \State $iter \gets iter +1 $
+      		\EndWhile
+      		 \State return $s_{greedy}$
+      	\end{algorithmic}
+      \end{algorithm}
+
      \section{Computational Results}

### 2020-08-31 doc/paper.tex
minor fix

@@
         \begin{algorithm}[!t]
-       	\caption{Local Search}\label{alg:hybrid-ls-greedy}
+       	\caption{Local Search + Greedy}\label{alg:hybrid-ls-greedy}
        	\begin{algorithmic}
-       		   	\State \textbf{Input:} and Instance of the problem; $pct$:percentage
+       		   	\State \textbf{Input:} and Instance of the problem; $pct\in (0,1)$:percentage
        		    \State \textbf{Output:} a complete solution $s$
@@
        		    \While{ $s_{greedy}$ is not complete}
-       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot p \rfloor$ guards 
+       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot pct \rfloor$ guards 
        		        \State $s_{greedy} \gets$ LS($s^P$)

### 2020-08-31 doc/paper.tex
best WMCS problem greedy added

@@
 These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (polygon $P$ is covered by the guards from $s^P$).
+
+       The best WSC problem greedy heuristic known from the literature was based on the following greedy heuristic:
+       \begin{align}
+          g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
+       \end{align} 
+      where $f(s^p) = |\bigcup_{s \in s^p} s |$.
         \subsection{An Alternative Greedy Heuristic}
@@
        In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method. 
-       The pseudocode is given in Algorithm~\ref{alg: hybrid-ls-greedy}.
+       The pseudocode is given in Algorithm~\ref{alg:hybrid-ls-greedy}.
         \begin{algorithm}[!t]
@@
        		    \While{ $s_{greedy}$ is not complete}
-       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot pct \rfloor$ guards 
-       		        \State $s_{greedy} \gets$ LS($s^P$)
+       		        \State $s_{greedy} \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot pct \rfloor$ guards 
+       		        \State $s_{greedy} \gets$ LS($s_{greedy}$)
        		    \EndWhile

### 2020-09-02 doc/paper.tex
new ideas for g-function included

@@
       where $f(s^p) = |\bigcup_{s \in s^p} s |$.
+
+      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
+      and the other sets $S_{p_j}$, $j \neq i$ as follow:
+      \begin{align}\label{eq:intersection-heuristic}
+      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
+      \end{align}
+      where $|S_{p_i} \cap S_{p_j}|$ denotes the surface (in some unit) of the intersection of the two 
+      visible regions.
+If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard.
+So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc.
+to formula~(\ref{eq:intersection-heuristic})
+
         \subsection{An Alternative Greedy Heuristic}

### 2020-09-02 doc/paper.tex
Dodat pocetak literature

--- 2020-08-31 doc/paper.tex
@@
 AGP asks for a set of points $G$ of minimal cardinality on some polygon $P$ such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
-Set $P$ is called guard set of $P$, and the points from $G$ as guards.
-The orthogonal AGP consider on arbitrary polygon but whose angles are $90^{\deg}$ and $270^{\deg}$.
-This problem is stated by Victor  Klee in 1973.~\cite{o1987art}.
+Set $G$ is called guard set of $P$ and the points from $G$ as guards.
+The orthogonal AGP consider on arbitrary polygon but whose angles are $90^{\circ}$ and $270^{\circ}$.
+This problem was stated by Victor  Klee in 1973.~\cite{o1987art}.
 The problem is motivated from installing the cameras in a building (or gallery) such that the whole surface of the building is covered.
-Orthogonality comes out from the walls which are orthogonal to some other wall in a building.
-A variant of the OAGP for which we are interested in this studies allows only that guards are positioned at the edges of polygon $P$.
-This problem is known to be NP--hard~\cite{devadoss2011discrete}.
-Let su denote set $V$ as a set of all vertices of polygon $P$.
+Orthogonality constraint naturally comes out from the orthogonality of the walls in a building.
 
-     Since then, many approaches have been proposed to solve the problem.
+     Kahn et al.
+in ~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.
+A variant of the OAGP for which we are interested in this study allows only that guards are positioned at the vertices of polygon $P$.
+Actually, we are looking for minimum vertex guards needed to cover an orthogonal polygon.
+This problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.
+
+     By discretization $D(P)$ the set of points of the polygon $P$, the art gallery problem can be reduced to the well-known Min Set Cover Problem.
+For each vertex of the polygon $P$, a set of points of visibility is determined.
+On that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets.
+
+     In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal, is presented for simple polygon with $n$ vertices.
+Firstly, this algorithm partition the polygonal region into convex components and construct sets consisting of these convex components.
+After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the Minimum set-covering problem (MSC) is applied to get solution.
+
+     An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in ~\cite{tomas2003approximation}.
+A major idea of this approach is exploring dominance of visibility regions to first detect pieces that are
+more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
+
+Tozoni et a.
+~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact Integer linear programming  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
+
+More detailed overview of the results on art gallery problems is out the scope of this paper and can be found in a survey paper  ~\cite{ghosh2010approximation2}.
+
+    Couto et al.
+presented an exact and efficient algorithm for the Orthogonal Art Gallery Problem in ~\cite{couto2007exact}.
+The algorithm is divided into two phases.
+In the preprocessing phase an initial discretization is constructed and the Integer Programming model for solving MSC is applied.
+In the solution phase, the discretized instance is iteratively refined and solved, until the solution becomes viable.
+
      \fxnote{TODO: work on literature approaches}

### 2020-09-02 doc/paper.tex
udapte

--- 2020-09-02 doc/paper.tex
@@
       \end{align}
-      where $|S_{p_i} \cap S_{p_j}|$ denotes the surface (in some unit) of the intersection of the two 
+      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two 
       visible regions.
@@
 
+     \subsection{Beam Search (BS)}
+        BS is an incomplete BFS heuristic search algorithm.
+
      \section{Computational Results}

### 2020-09-02 doc/paper.tex

--- 2020-09-02 doc/paper.tex
@@
       where $f(s^p) = |\bigcup_{s \in s^p} s |$.
+
+      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
+      and the other sets $S_{p_j}$, $j \neq i$ as follow:
+      \begin{align}\label{eq:intersection-heuristic}
+      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
+      \end{align}
+      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two 
+      visible regions.
+If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard.
+So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc.
+to formula~(\ref{eq:intersection-heuristic})
+
         \subsection{An Alternative Greedy Heuristic}

### 2020-09-04 doc/paper.tex
update

@@
      \subsection{Beam Search (BS)}
-        BS is an incomplete BFS heuristic search algorithm.
+        Beam Searxh is an incomplete BFS heuristic search algorithm.
+At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$.
+all nodes are then expanded in all possible ways.
+Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level.
+        The search is processed in the same manner until $B$ is empty.
+The main question concerns of the criterion of choosing the nodes for a beam.
+This is done by means of a heuristic evaluation of the nodes.
+The heuristic is a problem-specific aspect of each problem that has to be solved.
+\fxnote{work in progress...}
 

### 2020-09-05 doc/software/milan/pretprocesiranje.cpp
Add pretprocesiranje.cpp

@@ -1,0 +1,383 @@
+#include <CGAL/Exact_predicates_inexact_constructions_kernel.h>
+#include <CGAL/Polygon_2.h>
+#include <CGAL/Bbox_2.h>
+#include <CGAL/Exact_predicates_exact_constructions_kernel.h>
+#include <CGAL/Simple_polygon_visibility_2.h>
+#include <CGAL/Triangular_expansion_visibility_2.h>
+#include <CGAL/Arrangement_2.h>
+#include <CGAL/Arr_segment_traits_2.h>
+#include <CGAL/Arr_naive_point_location.h>
+#include <CGAL/Boolean_set_operations_2.h>
+#include <CGAL/General_polygon_set_2.h>
+#include <CGAL/Gps_segment_traits_2.h>
+#include <CGAL/centroid.h>
+#include <list>
+#include <minisat/core/Solver.h>
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <sstream>
+#include <chrono>
+#include <bits/stdc++.h>
+
+typedef CGAL::Exact_predicates_inexact_constructions_kernel             K;
+typedef CGAL::Polygon_2<K>                                              Polygon;
+typedef CGAL::Point_2<K>                                                Point;
+typedef CGAL::Exact_predicates_exact_constructions_kernel               Kernel;
+typedef Kernel::Point_2                                                 Point_2;
+typedef CGAL::Polygon_2<Kernel>                                         Polygon_2;
+typedef Kernel::Segment_2                                               Segment_2;
+typedef CGAL::Arr_segment_traits_2<Kernel>                              Traits_2;
+typedef CGAL::Arrangement_2<Traits_2>                                   Arrangement_2;
+typedef Arrangement_2::Edge_const_iterator                              Edge_const_iterator;
+typedef Arrangement_2::Halfedge_const_handle                            Halfedge_const_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef CGAL::Simple_polygon_visibility_2<Arrangement_2,CGAL::Tag_true> RSPV;
+typedef CGAL::Polygon_with_holes_2<Kernel>                              Polygon_with_holes_2;
[…]

### 2020-09-05 doc/software/milan/greedyLovasz.cpp
Add greedyLovasz.cpp and result for small polygons

@@ -1,0 +1,416 @@
+#include <CGAL/Exact_predicates_inexact_constructions_kernel.h>
+#include <CGAL/Polygon_2.h>
+#include <CGAL/Bbox_2.h>
+#include <CGAL/Exact_predicates_exact_constructions_kernel.h>
+#include <CGAL/Simple_polygon_visibility_2.h>
+#include <CGAL/Triangular_expansion_visibility_2.h>
+#include <CGAL/Arrangement_2.h>
+#include <CGAL/Arr_segment_traits_2.h>
+#include <CGAL/Arr_naive_point_location.h>
+#include <CGAL/Boolean_set_operations_2.h>
+#include <CGAL/General_polygon_set_2.h>
+#include <CGAL/Gps_segment_traits_2.h>
+#include <CGAL/centroid.h>
+#include <list>
+#include <minisat/core/Solver.h>
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <sstream>
+#include <chrono>
+#include <bits/stdc++.h>
+
+typedef CGAL::Exact_predicates_inexact_constructions_kernel             K;
+typedef CGAL::Polygon_2<K>                                              Polygon;
+typedef CGAL::Point_2<K>                                                Point;
+typedef CGAL::Exact_predicates_exact_constructions_kernel               Kernel;
+typedef Kernel::Point_2                                                 Point_2;
+typedef CGAL::Polygon_2<Kernel>                                         Polygon_2;
+typedef Kernel::Segment_2                                               Segment_2;
+typedef CGAL::Arr_segment_traits_2<Kernel>                              Traits_2;
+typedef CGAL::Arrangement_2<Traits_2>                                   Arrangement_2;
+typedef Arrangement_2::Edge_const_iterator                              Edge_const_iterator;
+typedef Arrangement_2::Halfedge_const_handle                            Halfedge_const_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef CGAL::Simple_polygon_visibility_2<Arrangement_2,CGAL::Tag_true> RSPV;
+typedef CGAL::Polygon_with_holes_2<Kernel>                              Polygon_with_holes_2;
+typedef std::list<Polygon_with_holes_2>                                 Pwh_list_2;
[…]

### 2020-09-06 doc/paper.tex
TODOs added

@@
       \end{algorithm}
+    \begin{comment}
 
@@
 This is done by means of a heuristic evaluation of the nodes.
-The heuristic is a problem-specific aspect of each problem that has to be solved.
+The heuristic is a problem-specific aspect of each problem that is considered for solving.
 \fxnote{work in progress...}
-
+    \end{comment}   
      \section{Computational Results}
@@
 } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
-       	  \item \emph{topological-type benchmarks}.
+       	  \item \emph{topologically-based benchmarks}.
 For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$.
@@
 This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
-       	  \item    ...
+       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon).
        \end{itemize}

### 2020-09-06 doc/software/milan/greedyLovasz.cpp

@@ -44,6 +44,12 @@ typedef CGAL::Triangular_expansion_visibility_2<Arrangement_2>          TEV;
 CGAL::Cartesian_converter<Kernel,K> converter; 
 CGAL::Cartesian_converter<K, Kernel> converter2; 
 
+/** pomocne strukture za gridi metod **/
+vector<float> Surface;
+vector<int> Cost;
+vector<vector<float>>Intersection;
+/** kraj pomocnih str. za gridi metode **/
+
 using namespace std;
 using namespace std::chrono;
 
@@ -300,7 +306,41 @@ int f_minus(vector<set<Point_2>>& C, set<Point_2>& ss ) // f(C u {s}) - f(S)
     return ss.size() - count; 
 }
 
-float greedy_criterion(vector<int>& Cost, vector<set<Point_2>>& S, int i, vector<set<Point_2>>& C) // take s_i from S
+/** 
+ parametar 
+ @i: Za i-tog cuvara (tacku poligona koja je ideksirana u preprocesingu), vraca povrsinu poligona koju ovaj poligon vidi 
+ 
+ TODO: Milane, za ovo je potrebno da mi pripremis je za i-ti cvor poligona povrsina koju on vidi, to mi vrati u vektor Surface[i] 
+*/
+float greedy_criterion1(int i)
+{
+
+    return Cost[i] / Surface[i];
+
+}
+
+/**   Gridi funkcija (6)  prema indeksiranju u radu
+TODO: Milane, Za svaka dva cuvara i,j, potrebna mi je struktura koja racuna povrsinu poligona koji je presjek poligona vidljivosti cvora i te poligona vidljivosti cvora j
+--> cuvaj ih po mogucnosti u nekoj matricnoj strukturi Intersection[i][j]
+
+Param:
+@i: indeks cvora za koji se racuna gridi vrijednost 
+@S: trenutni parcijalni skup 
+@n: broj tjemena
+ **/
+float greedy_criterion2(vector<set<Point_2>>& S, int i, int n)
+{
+      float num = 0.0;
+      int den = n - S.size();
+      for(int j = 0; j < n; ++j) {
+          if(S[j] != S[i]){
+             num += Intersection[ i ][ j ];
+          }
+      }
+      return num / den;
+}
+
+float greedy_criterion(vector<set<Point_2>>& S, int i, vector<set<Point_2>>& C) // take s_i from S
 {     
     set<Point_2> s = S[i];
[…]

### 2020-09-06 doc/software/milan/greedyLovasz.cpp
Add instances and results

@@ -44,14 +44,14 @@ typedef CGAL::Triangular_expansion_visibility_2<Arrangement_2>          TEV;
 CGAL::Cartesian_converter<Kernel,K> converter; 
 CGAL::Cartesian_converter<K, Kernel> converter2; 
 
+using namespace std;
+using namespace std::chrono;
+
 /** pomocne strukture za gridi metod **/
 vector<float> Surface;
 vector<int> Cost;
 vector<vector<float>>Intersection;
 /** kraj pomocnih str. za gridi metode **/
-
-using namespace std;
-using namespace std::chrono;
 
 vector<string> split(const string& str, const string& delim)
 {
@@ -265,6 +265,37 @@ void write_test(const string &filename, string &tekst)
   outfile << tekst; 
 }
 
+template<class Kernel, class Container>
+Traits_2::FT area_polygon_with_holes(const CGAL::Polygon_with_holes_2<Kernel, Container> & pwh)
+{
+  Traits_2::FT res = 0;
+  if (! pwh.is_unbounded()) {
+    res = pwh.outer_boundary().area();
+  } else
+    return res;
+
+  typename CGAL::Polygon_with_holes_2<Kernel,Container>::Hole_const_iterator hit;
+  unsigned int k = 1;
+  for (hit = pwh.holes_begin(); hit != pwh.holes_end(); ++hit, ++k) 
+    res -= (*hit).area();
+
+  return res;
+}
+
+Traits_2::FT area_set_polygons(Polygon_set_2 S)
+{
+  Traits_2::FT povrsina = 0;
+
+  std::list<Polygon_with_holes_2> res;
+  S.polygons_with_holes (std::back_inserter (res));
+
+  Pwh_list_2::const_iterator it_res;
+  for (it_res = res.begin(); it_res != res.end(); ++it_res) 
+    povrsina += area_polygon_with_holes(*it_res);
+      
+  return povrsina;
+}
+
 // Markove funkcije  -  malo modifikovano
 
 int f(vector<set<Point_2>> &C)
@@ -285,7 +316,7 @@ int f(vector<set<Point_2>> &C)
        return (int)d.size();
 }
 
-int f_minus(vector<set<Point_2>>& C, set<Point_2>& ss ) // f(C u {s}) - f(S)
+int f_minus(vector<set<Point_2>>& C, set<Point_2>& ss) // f(C u {s}) - f(S)
 {
[…]

### 2020-09-06 doc/software/milan/greedyLovasz.cpp
fix in greedy2 function

@@ -349,22 +349,27 @@ TODO: Milane, Za svaka dva cuvara i,j, potrebna mi je struktura koja racuna povr
 
 Param:
 @i: indeks cvora za koji se racuna gridi vrijednost 
-@S: trenutni parcijalni skup 
-@n: broj tjemena
+@indeks: trenutni parcijalni skup  --> samo indeksi skupova uzeti radi optimizacije
+@S: skup svih tjemena
  **/
 
-float greedy_criterion2(vector<set<Point_2>>& S, int i, int n)
+float greedy_criterion2(vector<set<Point_2>>& S, vector<int>& indeks, int i)   //vector<set<Point_2>>& C, int i)
 {
       float num = 0.0;
-      int den = n;// - S.size();
-      for(int j = 0; j < n; ++j) {
-          if(S[j] != S[i]){
-             num += Intersection[i][j];
-          }
+      int den = S.size() - indeks.size();
+      for(int j = 0; j < S.size(); ++j) {
+          if( S[j] != S[i] and  std::find(indeks.begin(), indeks.end(), j) == indeks.end()) ){ // S_j ne smije biti u vec dodanom parcijalnom skupu 
+              num += Intersection[i][j];
+          } 
       }
       return num / den;
 }
-
+/**
+param:
+@S: skup svih skupova (instance) 
+@C: parcijalno rjesenje (trenutno) 
+@i: index skupa S_i koji se razmatra za dodavanje u parcijalni skup @C
+**/
 float greedy_criterion(vector<set<Point_2>>& S, int i, vector<set<Point_2>>& C) // take s_i from S
 {     
     set<Point_2> s = S[i];
@@ -393,7 +398,7 @@ int min_greedy(vector<set<Point_2>>& S, vector<set<Point_2>>& C, vector<int>& in
           {  // cout << "i " << i << endl;
               //float g_mi = greedy_criterion(S, i, C); //cout << "gmi: " << g_mi << endl;
               //float g_mi = greedy_criterion1(i);
-              float g_mi = greedy_criterion2(S,i,S.size());
+              float g_mi = greedy_criterion2(S, indeks, i);
               if(g_mi < g_m and g_mi != 100000 and !findA(indeks, i)) 
               { 
                  dodaj = i;

### 2020-09-06 doc/software/milan/greedyLovasz.cpp
new resultat

@@ -358,7 +358,8 @@ float greedy_criterion2(vector<set<Point_2>>& S, vector<int>& indeks, int i)   /
       float num = 0.0;
       int den = S.size() - indeks.size();
       for(int j = 0; j < S.size(); ++j) {
-          if( S[j] != S[i] and  std::find(indeks.begin(), indeks.end(), j) == indeks.end()) ){ // S_j ne smije biti u vec dodanom parcijalnom skupu 
+          if(S[j] != S[i] &&  std::find(indeks.begin(), indeks.end(), j) == indeks.end())
+          { // S_j ne smije biti u vec dodanom parcijalnom skupu 
               num += Intersection[i][j];
           } 
       }

### 2020-09-06 doc/software/milan/greedyLovasz.cpp
another fix

@@ -51,6 +51,8 @@ using namespace std::chrono;
 vector<float> Surface;
 vector<int> Cost;
 vector<vector<float>>Intersection;
+#define INFEASIBLE 100000;
+
 /** kraj pomocnih str. za gridi metode **/
 
 vector<string> split(const string& str, const string& delim)
@@ -355,6 +357,9 @@ Param:
 
 float greedy_criterion2(vector<set<Point_2>>& S, vector<int>& indeks, int i)   //vector<set<Point_2>>& C, int i)
 {
+      if(std::find(indeks.begin(), indeks.end(), i) != indeks.end() ) // i vec u skupu indeks koji odg. parcijalnom rjesenju...
+         return INFEASIBLE;
+ 
       float num = 0.0;
       int den = S.size() - indeks.size();
       for(int j = 0; j < S.size(); ++j) {
@@ -375,7 +380,7 @@ float greedy_criterion(vector<set<Point_2>>& S, int i, vector<set<Point_2>>& C) 
     set<Point_2> s = S[i];
     int f_m = f_minus(C, s);  //cout << "f_m: " << f_m << endl;
     if(f_m == 0)
-       return 100000;
+       return INFEASIBLE;
 
     float val = ((float)Cost[i]) / (f_minus(C, s));     //cout << "val: " << val << endl; 
     return val;
@@ -399,7 +404,7 @@ int min_greedy(vector<set<Point_2>>& S, vector<set<Point_2>>& C, vector<int>& in
               //float g_mi = greedy_criterion(S, i, C); //cout << "gmi: " << g_mi << endl;
               //float g_mi = greedy_criterion1(i);
               float g_mi = greedy_criterion2(S, indeks, i);
-              if(g_mi < g_m and g_mi != 100000 and !findA(indeks, i)) 
+              if(g_mi < g_m and g_mi != INFEASIBLE and !findA(indeks, i)) 
               { 
                  dodaj = i;
                  g_m = g_mi;   

### 2020-09-06 doc/software/milan/greedyLovasz.cpp
new resultat

@@ -51,7 +51,7 @@ using namespace std::chrono;
 vector<float> Surface;
 vector<int> Cost;
 vector<vector<float>>Intersection;
-#define INFEASIBLE 100000;
+#define INFEASIBLE 100000
 
 /** kraj pomocnih str. za gridi metode **/
 
@@ -449,7 +449,7 @@ float greedy_procedure(vector<set<Point_2>> &S)
 
 int main(int argc, char const *argv[])
 {
-  for(int file_number=8; file_number<=200; file_number+=2) // start = 8
+  for(int file_number=50; file_number<=200; file_number+=2) // start = 8
   for(int file_order=1; file_order<=1; file_order++) // file_order<=file_number
   {
     const string category = "small";

### 2020-09-07 doc/paper.tex
small fix
extended the doc

@@
 If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard.
-So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc.
+So, based on it, we always try to  add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc.
 to formula~(\ref{eq:intersection-heuristic})
@@
        	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon).
+       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$.
+Based on this measure, we assign prices to the vertices.
+If |V(j)| is larger, the large is the price of the vertex $j$.
        \end{itemize}

### 2020-09-07 doc/software/milan/greedyLovasz.cpp
add cardinalityD, union_by_index and cardinality_by_index

@@ -52,6 +52,7 @@ vector<float> Surface;
 vector<int> Cost;
 vector<vector<float>>Intersection;
 #define INFEASIBLE 100000
+int cardinalityD;
 
 /** kraj pomocnih str. za gridi metode **/
 
@@ -298,7 +299,37 @@ Traits_2::FT area_set_polygons(Polygon_set_2 S)
   return povrsina;
 }
 
+
+// unija skupova iz @S sa indeksima iz @index
+/**
+param:
+@index: skup indeksa cije vrijednosti treba sojiti uniom
+@S: Skuovi tacaka vidljivosti za odgovarajuce strazare
+**/
+set<Point_2> union_by_index(vector<int> &index, vector<set<Point_2>> &S)
+{
+  set<Point_2> result;
+  for (size_t i = 0; i < index.size(); i++)
+    for(Point_2 p : S[i])
+      result.insert(p);
+  
+  return result;
+}
+
+// kardinalnost skupa tacaka koje su pokrivene sa tjemenima ciji su indeksi dati sa @indeks
+/**
+param:
+@index: skup indeksa cije vrijednosti treba sojiti uniom
+@S: Skuovi tacaka vidljivosti za odgovarajuce strazare
+**/
+int cardinality_by_index(vector<int> &index, vector<set<Point_2>> &S)
+{
+  return union_by_index(index, S).size();
+}
+
 // Markove funkcije  -  malo modifikovano
+
+
 
 int f(vector<set<Point_2>> &C)
 {
@@ -399,13 +430,13 @@ bool findA(vector<int>& s, int a)
 
 int min_greedy(vector<set<Point_2>>& S, vector<set<Point_2>>& C, vector<int>& indeks)
 {         //cout << "min_greedy" << endl;
-          float g_m = 10000000; int dodaj;
+          float g_m = -1; int dodaj;
           for(int i = 0; i < S.size(); ++i)
           {  // cout << "i " << i << endl;
               //float g_mi = greedy_criterion(S, i, C); //cout << "gmi: " << g_mi << endl;
               //float g_mi = greedy_criterion1(i);
               float g_mi = greedy_criterion2(S, indeks, i);
-              if(g_mi < g_m and g_mi != INFEASIBLE and !findA(indeks, i)) 
+              if(g_mi > g_m and g_mi != INFEASIBLE and !findA(indeks, i)) 
               { 
                  dodaj = i;
                  g_m = g_mi;   
[…]

### 2020-09-07 doc/software/milan/greedyLovasz.cpp
implemented greedy from Dragan

@@ -53,6 +53,7 @@ vector<int> Cost;
 vector<vector<float>>Intersection;
 #define INFEASIBLE 100000
 int cardinalityD;
+int wTotal = 0;
 
 /** kraj pomocnih str. za gridi metode **/
 
@@ -319,7 +320,7 @@ set<Point_2> union_by_index(vector<int> &index, vector<set<Point_2>> &S)
 // kardinalnost skupa tacaka koje su pokrivene sa tjemenima ciji su indeksi dati sa @indeks
 /**
 param:
-@index: skup indeksa cije vrijednosti treba sojiti uniom
+@index: skup indeksa cije vrijednosti treba spojiti uniom
 @S: Skuovi tacaka vidljivosti za odgovarajuce strazare
 **/
 int cardinality_by_index(vector<int> &index, vector<set<Point_2>> &S)
@@ -403,9 +404,11 @@ float greedy_criterion2(vector<set<Point_2>>& S, vector<int>& indeks, int i)   /
 }
 /**
 param:
+
 @S: skup svih skupova (instance) 
 @C: parcijalno rjesenje (trenutno) 
 @i: index skupa S_i koji se razmatra za dodavanje u parcijalni skup @C
+
 **/
 float greedy_criterion(vector<set<Point_2>>& S, int i, vector<set<Point_2>>& C) // take s_i from S
 {     
@@ -427,6 +430,38 @@ bool findA(vector<int>& s, int a)
 
       return false;  
 }
+/**
+param: 
+@indeks: indeks svih skupova koji su u trenutnom parcijalnom rjesenju;
+@i: ineks skupa za koji racunamo gridi vrijednost.
+
+**/
+float gridi_cirterion_dragan(vector<int> &index, int i)
+{
+      if(std::find(index.begin(), index.end(), i) != index.end())
+          return INFEASIBLE;
+      index.push_back(i); // trebalo bi ovo optimizovati 
+
+      int correct_total = cardinality_by_index(index, S);  // broj pokrivenih tacaka diskretizacije
+      int incorrect_total =  cardinalityD - correct_total;
+      
+      int wPartial = 0; 
+      for(int i: index)
+      {
+          wPartial += Cost[ i ]; 
+      }
+
+      double obj1part = ((double) wPartial) / wTotal;
+      double obj2part = (float) incorrect_total / cardinalityD;
+      double obj = obj1part + obj2part;
+      
+      // drop vertex i from indeks 
[…]

### 2020-09-07 doc/software/milan/greedyLovasz.cpp
new results

@@ -436,7 +436,7 @@ param:
 @i: ineks skupa za koji racunamo gridi vrijednost.
 
 **/
-float gridi_cirterion_dragan(vector<int> &index, int i)
+float gridi_cirterion_dragan(vector<set<Point_2>>& S, vector<int> &index, int i)
 {
       if(std::find(index.begin(), index.end(), i) != index.end())
           return INFEASIBLE;
@@ -456,8 +456,8 @@ float gridi_cirterion_dragan(vector<int> &index, int i)
       double obj = obj1part + obj2part;
       
       // drop vertex i from indeks 
-      vector<int>::iterator it = std::find(indeks.begin(), indeks.end(), i); 
-      indeks.erase(it);
+      vector<int>::iterator it = std::find(index.begin(), index.end(), i); 
+      index.erase(it);
 
       return obj;
 }
@@ -470,7 +470,8 @@ int min_greedy(vector<set<Point_2>>& S, vector<set<Point_2>>& C, vector<int>& in
           {  // cout << "i " << i << endl;
               //float g_mi = greedy_criterion(S, i, C); //cout << "gmi: " << g_mi << endl;
               //float g_mi = greedy_criterion1(i);
-              float g_mi = greedy_criterion2(S, indeks, i);
+              //float g_mi = greedy_criterion2(S, indeks, i);
+              float g_mi = gridi_cirterion_dragan(S, indeks, i);
               if(g_mi > g_m and g_mi != INFEASIBLE and !findA(indeks, i)) 
               { 
                  dodaj = i;
@@ -518,11 +519,11 @@ float greedy_procedure(vector<set<Point_2>> &S, Polygon_2 &pol)
 
 int main(int argc, char const *argv[])
 {
-  for(int file_number=14; file_number<=14; file_number+=2) // start = 8
+  for(int file_number=8; file_number<=200; file_number+=2) // start = 8
   for(int file_order=1; file_order<=1; file_order++) // file_order<=file_number
   {
     const string category = "small";
-    const string result_location = "test-small-greedy-criterion2.txt";
+    const string result_location = "test-small-greedy-criterion-dragan.txt";
 
     string filename = "min-" + std::to_string(file_number) + "-" + std::to_string(file_order) + ".pol";
     string location = "instance/" + category + "/" + filename;
@@ -551,7 +552,7 @@ int main(int argc, char const *argv[])
     cout<<"end!!!"<<endl;
     
     //-------------------------------- area of intersection poligons -------------------------
[…]

### 2020-09-07 doc/software/milan/greedyLovasz.cpp
implemented weights based on D(P) -- visibility set

@@ -49,7 +49,7 @@ using namespace std::chrono;
 
 /** pomocne strukture za gridi metod **/
 vector<float> Surface;
-vector<int> Cost;
+vector<float> Cost;
 vector<vector<float>>Intersection;
 #define INFEASIBLE 100000
 int cardinalityD;
@@ -586,12 +586,15 @@ int main(int argc, char const *argv[])
     cardinalityD = f(pvD);
 
     // ---------------------------------greedy------------------------------------
-    // vector<int> cost;
+    
+    // ----------------------- dodjela tezina (proporcionalno broju pokrivenih tacaka iz D(P) ------------------------------------
+ 
     for (size_t i = 0; i < n; i++){
-         //wTotal += 1;
-         Cost.push_back(1);
+         float w_i = n * n * ( ((float)S[i].size()) / cardinalityD );
+         wTotal += w_i;
+         Cost.push_back(w_i);
     }
-    wTotal = n; // ovo ce biti promijenjeno kada se tezine budu generisale (kao zbir svih tezina); 
+    //wTotal = n; // ovo ce biti promijenjeno kada se tezine budu generisale (kao zbir svih tezina); 
 
     auto start = high_resolution_clock::now();
     float s = greedy_procedure(pvD, p);

### 2020-09-08 doc/software/milan/greedyLovasz.cpp
minor fix

@@ -591,7 +591,7 @@ int main(int argc, char const *argv[])
     // ----------------------- dodjela tezina (proporcionalno broju pokrivenih tacaka iz D(P) ------------------------------------
  
     for (size_t i = 0; i < n; i++){
-         float w_i = n * n * ( ((float)S[i].size()) / cardinalityD );
+         float w_i = n * n * ( ((float) pvD[i].size()) / cardinalityD );
          wTotal += w_i;
          Cost.push_back(w_i);
     }

### 2020-09-08 doc/software/milan/greedy.cpp
new file greedy.cpp

@@ -1,0 +1,268 @@
+#include <list>
+// #include <minisat/core/Solver.h>
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <sstream>
+#include <chrono>
+#include <bits/stdc++.h>
+#include <utility>
+
+using namespace std;
+using namespace std::chrono;
+
+typedef pair<float, float> Point_2;
+
+/** pomocne strukture za gridi metod **/
+
+vector<float> Surface; // for a vertex indexed by i, we return the surface of V(i)
+vector<float> Cost; // at index i --> w_i
+vector<vector<float>>Intersection; // Intersection[i][j] = Volume of V(i) intersected by V(j)
+vector<set<Point_2>> S; // i-th position of S is a set of all points that are visible from vertex i
+#define INFEASIBLE 1000000
+int cardinalityD; // |D(P)|
+int wTotal = 0; // total weight 
+int t_lim = 0; // time limit
+std::string path;
+/** kraj pomocnih str. za gridi metode **/
+
+
+inline int stoi(string &s) {
+
+     return atoi(s.c_str());
+}
+
+inline double stof(string &s) {
+
+     return atof(s.c_str());
+}
+
+void read_parameters(int argc, char **argv) {
+
+     int iarg=1;
+     if (strcmp(argv[iarg],"-f") == 0) path = (argv[++iarg]);
+     else if(strcmp(argv[iarg],"-t") == 0) t_lim = atoi(argv[++iarg]);
+     else ++iarg;
+}
+
+void read_from_file(std:: string path)
+{
+     // TODO: read from file
+}
+
+// unija skupova iz @S sa indeksima iz @index
+/**
+param:
+@index: skup indeksa cije vrijednosti treba sojiti uniom
+@S: Skuovi tacaka vidljivosti za odgovarajuce strazare
+**/
+set<Point_2> union_by_index(vector<int> &index)
+{
+  set<Point_2> result;
+  for (size_t i = 0; i < index.size(); i++)
+    for(Point_2 p : S[i])
+       result.insert(p);
+  
+  return result;
+}
+
+// kardinalnost skupa tacaka koje su pokrivene sa tjemenima ciji su indeksi dati sa @indeks
+/**
+param:
+@index: skup indeksa cije vrijednosti treba spojiti uniom
+@S: Skuovi tacaka vidljivosti za odgovarajuce strazare
+**/
+int cardinality_by_index(vector<int> &index)
+{
[…]

### 2020-09-08 doc/software/milan/greedy.cpp
params extended

@@ -13,6 +13,7 @@ using namespace std::chrono;
 
 typedef pair<float, float> Point_2;
 
+
 /** pomocne strukture za gridi metod **/
 
 vector<float> Surface; // for a vertex indexed by i, we return the surface of V(i)
@@ -23,6 +24,7 @@ vector<set<Point_2>> S; // i-th position of S is a set of all points that are vi
 int cardinalityD; // |D(P)|
 int wTotal = 0; // total weight 
 int t_lim = 0; // time limit
+int greedy = 0; // tip gridija => 0: Lovasz; 1: price-per-unit; 2: intersection-based; 3: Greedy by Dragan
 std::string path;
 /** kraj pomocnih str. za gridi metode **/
 
@@ -42,6 +44,7 @@ void read_parameters(int argc, char **argv) {
      int iarg=1;
      if (strcmp(argv[iarg],"-f") == 0) path = (argv[++iarg]);
      else if(strcmp(argv[iarg],"-t") == 0) t_lim = atoi(argv[++iarg]);
+     else if(strcmp(argv[iarg],"-greedy") == 0) greedy = atoi(argv[++iarg]);
      else ++iarg;
 }
 
@@ -202,11 +205,14 @@ int min_greedy(vector<set<Point_2>>& C, vector<int>& indeks)
 {         //cout << "min_greedy" << endl;
           float g_m = -1; int dodaj;
           for(int i = 0; i < S.size(); ++i)
-          {  // cout << "i " << i << endl;
-              float g_mi = greedy_criterion(i, C); //cout << "gmi: " << g_mi << endl;
-              //float g_mi = greedy_criterion1(i);
-              //float g_mi = greedy_criterion2(S, indeks, i);
-              //float g_mi = gridi_criterion_dragan(S, indeks, i);
+          { 
+              float g_mi;
+              switch(greedy){
+                  case 0: g_mi = greedy_criterion(i, C); break;
+                  case 1: g_mi = greedy_criterion_1(i); break;
+                  case 2: g_mi = greedy_criterion_2(indeks, i); break;
+                  default: g_mi = gridi_criterion_dragan(indeks, i);
+              }
               if(g_mi <= g_m and g_mi != INFEASIBLE and !findA(indeks, i)) 
               { 
                  dodaj = i;
@@ -261,8 +267,8 @@ int main( int argc, char **argv ) {
     // ------------------------------greedy - end------------------------------------
 
[…]

### 2020-09-08 doc/software/milan/pretprocesiranje.cpp
add instances for polygons with small area

@@ -312,12 +312,53 @@ void print_polygon_with_holes(const CGAL::Polygon_with_holes_2<Kernel, Container
   }
 }
 
-void write_test(string filename, string tekst)
+void print_set_poligon(Polygon_set_2 S)
+{
+  std::list<Polygon_with_holes_2> res;
+  S.polygons_with_holes (std::back_inserter (res));
+
+  Pwh_list_2::const_iterator it_res;
+  for (it_res = res.begin(); it_res != res.end(); ++it_res) 
+    print_polygon_with_holes(*it_res);
+}
+
+void write_test(string location, string tekst)
 {
   std::ofstream outfile;
 
-  outfile.open("predprocesing/small/"+filename, std::ios_base::app); // append instead of overwrite
-  outfile << tekst; 
+  outfile.open(location, std::ios_base::app); // append instead of overwrite
+  outfile << tekst;
+}
+
+template<class Kernel, class Container>
+Traits_2::FT area_polygon_with_holes(const CGAL::Polygon_with_holes_2<Kernel, Container> & pwh)
+{
+  Traits_2::FT res = 0;
+  if (! pwh.is_unbounded()) {
+    res = abs(pwh.outer_boundary().area());
+  } else
+    return res;
+/*
+  typename CGAL::Polygon_with_holes_2<Kernel,Container>::Hole_const_iterator hit;
+  unsigned int k = 1;
+  for (hit = pwh.holes_begin(); hit != pwh.holes_end(); ++hit, ++k) 
+    res -= abs((*hit).area());
+*/
+  return res;
+}
+
+Traits_2::FT area_set_polygons(Polygon_set_2 S)
+{
+  Traits_2::FT povrsina = 0;
+
+  std::list<Polygon_with_holes_2> res;
+  S.polygons_with_holes (std::back_inserter (res));
+
+  Pwh_list_2::const_iterator it_res;
+  for (it_res = res.begin(); it_res != res.end(); ++it_res) 
+    povrsina += area_polygon_with_holes(*it_res);
+      
+  return povrsina;
 }
 
 int main(int argc, char const *argv[])
@@ -325,16 +366,20 @@ int main(int argc, char const *argv[])
   for(int file_number=8; file_number<201; file_number+=2) // start = 8
   for(int file_order=1; file_order<=1; file_order++) // file_order<=file_number
   {
-    string filename = "min-" + std::to_string(file_number) + "-" + std::to_string(file_order) + ".pol";
[…]

### 2020-09-09 doc/software/milan/greedy.cpp
extended parameters

@@ -26,6 +26,8 @@ int wTotal = 0; // total weight
 int t_lim = 0; // time limit
 int greedy = 0; // tip gridija => 0: Lovasz; 1: price-per-unit; 2: intersection-based; 3: Greedy by Dragan
 std::string path;
+int n = 0; // |V(P)|
+int w_type = 0; // ti ptezine koju pozivamo; 0: tezina proporcionalna velicini vidljivosti svakog vrha; 1: --; 2: --
 /** kraj pomocnih str. za gridi metode **/
 
 
@@ -45,6 +47,7 @@ void read_parameters(int argc, char **argv) {
      if (strcmp(argv[iarg],"-f") == 0) path = (argv[++iarg]);
      else if(strcmp(argv[iarg],"-t") == 0) t_lim = atoi(argv[++iarg]);
      else if(strcmp(argv[iarg],"-greedy") == 0) greedy = atoi(argv[++iarg]);
+     else if(strcmp(argv[iarg],"-w_type") == 0) w_type = atoi(argv[++iarg]);
      else ++iarg;
 }
 
@@ -260,6 +263,24 @@ int main( int argc, char **argv ) {
 
     read_parameters(argc, argv);
     read_from_file(path); // fill Cost, Intersection and Surface
+
+    // ----------------------- dodjela tezina (proporcionalno broju pokrivenih tacaka iz D(P) ------------------------------------
+    switch(w_type){
+ 
+          case 0: { // tezina proporcionalna sa velicinom skupa S[i]
+                  for(auto& X: S){
+                      cardinalityD += X.size();
+                  }
+                  for (size_t i = 0; i < n; i++){
+                      float w_i = n * n * ( ((float) S[i].size()) / cardinalityD );
+                      wTotal += w_i;
+                      Cost.push_back(w_i);
+                  }; break;}
+          default: {
+                    for(size_t i = 0; i < n; i++) // non-weighted version of the problem
+                       Cost.push_back(1);
+                   }
+   }
     // ---------------------------------greedy------------------------------------
     auto start = high_resolution_clock::now();
     float s = greedy_procedure();

### 2020-09-09 doc/software/milan/greedy.cpp
dodato citanje iz datoteke

@@ -7,6 +7,7 @@
 #include <chrono>
 #include <bits/stdc++.h>
 #include <utility>
+#include <string>
 
 using namespace std;
 using namespace std::chrono;
@@ -54,7 +55,130 @@ void read_parameters(int argc, char **argv) {
 void read_from_file(std:: string path)
 {
      // TODO: read from file
+     std::ifstream infile(path);
+     std::string line;
+     std::getline(infile, line);
+     int n = stoi(line); // number of vertices
+
+    int temp = 0;
+
+    while(temp<n){
+        std::getline(infile, line);
+
+        std::string delim1 = ":";
+         auto start = 0U;
+         auto end = line.find(delim1);
+
+         //izdvajanje koordinata tjemena (vrha) poligona
+         std:: string  vrh =  line.substr(start, end - start);
+
+         std::string delim2 = ",";
+
+         auto start1 = 0U;
+         auto end1 = vrh.find(delim2);
+
+         std:: string  vrh1 =  vrh.substr(start1+1, end1 - start1-1);
+         std:: string  vrh2 =  vrh.substr(end1+1, vrh.length()-end1-2);
+
+
+         Point_2 vertex;
+         vertex.first = stof(vrh1);
+         vertex.second = stof(vrh2);
+
+         Vertices.push_back(vertex);
+
+        //izdvjanje skupa tacaka koje se vide iz tog vrha
+
+        std:: string ostatak = line.substr(end+1, line.length() - end);
+
+        std::string delimiter = "\t";
+
+        size_t pos = 0;
+        std::string token;
+        set<Point_2> vertexSet;
+
+        while ((pos = ostatak.find(delimiter)) != std::string::npos) {
+            token = ostatak.substr(0, pos);
+            std::cout << token << std::endl;
+
+            //obrada svakog tokena da bi se dobile koordinate tacaka
+
+
+         std::string delim3 = ",";
+
+         auto start3 = 0U;
+         auto end3 = vrh.find(delim3);
+
+         std:: string  x =  token.substr(start3+1, end3 - start3-1);
+         std:: string  y =  token.substr(end3+1, token.length()-end3-2);
+
+         Point_2 tacka;
+         tacka.first = stof(x);
+         tacka.second = stof(y);
+
+        vertexSet.insert(tacka);
+
+          ostatak.erase(0, pos + delimiter.length());
+    }
+
+
+    //izdvajanje povrsina
+    temp = 0;
+    while(temp<n){
[…]

### 2020-09-09 doc/software/milan/greedy.cpp
neke izmjene

@@ -21,6 +21,7 @@ vector<float> Surface; // for a vertex indexed by i, we return the surface of V(
 vector<float> Cost; // at index i --> w_i
 vector<vector<float>>Intersection; // Intersection[i][j] = Volume of V(i) intersected by V(j)
 vector<set<Point_2>> S; // i-th position of S is a set of all points that are visible from vertex i
+vector<Point_2> Vertices; // vector of vertices
 #define INFEASIBLE 1000000
 int cardinalityD; // |D(P)|
 int wTotal = 0; // total weight 
@@ -117,11 +118,11 @@ void read_from_file(std:: string path)
          tacka.second = stof(y);
 
         vertexSet.insert(tacka);
-
-          ostatak.erase(0, pos + delimiter.length());
+        ostatak.erase(0, pos + delimiter.length());
     }
-
-
+    S.push_back(vertexSet);
+    temp++;
+   }
     //izdvajanje povrsina
     temp = 0;
     while(temp<n){
@@ -170,13 +171,7 @@ void read_from_file(std:: string path)
             temp=1;
             n--;
         }
-
-
     }
-
-
-    }
-
 }
 
 
@@ -387,6 +382,7 @@ int main( int argc, char **argv ) {
 
     read_parameters(argc, argv);
     read_from_file(path); // fill Cost, Intersection and Surface
+    cout << S.size() << " " << S[0].size() << " " << Surface[0] << endl;
 
     // ----------------------- dodjela tezina (proporcionalno broju pokrivenih tacaka iz D(P) ------------------------------------
     switch(w_type){

### 2020-09-09 doc/software/milan/greedy.cpp
update in the code

@@ -46,11 +46,13 @@ inline double stof(string &s) {
 void read_parameters(int argc, char **argv) {
 
      int iarg=1;
+     while (iarg < argc) {
      if (strcmp(argv[iarg],"-f") == 0) path = (argv[++iarg]);
      else if(strcmp(argv[iarg],"-t") == 0) t_lim = atoi(argv[++iarg]);
      else if(strcmp(argv[iarg],"-greedy") == 0) greedy = atoi(argv[++iarg]);
      else if(strcmp(argv[iarg],"-w_type") == 0) w_type = atoi(argv[++iarg]);
      else ++iarg;
+   }
 }
 
 void read_from_file(std:: string path)
@@ -202,38 +204,42 @@ int cardinality_by_index(vector<int> &index)
   return union_by_index(index).size();
 }
 
-int f(vector<set<Point_2>> &C)
+int f(vector<int> &C)
 {
-  std::set<Point_2> d;
-       for(set<Point_2> di : C){
+      std::set<Point_2> d;
+      for(int ix: C){
      
-           for (Point_2 dii: di){
-               //cout << "dii" << dii << endl;
+           for (Point_2 dii: S[ix]){
+              // cout << "dii" << dii.first << endl;
                d.insert(dii);
            }
-       }
-       return (int)d.size();
+      }
+      return (int)d.size();
 }
 
-int f_minus(vector<set<Point_2>>& C, set<Point_2>& ss) // f(C u {s}) - f(S)
+int f_minus(vector<int>& C, int i) // f(C u {S_i}) - f(S)
 {
+    //cout <<" f_minus" << C.size() << " - " << ss.size() << endl;
     int count = 0; // ako i \in ss nije niti u jednom od skupova u S, onda count++;
-    if(C.empty())
-       return ss.size();
-
-    for(Point_2 i: ss) 
+    if(C.size() == 0 ){
+       //cout << "before " << S[i].size() - count;
+       return S[i].size();
+    }
+    // cout << "continue" << endl;
+    for(auto ix: S[i]) 
     {
+        //cout << ix.first << " " << ix.second << endl;
         bool presented = false;
-        for(set<Point_2>& di : C){
-            if(di.count(i) > 0){
+        for(int id : C){
+            if(S[id].count(ix) > 0){
                presented = true;
                break; 
             }
         }
         if(presented) 
            count++;
-    }
-    return ss.size() - count; 
+    } 
+    return S[i].size() - count; 
 }
 
 float greedy_criterion_1(int i)
[…]

### 2020-09-09 doc/software/milan/greedy.cpp
add result and bash script

@@ -28,6 +28,7 @@ int wTotal = 0; // total weight
 int t_lim = 0; // time limit
 int greedy = 0; // tip gridija => 0: Lovasz; 1: price-per-unit; 2: intersection-based; 3: Greedy by Dragan
 std::string path;
+std::string output = "";
 int n = 0; // |V(P)|
 int w_type = 0; // ti ptezine koju pozivamo; 0: tezina proporcionalna velicini vidljivosti svakog vrha; 1: --; 2: --
 /** kraj pomocnih str. za gridi metode **/
@@ -51,6 +52,7 @@ void read_parameters(int argc, char **argv) {
      else if(strcmp(argv[iarg],"-t") == 0) t_lim = atoi(argv[++iarg]);
      else if(strcmp(argv[iarg],"-greedy") == 0) greedy = atoi(argv[++iarg]);
      else if(strcmp(argv[iarg],"-w_type") == 0) w_type = atoi(argv[++iarg]);
+     else if(strcmp(argv[iarg],"-l") == 0) output = argv[++iarg];
      else ++iarg;
    }
 }
@@ -398,6 +400,31 @@ float greedy_procedure()
      //return C.size();
 }
 
+vector<string> split(const string& str, const string& delim)
+{
+    vector<string> tokens;
+    size_t prev = 0, pos = 0;
+    do
+    {
+        pos = str.find(delim, prev);
+        if (pos == string::npos) pos = str.length();
+        string token = str.substr(prev, pos-prev);
+        if (!token.empty()) tokens.push_back(token);
+        prev = pos + delim.length();
+    }
+    while (pos < str.length() && prev < str.length());
+
+    return tokens;
+}
+
+void write_test(string tekst)
+{
+  std::ofstream outfile;
+
+  outfile.open(output, std::ios_base::app); // append instead of overwrite
+  outfile << tekst;
+}
+
 int main( int argc, char **argv ) {
 
     read_parameters(argc, argv);
@@ -441,6 +468,13 @@ int main( int argc, char **argv ) {
     auto duration = duration_cast<microseconds>(stop - start); 
     cout << "Time Execution: " << duration.count() << " microseconds" << endl;
     cout << "Result: " << s << endl;
+
+    if(output.compare("") != 0){
+        string name_polygon = split(split(path, "/")[2], "_")[0];
+        cout<<name_polygon<<"---"<<output<<endl;
[…]

### 2020-09-09 doc/software/milan/pretprocesiranje.cpp

@@ -363,15 +363,15 @@ Traits_2::FT area_set_polygons(Polygon_set_2 S)
 
 int main(int argc, char const *argv[])
 {
-  for(int file_number=8; file_number<201; file_number+=2) // start = 8
-  for(int file_order=1; file_order<=1; file_order++) // file_order<=file_number
+  for(int file_number=100; file_number<150; file_number+=2) // start = 8
+  for(int file_order=1; file_order<=file_number; file_order++) // file_order<=file_number
   {
-    const string category = "small";
-    string filename = "min-" + std::to_string(file_number) + "-" + std::to_string(file_order);
+    const string category = "random";
+    string filename = "rand-" + std::to_string(file_number) + "-" + std::to_string(file_order);
     
     string location = "instance/" + category + "/" + filename + + ".pol";
     string output = "preprocessing/" + category + "/" + filename + "_D1.txt";
-    string timeexecution = "executiontime-" + category + "_D1.txt";
+    string timeexecution = "executiontime-" + category + "_D1 - 2.txt";
 
     // ----------------------------read polygon---------------------------------
     auto start = high_resolution_clock::now();
@@ -389,27 +389,37 @@ int main(int argc, char const *argv[])
         pv[i].reverse_orientation();
     // kraj promjene orjentacije
     cout<<"end!!!"<<endl;
+     
 
     // -----------------------diskretization polygon------------------------------
     cout<<"Creating diskretization polygon P..............";
     vector<Point_2> D = discrate(p);
+    auto stop = high_resolution_clock::now();
+    auto duration1 = duration_cast<microseconds>(stop - start);
     cout<<"end!!!"<<endl;
 
     // -----------------------diskretization visibility polygons-------------------
     cout<<"Creating diskretization for visibility polygons...................";
+    start = high_resolution_clock::now();
     vector<set<Point_2>> pvD(p.size());
     for (size_t i = 0; i < pv.size(); i++)
         discratePVI(D, pv[i], pvD[i]);
+    stop = high_resolution_clock::now();
+    auto duration2 = duration_cast<microseconds>(stop - start);
 
     //-------------------------------- area of poligons -------------------------
-    vector<float> Surface;
     cout<<"Calculating area of polygon...................";
+    start = high_resolution_clock::now();
+    vector<float> Surface;
     for (size_t i = 0; i < n; i++)
       Surface.push_back((float)converter(pv[i].area()));
[…]

### 2020-09-09 doc/software/milan/test.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+for i in $(seq 8 2 200)
+do
+   ./greedy.out -f preprocessing/small/min-$i-1_D1.txt -t 10 -greedy 3 -l result/result_D1_small_greedy3.txt
+done

### 2020-09-09 doc/software/milan/greedy.cpp
added new weights

@@ -8,6 +8,7 @@
 #include <bits/stdc++.h>
 #include <utility>
 #include <string>
+#include <math.h>       /* sqrt */
 
 using namespace std;
 using namespace std::chrono;
@@ -417,6 +418,12 @@ vector<string> split(const string& str, const string& delim)
     return tokens;
 }
 
+float dist(int i, int j)
+{
+     return sqrt( pow( Vertices[i].first - Vertices[j].first, 2) + pow( Vertices[ i ].second - Vertices[ j ].second, 2) );
+
+}
+
 void write_test(string tekst)
 {
   std::ofstream outfile;
@@ -432,14 +439,14 @@ int main( int argc, char **argv ) {
     cout << S.size() << " " << S[0].size() << " " << Surface[0] <<  endl;
     n = Surface.size();
 
-    for(set<Point_2>& s: S)
+    /*for(set<Point_2>& s: S)
     {
         for(Point_2 sx: s){
            cout << "(" << sx.first << ", " << sx.second << ")" << " ";
         }
         cout << endl;
 
-    }
+    }*/
 
     // ----------------------- dodjela tezina (proporcionalno broju pokrivenih tacaka iz D(P) ------------------------------------
     switch(w_type){
@@ -449,10 +456,18 @@ int main( int argc, char **argv ) {
                       cardinalityD += X.size();
                   }
                   for (size_t i = 0; i < n; i++){
-                      float w_i = n * n * ( ((float) S[i].size()) / cardinalityD );
+                      float w_i = n * ( ((float) S[i].size()) / cardinalityD );
                       wTotal += w_i;
                       Cost.push_back(w_i);
                   }; break;}
+          case 1: {     
+                  float dist0  = (dist(0, n-1) + dist(0,1) ) / 2; 
+                  Cost.push_back(dist0); 
+                   for(int i = 1; i < n; ++i){
+                      Cost.push_back( ( (0.0 + dist(i-1, i) + dist(i, i+1) ) / 2 ) );
+                      cout << "w_i= " << Cost[i] << endl;
+                   }
+                     break;}
           default: {
                     for(size_t i = 0; i < n; i++) // non-weighted version of the problem
                        Cost.push_back(1);

### 2020-09-09 doc/software/milan/greedy.cpp
fixing weights

@@ -179,7 +179,6 @@ void read_from_file(std:: string path)
     }
 }
 
-
 // unija skupova iz @S sa indeksima iz @index
 /**
 param:
@@ -189,10 +188,10 @@ param:
 set<Point_2> union_by_index(vector<int> &index)
 {
   set<Point_2> result;
-  for (size_t i = 0; i < index.size(); i++)
+  for (int i: index){
     for(Point_2 p : S[i])
        result.insert(p);
-  
+  }
   return result;
 }
 
@@ -211,11 +210,10 @@ int f(vector<int> &C)
 {
       std::set<Point_2> d;
       for(int ix: C){
-     
-           for (Point_2 dii: S[ix]){
+          for (Point_2 dii: S[ix]){
               // cout << "dii" << dii.first << endl;
                d.insert(dii);
-           }
+          }
       }
       return (int)d.size();
 }
@@ -308,8 +306,10 @@ param:
 **/
 float gridi_criterion_dragan(vector<int> &index, int i)
 {
-      if(std::find(index.begin(), index.end(), i) != index.end())
-          return INFEASIBLE;
+
+      if(index.size() > 0 and std::find( index.begin(), index.end(), i)  != index.end() )
+         return INFEASIBLE;
+          
       index.push_back(i); // trebalo bi ovo optimizovati 
 
       int correct_total = cardinality_by_index(index);  // broj pokrivenih tacaka diskretizacije
@@ -328,7 +328,7 @@ float gridi_criterion_dragan(vector<int> &index, int i)
       // drop vertex i from indeks 
       vector<int>::iterator it = std::find(index.begin(), index.end(), i); 
       index.erase(it);
-
+      cout << "obj: " << obj << endl;
       return obj;
 }
 
@@ -340,7 +340,7 @@ int min_greedy(vector<int>& indeks)
           if(greedy == 2) 
              g_m *= -1; 
 
-          int dodaj;
+          int dodaj = -1;
           for(int i = 0; i < S.size(); ++i)
           { 
               float g_mi;
@@ -352,14 +352,14 @@ int min_greedy(vector<int>& indeks)
               }
               bool us = g_mi <= g_m; 
               if(greedy == 2)  // reverse order here
-                 us = !us; 
+                 us = !us && (g_mi == g_m); 
 
               if(us and g_mi != INFEASIBLE and !findA(indeks, i)) 
               { 
                  dodaj = i;
                  g_m = g_mi;   
               }
[…]

### 2020-09-09 doc/software/milan/greedy.cpp
results for w_type 1

@@ -488,7 +488,7 @@ int main( int argc, char **argv ) {
 
     if(output.compare("") != 0){
         string name_polygon = split(split(path, "/")[2], "_")[0];
-        cout<<name_polygon<<"---"<<output<<endl;
+        //cout<<name_polygon<<"---"<<output<<endl;
         write_test(name_polygon + ";" + std::to_string(s) + ";" + std::to_string(duration.count()) + "\n");
     }
     

### 2020-09-09 doc/software/milan/greedy.cpp
fix in greedy 2

@@ -262,13 +262,14 @@ float greedy_criterion_2(vector<int>& indeks, int i)
          return INFEASIBLE;
  
       float num = 0.0;
-      int den = S.size() - indeks.size();
+      int den = S.size() - indeks.size(); cout<< "den: " << den <<" " <<  S.size()  << endl; 
       for(int j = 0; j < S.size(); ++j) {
           if( std::find(indeks.begin(), indeks.end(), j) == indeks.end() and i < j)
           { // S_j ne smije biti u vec dodanom parcijalnom skupu 
              cout << i << " " << j << endl;   num += Intersection[i][j];
           } 
       }
+      cout << "obj: " << num /den << endl;
       return num / den;
 }
 /**
@@ -337,9 +338,6 @@ int min_greedy(vector<int>& indeks)
 {        
           cout << "min_greedy" << endl;
           float g_m = INFEASIBLE; 
-          if(greedy == 2) 
-             g_m *= -1; 
-
           int dodaj = -1;
           for(int i = 0; i < S.size(); ++i)
           { 
@@ -347,19 +345,18 @@ int min_greedy(vector<int>& indeks)
               switch(greedy){
                   case 0: g_mi = greedy_criterion(indeks, i); break;
                   case 1: g_mi = greedy_criterion_1(i); break;
-                  case 2: g_mi = greedy_criterion_2(indeks, i) * (-1) ; break;
+                  case 2: g_mi = greedy_criterion_2(indeks, i) ; break;
                   default: g_mi = gridi_criterion_dragan(indeks, i);
               }
               bool us = g_mi <= g_m; 
-              if(greedy == 2)  // reverse order here
-                 us = !us && (g_mi == g_m); 
+              bool us1 = g_mi != INFEASIBLE;
 
-              if(us and g_mi != INFEASIBLE and !findA(indeks, i)) 
+              if(us and us1 and !findA(indeks, i)) 
               { 
                  dodaj = i;
                  g_m = g_mi;   
               }
-          } // cout << "dodati....." << dodaj << endl;
+          } cout << "dodati....." << dodaj << endl;
           return dodaj;
 }
 
@@ -367,7 +364,7 @@ float greedy_procedure()
 {  
      vector<int> C;
      vector<int> indeks;
-     vector<int> Sx; 
+     vector<int> Sx; cout << "n: "<< n << endl;
      for(int i=0; i < n; ++i)
          Sx.push_back(i);
      cout << Sx.size() << endl;
[…]

### 2020-09-09 doc/software/milan/test.sh
results for w_type 1 greedy 2

@@ -1,5 +1,5 @@
 #!/bin/bash
 for i in $(seq 8 2 200)
 do
-   ./greedy.out -f preprocessing/small/min-$i-1_D1.txt -t 10 -greedy 3 -l result/result_D1_small_greedy3_w-type1.txt
+   ./greedy.out -f preprocessing/small/min-$i-1_D1.txt -t 10 -greedy 2 -l result/result_D1_small_greedy2_w-type1.txt
 done

### 2020-09-18 doc/software/Heuristic/greedy.cpp
code upgrade

@@ -181,7 +181,7 @@ bool LS(float * obj){
 	int i = 0;
 	while(i<copy.size()){
 		int vertex = copy[i];
-		cout<<"Cvor: "<<vertex<<endl;
+		//cout<<"Cvor: "<<vertex<<endl;
 		int neigh1 = (vertex+1) % n;
 		int neigh2 = (vertex-1) % n; 
                if( neigh2 <  0) neigh2 = n - 1; 
@@ -508,7 +508,7 @@ float gridi_criterion_dragan(vector<int> &index, int i)
 
 int min_greedy(vector<int>& indeks)
 {        
-          cout << "min_greedy" << endl;
+           
           float g_m = INFEASIBLE; 
           int dodaj = -1;
           for(int i = 0; i < S.size(); ++i)
@@ -529,7 +529,7 @@ int min_greedy(vector<int>& indeks)
                  dodaj = i;
                  g_m = g_mi;   
               }
-          } cout << "dodati....." << dodaj << endl;
+          }// cout << "dodati....." << dodaj << endl;
           return dodaj;
 }
 
@@ -546,7 +546,7 @@ float greedy_procedure()
 
      while(f_C != f_S) 
      { 
-           int index_set = min_greedy(indeks); cout <<"index--------------> " << index_set << endl;
+           int index_set = min_greedy(indeks); // cout <<"index--------------> " << index_set << endl;
            //cout<<pol[index_set]<<endl;
            cout<<"index set: " << index_set<<endl;
            if(!findA(indeks, index_set)){ //jos nije dodan
@@ -577,92 +577,110 @@ float greedy_procedure()
 // uzmemo distancu D i uzmemo samo one cvorove koji su na udaljenosti vecoj od D od v_i (skup VC)
 // random izbacimo neki iz skupa VC...
 
-int izbaciCvor(){
+int izbaciCvor(vector<int>& copy){
 
-     int K = 3;
+     int K = std::min(10, (int) copy.size() / 2); 
+     float Dist = 2.0; 
+     
+     //cout <<"K: " << K << endl;
      vector<int> Candidates; // kandidati za izbacivanje
-     int i = random() % indeks.size(); // uzmemo i-ti vektor
-     int cvor = indeks[ i ];
-     int count1 = 0; 
-     for(int i = cvor + 1; i < n; ++i) 
+     int i = random() % copy.size(); // uzmemo i-ti vektor
+     int cvor = copy[ i ];  
[…]

### 2020-09-20 doc/software/EXACT/cplex_woagp.cpp
CPLEX model and partial solutions

@@ -35,6 +35,7 @@ vector<float> Cost; // at index i --> w_i
 vector<vector<float>>Intersection; // Intersection[i][j] = Volume of V(i) intersected by V(j)
 vector<set<Point_2>> S; // i-th position of S is a set of all points that are visible from vertex i
 set<Point_2> D_P;
+vector<int> indeks; // parcijalno rjesenje (indeksi skupova) 
 vector<Point_2> Vertices; // vector of vertices
 #define INFEASIBLE 1000000
 int cardinalityD; // |D(P)|
@@ -269,6 +270,11 @@ void run_cplex(vector<set<Point_2>>& S, set<Point_2>& D_P, int n){
           model.add(expr_i >= 1);      
        index++ ;
    }  
+   // dopuna parcijalnog rjesenja do najboljeg rjesenja
+   for(int i: indeks) 
+   {
+       model.add(Z[ i ] == 1 ); 
+   }
 
    //std::cout << "#Constraints: "<< constraints_num << std::endl;
    //solve the modelIloLinearNumExpr objective = cplex.linearNumExpr();

### 2020-09-20 doc/software/Heuristic/greedy.cpp
Greedy + CPLEX

@@ -10,8 +10,12 @@
 #include <string>
 #include <math.h>       /* sqrt */
 
+// the following "include" is necessary for the correct working/compilation of CPLEX. You should adapt this path to your installation of CPLEX
+#include "/home/djukanovic/Desktop/projects/LCAPS_software/cplex-12.5/include/ilcplex/ilocplex.h"
+
 using namespace std;
 using namespace std::chrono;
+ILOSTLBEGIN
 
 typedef pair<float, float> Point_2;
 
@@ -23,7 +27,8 @@ set<Point_2> CoveredPoints;//set of points covered by the solution
 vector<int> indeks; //solution
 int alg = 0; // if alg = 1: we execute a Greedy+LS procedure
 bool turn_ls = 0; // tunr on LS into Greedy+LS
-
+int time_limit = 900; // time limit of CPLEX
+float partial = 0.0;
 /** pomocne strukture za gridi metod **/
 
 vector<float> Surface; // for a vertex indexed by i, we return the surface of V(i)
@@ -80,6 +85,105 @@ float distP(Point_2 x, Point_2 y)
      return sqrt( pow( x.first - y.first, 2) + pow( x.second - y.second, 2) );
 }
 
+// begin CPLEX model
+
+float run_cplex(vector<set<Point_2>>& S, vector<Point_2>& D_P, int n){
+
+  IloEnv env;  // cout << "run_cplex " << endl;
+  env.setOut(env.getNullStream());
+  try
+  {
+   IloModel model(env);
+   IloObjective obj = IloMinimize(env);
+   // defining the set of binary variables Z
+   vector<IloNumVar> Z; cout << "S.size() ----> " << S.size() << n << endl;
+   for(int i = 0; i < n; ++i){
+       //cout << "cost i " << Cost[i] << endl;
+       IloNumVar myIntVar(env, 0, 1, ILOINT);
+       Z.push_back(myIntVar); // x_i  \in {0, 1}
+       obj.setLinearCoef(Z[i], Cost[i]); // sum_i c_i x_i
+   }
+   // constraints 
+   cout << "#Vars: " << Z.size() << endl;
+   // constraints 
+   int index = 0;
+   for(Point_2 p : D_P) 
+   {
+       IloExpr expr_i(env); bool add = false;
+       for(int j = 0; j < n; ++j)   
+       {
+           if( S[j].count( p ) ){ // item i se nalazi u skupu j
+               expr_i += Z[j];
+               add = true;
[…]

### 2020-09-21 doc/paper.tex
update of concept

@@
     \end{comment}
+
+    \subsection{Hybrid Greedy + CPLEX}
+        CPLEX will soon or later degrade in its performance w.r.t.
+instance size.
+On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.
+So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete.
+Our approach consists of the following steps:
+        \begin{enumerate}
+        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
+        	\item Take solution $C$ and make it complete via. CPLEX model. 
+        	\begin{itemize}
+        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
+        		\item we obtain a complete solution $C'$;
+        	\end{itemize}
+            \item return $f(C')$. 
+        \end{enumerate}
+
+       \noindent \textbf{Improvements of the above method.} The above method can serve as a basic iteration 
+       of a more advanced techniques like ILP-LNS or CMSA. In this case, methods for destructing the solutions 
+       has to be proposed.  Underlying idea could be:
+       \begin{itemize}
+       	    \item remove $N$ guards with the largest costs out of $C'$
+       	    \item remove $N$ guards which have a higher amount of points from $D(P)$ covered by other guards, represented by the function
+       	    \begin{align}
+       	       ratio(i) = \frac{\sum_{v \in V, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
+       	    \end{align}
+       \end{itemize}
+
      \section{Computational Results}
@@
        	  \item \emph{random benchmarks}.
-For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK?
-} as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
+For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$  as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
        	  \item \emph{topologically-based benchmarks}.

### 2020-09-21 doc/software/Heuristic/greedy.cpp
update

@@ -560,6 +560,7 @@ param:
 @S: skup svih skupova (instance) 
 @C: parcijalno rjesenje (trenutno) 
 @i: index skupa S_i koji se razmatra za dodavanje u parcijalni skup @C
+// cuvati skup koji je pokriven (reference) ili idenkse (hes mapa ka indeksu), pa se pitamo koliko novih tacaka je pokriveno.... 
 **/
 float greedy_criterion(vector<int>& C, int i) // take s_i from S
 {   //cout << "greedy_criterion " << endl;
@@ -895,6 +896,8 @@ float Greedy_CPLEX()
          cout << "\n" << endl;
       }
       float s = run_cplex(S, Vertices, n);
+      //destroy ILP-LNS
+      
       return s;
 }
 

### 2020-09-21 doc/software/Heuristic/greedy.cpp
greedy speeed up: set structure used to save covered points

@@ -25,6 +25,8 @@ map<Point_2,vector<Point_2>> Visibility;//for each point, we provide the list od
 map<Point_2,int> numberOfGuards;//for each point we keep the number of Guards in solution which see that point
 set<Point_2> CoveredPoints;//set of points covered by the solution
 vector<int> indeks; //solution
+set<Point_2> indeksSet; // solution --> points from D(P) covered by indeks
+
 int alg = 0; // if alg = 1: we execute a Greedy+LS procedure
 bool turn_ls = 0; // tunr on LS into Greedy+LS
 int time_limit = 900; // time limit of CPLEX
@@ -48,6 +50,11 @@ int n = 0; // |V(P)|
 int w_type = 0; // ti ptezine koju pozivamo; 0: tezina proporcionalna velicini vidljivosti svakog vrha; 1: --; 2: --
 /** kraj pomocnih str. za gridi metode **/
 
+
+bool operator==(const Point_2& lhs, const Point_2& rhs)
+{
+    return  lhs.first == rhs.first && lhs.second == rhs.second;
+}
 
 inline int stoi(string &s) {
 
@@ -292,7 +299,6 @@ bool LS(float * obj){
 			        cout<<"Test1: "<<neigh1<<":  "<<CoveredPoints2.size()<<endl;
 				//cin.get();
 				updateCoveredPointsRemove(CoveredPoints2,numberOfGuards2,vertex);
-				
 				//cout<<"Test2: "<<CoveredPoints2.size()<<endl;
 				//cin.get();
 				updateCoveredPointsAdd(CoveredPoints2,numberOfGuards2,neigh1);
@@ -525,6 +531,19 @@ int f_minus(vector<int>& C, int i) // f(C u {S_i}) - f(S)
     return S[i].size() - count; 
 }
 
+int f_minus_update( int i ) // f( indeksSet U {i} )  - f( indeksSet) 
+{
+     int difference = 0;
+     for(Point_2 p : S[i])
+     {
+         if(!( indeksSet.count( p ) > 0))
+         {
+            difference++;
+         }
+     }
+     //cout << "difference: " << difference << endl;
+}
+
 float greedy_criterion_1(int i)
 {
     return Cost[i] / Surface[i];
@@ -566,11 +585,11 @@ float greedy_criterion(vector<int>& C, int i) // take s_i from S
 {   //cout << "greedy_criterion " << endl;
     //set<Point_2> s;
     //s = S[i]; cout << s.size() << endl;
[…]

### 2020-09-21 doc/software/Heuristic/greedy.cpp
update

@@ -25,7 +25,7 @@ map<Point_2,vector<Point_2>> Visibility;//for each point, we provide the list od
 map<Point_2,int> numberOfGuards;//for each point we keep the number of Guards in solution which see that point
 set<Point_2> CoveredPoints;//set of points covered by the solution
 vector<int> indeks; //solution
-set<Point_2> indeksSet; // solution --> points from D(P) covered by indeks
+//set<Point_2> indeksSet; // solution --> points from D(P) covered by indeks
 
 int alg = 0; // if alg = 1: we execute a Greedy+LS procedure
 bool turn_ls = 0; // tunr on LS into Greedy+LS
@@ -536,7 +536,7 @@ int f_minus_update( int i ) // f( indeksSet U {i} )  - f( indeksSet)
      int difference = 0;
      for(Point_2 p : S[i])
      {
-         if(!( indeksSet.count( p ) > 0))
+         if(!( CoveredPoints.count( p ) > 0))
          {
             difference++;
          }
@@ -585,7 +585,7 @@ float greedy_criterion(vector<int>& C, int i) // take s_i from S
 {   //cout << "greedy_criterion " << endl;
     //set<Point_2> s;
     //s = S[i]; cout << s.size() << endl;
-    int f_m = f_minus(C, i);  // f_minus_update( i )
+    int f_m =  f_minus_update( i );
     if(f_m == 0)
        return INFEASIBLE;
 
@@ -680,7 +680,7 @@ float greedy_procedure(bool upToK = false)
                //C.push_back((set<int>) S[index_set] );//cout << "dodaj ----> " << index_set << endl;
                indeks.push_back(index_set);
                for(Point_2 p: S[index_set])
-                   indeksSet.insert( p ); 
+                   CoveredPoints.insert( p ); 
            } 
            
            f_C = f(indeks); 

### 2020-09-22 doc/software/Heuristic/greedy.cpp
different tries to spped up f function

@@ -9,6 +9,8 @@
 #include <utility>
 #include <string>
 #include <math.h>       /* sqrt */
+#include <unordered_map> 
+#include <unordered_set> 
 
 // the following "include" is necessary for the correct working/compilation of CPLEX. You should adapt this path to your installation of CPLEX
 #include "/home/djukanovic/Desktop/projects/LCAPS_software/cplex-12.5/include/ilcplex/ilocplex.h"
@@ -50,6 +52,28 @@ int n = 0; // |V(P)|
 int w_type = 0; // ti ptezine koju pozivamo; 0: tezina proporcionalna velicini vidljivosti svakog vrha; 1: --; 2: --
 /** kraj pomocnih str. za gridi metode **/
 
+
+/** hash-map to store points in Covered points */
+
+/** another try to spped up operations over CoveredPoints structure **/
+vector<bool>covered;
+ 
+struct hashFunc{
+    size_t operator()(const Point_2 &k) const{
+    size_t h1 = std::hash<double>()(k.first);
+    size_t h2 = std::hash<double>()(k.second);
+    return (h1 ^ (h2 << 1));
+    }
+};
+
+struct equalsFunc{
+  bool operator()( const Point_2& lhs, const Point_2& rhs ) const{
+    return (lhs.first == rhs.first) && (lhs.second == rhs.second);
+  }
+};
+
+unordered_map<Point_2, bool, hashFunc, equalsFunc> pointDPMapping;
+/** end of the structure **/
 
 bool operator==(const Point_2& lhs, const Point_2& rhs)
 {
@@ -355,7 +379,7 @@ void read_from_file(std:: string path)
      int n = stoi(line); // number of vertices
 
     int temp = 0;
-
+    int indeksiranje = 0;
     while(temp<n){
         std::getline(infile, line);
 
@@ -378,7 +402,6 @@ void read_from_file(std:: string path)
          Point_2 vertex;
          vertex.first = stof(vrh1);
          vertex.second = stof(vrh2);
-
          Vertices.push_back(vertex);
 
         //izdvjanje skupa tacaka koje se vide iz tog vrha
@@ -410,7 +433,13 @@ void read_from_file(std:: string path)
          tacka.first = stof(x);
          tacka.second = stof(y);
 
-        vertexSet.insert(tacka);
+        vertexSet.insert(tacka); 
+        /*if(pointDPMapping.find( tacka ) == pointDPMapping.end() )
+        {
+           pointDPMapping[ tacka ] = indeksiranje; 
+           indeksiranje++;
[…]

### 2020-09-22 doc/software/Heuristic/greedy.cpp
some polishing

@@ -612,8 +612,7 @@ param:
 **/
 float greedy_criterion(vector<int>& C, int i) // take s_i from S
 {   //cout << "greedy_criterion " << endl;
-    //set<Point_2> s;
-    //s = S[i]; cout << s.size() << endl;
+
     int f_m =  f_minus_update( i );
     if(f_m == 0)
        return INFEASIBLE;
@@ -664,23 +663,26 @@ int min_greedy(vector<int>& indeks)
           int dodaj = -1;
           for(int i = 0; i < S.size(); ++i)
           { 
-              float g_mi;
-              switch(greedy){
+              if(!findA(indeks, i))
+              {  
+                 float g_mi;
+                 switch(greedy){
 
-                  case 0: g_mi = greedy_criterion(indeks, i); break;
-                  case 1: g_mi = greedy_criterion_1(i); break;
-                  case 2: g_mi = greedy_criterion_2(indeks, i) ; break;
-                  default: g_mi = gridi_criterion_dragan(indeks, i);
-              }
-              bool us = g_mi <= g_m; 
-              bool us1 = g_mi != INFEASIBLE;
+                        case 0:  g_mi = greedy_criterion(indeks, i); break;
+                        case 1:  g_mi = greedy_criterion_1(i); break;
+                        case 2:  g_mi = greedy_criterion_2(indeks, i) ; break;
+                        default: g_mi = gridi_criterion_dragan(indeks, i);
+                 }
+                 bool us = g_mi <= g_m; 
+                 bool us1 = g_mi != INFEASIBLE;
 
-              if(us and us1 and !findA(indeks, i)) 
-              { 
-                 dodaj = i;
-                 g_m = g_mi;   
-              }
-          }// cout << "dodati....." << dodaj << endl;
+                 if(us and us1) 
+                 { 
+                    dodaj = i;
+                    g_m = g_mi;   
+                 }
+               }// cout << "dodati....." << dodaj << endl;
+          }
           return dodaj;
 }
 
@@ -723,9 +725,7 @@ float greedy_procedure(bool upToK = false)
 
      float greedy_val = 0;
      for(int ix: indeks){
-         
         greedy_val += Cost[ ix ];
-        
      }
      cout << "number of guards: " << indeks.size() << endl;
      return greedy_val; 

### 2020-09-22 doc/software/Heuristic/greedy.cpp
update

@@ -635,7 +635,7 @@ float gridi_criterion_dragan(vector<int> &index, int i)
           
       index.push_back(i); // trebalo bi ovo optimizovati 
 
-      int correct_total = cardinality_by_index(index);  // broj pokrivenih tacaka diskretizacije
+      int correct_total = CoveredPoints.size();//cardinality_by_index(index);  // broj pokrivenih tacaka diskretizacije
       int incorrect_total =  cardinalityD - correct_total;
       
       int wPartial = 0; 

### 2020-09-22 doc/software/Heuristic/greedy.cpp
Dragan's greedy polished

@@ -571,6 +571,7 @@ int f_minus_update( int i ) // f( indeksSet U {i} )  - f( indeksSet)
          }
      }
      //cout << "difference: " << difference << endl;
+     return difference;
 }
 
 float greedy_criterion_1(int i)
@@ -621,6 +622,9 @@ float greedy_criterion(vector<int>& C, int i) // take s_i from S
     return val;
 }
 
+
+
+
 /**
 param: 
 @indeks: indeks svih skupova koji su u trenutnom parcijalnom rjesenju;
@@ -630,12 +634,13 @@ param:
 float gridi_criterion_dragan(vector<int> &index, int i)
 {
 
-      if(index.size() > 0 and std::find( index.begin(), index.end(), i)  != index.end() )
-         return INFEASIBLE;
+     /* if(index.size() > 0 and std::find( index.begin(), index.end(), i)  != index.end() )
+         return INFEASIBLE;*/
           
       index.push_back(i); // trebalo bi ovo optimizovati 
-
-      int correct_total = CoveredPoints.size();//cardinality_by_index(index);  // broj pokrivenih tacaka diskretizacije
+      
+      int number_after_add_i = f_minus_update( i ); 
+      int correct_total =  CoveredPoints.size() +  number_after_add_i;//cardinality_by_index(index);  // broj pokrivenih tacaka diskretizacije
       int incorrect_total =  cardinalityD - correct_total;
       
       int wPartial = 0; 

### 2020-09-23 doc/software/Heuristic/greedy.cpp
a try to fix the error in greedy + LS

@@ -252,8 +252,7 @@ void updateCoveredPointsRemove(set<Point_2>& CovPoints,map<Point_2,int> & noOfG,
 		else
 		{
 			noOfG.find(p)->second--;//one guard less see p
-		}
-			
+		}	
        
    }
 
@@ -528,7 +527,6 @@ int f(vector<int> &C)
       std::set<Point_2> d;
       for(int ix: C){
           for (Point_2 dii: S[ix]){
-              // cout << "dii" << dii.first << endl;
                d.insert(dii);
           }
       }
@@ -661,22 +659,23 @@ float gridi_criterion_dragan(vector<int> &index, int i)
 }
 
 
-int min_greedy(vector<int>& indeks)
+int min_greedy(vector<int>& indeks1)
 {        
            
           float g_m = INFEASIBLE; 
-          int dodaj = -1;
+          int dodaj = -1; cout << " isize " << indeks1.size() << " " << S.size() <<  endl;
           for(int i = 0; i < S.size(); ++i)
-          { 
-              if(!findA(indeks, i))
-              {  
+          {    cout <<"i: " << i << " ";
+              
+              if( std::find(indeks1.begin(), indeks1.end(), i) == indeks1.end() )
+              {  cout << " nalazi se " << i << "\n "; 
                  float g_mi;
                  switch(greedy){
 
-                        case 0:  g_mi = greedy_criterion(indeks, i); break;
-                        case 1:  g_mi = greedy_criterion_1(i); break;
-                        case 2:  g_mi = greedy_criterion_2(indeks, i) ; break;
-                        default: g_mi = gridi_criterion_dragan(indeks, i);
+                        case 0 :  g_mi = greedy_criterion(indeks1, i); break;
+                        case 1 :  g_mi = greedy_criterion_1(i); break;
+                        case 2 :  g_mi = greedy_criterion_2(indeks1, i) ; break;
+                        default: g_mi = gridi_criterion_dragan(indeks1, i);
                  }
                  bool us = g_mi <= g_m; 
                  bool us1 = g_mi != INFEASIBLE;
@@ -836,7 +835,7 @@ float greedy_LS()
          Sx.push_back(i);
      //cout << Sx.size() << endl;
      int f_S = f(Sx);  
-     cout << "f_S: " << f_S << endl;
+     cout << "f_S: " << f_S << endl; 
      int f_C = 0;
      float obj_val = 0;
      bool covered = false; 
@@ -847,7 +846,7 @@ float greedy_LS()
[…]

### 2020-09-23 doc/software/Heuristic/greedy.cpp
update

@@ -235,7 +235,7 @@ void updateCoveredPointsRemove(set<Point_2>& CovPoints,map<Point_2,int> & noOfG,
     	
         if (noOfG.find(p) == noOfG.end()){
         	cout<<"------------------ERROR:"<<p<<"  "<<noOfG.find(p)->second<<endl;
-        	cin.get();
+        	//cin.get();
         	return;
         }
        // cout<<"Tacka "<<p<<" pokrivena sa: "<< noOfG.find(p)->second<<endl;
@@ -401,7 +401,7 @@ void read_from_file(std:: string path)
          Point_2 vertex;
          vertex.first = stof(vrh1);
          vertex.second = stof(vrh2);
-         Vertices.push_back(vertex);
+         Vertices.push_back(vertex); numberOfGuards[vertex] = 0;
 
         //izdvjanje skupa tacaka koje se vide iz tog vrha
 
@@ -432,7 +432,7 @@ void read_from_file(std:: string path)
          tacka.first = stof(x);
          tacka.second = stof(y);
 
-        vertexSet.insert(tacka); 
+        vertexSet.insert(tacka); numberOfGuards[tacka] =  0;
         /*if(pointDPMapping.find( tacka ) == pointDPMapping.end() )
         {
            pointDPMapping[ tacka ] = indeksiranje; 

### 2020-09-23 doc/software/Heuristic/greedy.cpp
update

@@ -219,14 +219,7 @@ void updateCoveredPointsAdd(set<Point_2>& CovPoints,map<Point_2,int> & noOfG, in
     for(Point_2 p : S[v]){
     	
        CovPoints.insert(p);
-        if (noOfG.find(p) == noOfG.end()){
-       		noOfG.insert(std::make_pair(p,1));//first guard which cover point p
-       		//cout<<++temp<<"  First time: "<<p<<endl;
-       	}
-       	else{
-       		//p was already covered
-	        noOfG.find(p)->second++;	
-       	}
+       noOfG.find(p)->second++;
    }
 
 }

### 2020-09-23 doc/software/Heuristic/greedy.cpp
update

@@ -224,33 +224,22 @@ void updateCoveredPointsAdd(set<Point_2>& CovPoints,map<Point_2,int> & noOfG, in
 
 }
 void updateCoveredPointsRemove(set<Point_2>& CovPoints,map<Point_2,int> & noOfG, int v){//we remove all points which are covered by v, when v is removed from solution
-    for(Point_2 p : S[v]){
+
+        for(Point_2 p : S[v]){
     	
-        if (noOfG.find(p) == noOfG.end()){
+           /*if (noOfG.find(p) == noOfG.end() || noOfG.find(p)->second <= 0){
         	cout<<"------------------ERROR:"<<p<<"  "<<noOfG.find(p)->second<<endl;
-        	//cin.get();
+        	cin.get();
         	return;
-        }
-       // cout<<"Tacka "<<p<<" pokrivena sa: "<< noOfG.find(p)->second<<endl;
-        if(noOfG.find(p)->second == 1)
-        {
-        		//only the guard v see p in the solution
-        		//remove from CovPoints and remove from noOfGuards
-        		CovPoints.erase(p);
-        		noOfG.erase(p);
-        		//cout<<"Point "<<p<< "is no longer covered"<<endl;
-        		
-        		
-		}
-		else
-		{
-			noOfG.find(p)->second--;//one guard less see p
-		}	
-       
-   }
-
+           }*/
+	   noOfG.find(p)->second--;//smanjujemo broj cuvara za 1
+	  if(noOfG.find(p)->second == 0)
+          {	
+	     CovPoints.erase(p);//tacka vise nije pokrivena, pa je brisemo iz liste pokrivenih tacaka
+	  }
+ 
+       }
 }
-
 
 /*create map structure <key, value> 
 key is a point from D(P), value is the vector of Polygon vertices which cover the key

### 2020-09-30 doc/paper.tex
update

@@
           \end{itemize}
+      Ties are broken by using  price-per-unit heuristic.
       \subsection{An improvement of Greedy Solution}
@@
       Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
-      The first configuration of neighbourhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t.
+      The first configuration of neighborhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t.
 value $obj(;)$.
 
-      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$.
+      %Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$.
 Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.
@@
         \end{enumerate}
+      \begin{comment}
 
@@
        	    \begin{align}
-       	       ratio(i) = \frac{\sum_{v \in V, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
+       	       ratio(i) = \frac{\sum_{v \in V\setminus{ \{i\}}, j \in V(i)} 1_{j \mbox{ is veasible from } v} }{|V(i)|}. 
        	    \end{align}
        \end{itemize}
+      \end{comment}
 

### 2020-10-01 doc/paper.tex
polishing + questions

@@
 So, the task of OAPG becomes finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
-     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ The Integer Programming model for the Set Cover problem is known, and is as follows:
+     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ The IP  model for the Set Cover problem is well-known, and based on it the following model
      \begin{align}
@@
       presents a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
-     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem.
+     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discrete relaxation $D$ of the polygon.
      Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
 
-     If we want to add weights into the OAGP problem such that all guard have no equal weight (of 1), we obtained the weighted variant of OAGP, that is the WOAGP problem.
-This can be augmented that the prices of cameras do not need to be equal and these prices might be different due to the quality (of the range) of the cameras that are installed at some specific corners.
-Let us suppose that for any guard $p_i$ we assign a price $w_i$, $i=1,...,n$.
+     If we want to add weights into the OAGP problem such that all guards have no equal weight (of 1), we obtained the weighted variant of OAGP, labelled by WOAGP problem.
+Introducing prices into the basic problem can be augmented by the fact that the prices of cameras do not need to be equal and these prices might be different due to the quality (respecting the range of spectrum of view) of the cameras that are installed at some specific corners.
+Let us suppose that for any guard $p_i$, we assign a price $w_i>0$, $i=1,...,n$.
 Then, the above model is may be extended to its weighted version where the objective function has to be replaced by
@@
 
-      In order to solve this model, we propose to use a general purpose solver \textsc{Cplex}.
+      In order to solve this model, we use a general purpose solver \textsc{Cplex}.
      \section{Algorithmic Approaches for WOAGP}
-          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to apply greedy algorithms to solve WOAGP.
+          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance \fxerror{TODO: Milan treba da ovo objasni (proces transformacije -- neka uzme citavu jednu pod-sekciju za ovo...) }and then
+          apply greedy algorithms to solve WOAGP.
 These algorithms produce a solution of reasonable quality within a short interval of time.
-Efficient of greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, that is partial) solution to complete one.
-Among all candidates ( solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value etc.
-until the solution is complete (i.e., cover all regions of the polygon).
-          Pseudocode of Greedy heuristic is given in Algorithm~\ref{alg:greedy}
+Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
+Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
+          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}
 
@@
           \end{algorithm}
-      \subsection{Greedy Heuristic based on Price-per-Unit}
-       Our greedy criterion to expand current partial solution $s^P$  is based on the WOAGP characteristics, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$.
-For each not yet considered guards $p_i$, we assign the region he is able to see by $S_{p_i}$.
-As the next candidate to extend $s^P$, we choose not-yet-considered guard $p^*$ which is able to cover his part $S_{p_i}$ by smallest price per unit, among the other not considered guards.
+      \subsection{Greedy Criterion based on Price-per-Unit}
+       This greedy criterion to extend current partial solution $s^P$  is based on exploiting the characteristics of the  WOAGP, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$.
+For each not yet considered guards $p_i$, we assign the region which is able to see by $S_{p_i}$.
+As the next candidate to extend $s^P$, we choose that guard $p^*$ which is able to cover set $S_{p_i}$ by smallest price per unit, among the other not considered guards.
 More precisely, greedy criterion $g$ is given as:
@@
        and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
-       Afterwards the region $S_{p^*}$ is further then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and update $s^p= s^p \cup \{p^*\}$.
+       Afterwards, the region $S_{p^*}$ is then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and we update $s^p= s^p \cup \{p^*\}$.
 These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (polygon $P$ is covered by the guards from $s^P$).
 
-       The best WSC problem greedy heuristic known from the literature was based on the following greedy heuristic:
+       Concerning the literature for WSC problem (\fxnote{citirati}), the most known greedy heuristic was based on the following greedy heuristic:
        \begin{align}
@@
       One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
-      and the other sets $S_{p_j}$, $j \neq i$ as follow:
+      and the other sets $S_{p_j}$, $j \neq i$ as follow (\fxerror{Izbaciti ovaj kriterij}):
       \begin{align}\label{eq:intersection-heuristic}
@@
 
-        \subsection{An Alternative Greedy Heuristic}
-        \fxnote{TODO: work in progress...} Greedy criterion:
-          \begin{itemize}
-          	\item prefer those guards with a smaller cost $w_i$;
-          	\item If there are more guards with the smallest cost,
-          	prefer one with the largest $S_{p_i}$.
-          \end{itemize}
-		\fxnote{TODO: work in progress...} Another approach DRAGAN:
+        \subsection{An Novel Greedy Heuristic}
+          We proposed greedy criterion based on the following steps::
            \begin{itemize}
 			\item introduce a penalty function
-          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
+          	\item introduce a term ``incorrect point''. For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
+			\item let $incorrect_{total}$ be the total number of incorrect points from discretization $D(P)$
 			\item let $w_{total}$ be the total sum of all weights among all verteces
@@
           \end{itemize}
-      Ties are broken by using  price-per-unit heuristic.
+      Ties occurred in the search are broken by using  price-per-unit heuristic.
       \subsection{An improvement of Greedy Solution}
-      Local search and Large Neighborhood search \fxnote{TODO...}
+      Local search and Large Neighborhood search \fxnote{TODO: izbaciti ovo!}
       Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
@@
 
-      %Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$.
-Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.
-
-      \subsection{Hybrid of the Greed Heuristic and Local Search}
+      \subsection{Hybrid of the Greed Heuristic and Local Search}\fxnote{TODO: izbaciti i ovo!}
 
@@
     \end{comment}   
-
-    \subsection{Hybrid Greedy + CPLEX}
+    \subsection{A hybrid of the Greedy and shaking}
+    \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
+    \subsection{A Hybrid of the Greedy + CPLEX}
         CPLEX will soon or later degrade in its performance w.r.t.

### 2020-10-01 doc/paper.tex
polishing + questions

@@
     \subsection{A Hybrid of the Greedy + CPLEX}
-        CPLEX will soon or later degrade in its performance w.r.t.
+        CPLEX will soon or later degrades its performance w.r.t.
 instance size.
 On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.
-So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete.
+So it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX up to completion of the partial solution.
 Our approach consists of the following steps:
         \begin{enumerate}
-        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
+        	\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|C| = K$); 
         	\item Take solution $C$ and make it complete via. CPLEX model. 
         	\begin{itemize}
-        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
+        		\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
         		\item we obtain a complete solution $C'$;

### 2020-10-02 doc/paper.tex
update
Novi paper.tex i paper.pdf

@@
-\documentclass[runningheads,a4paper]{llncs}
+\documentclass[runningheads,a4paper]{elsarticle}
 % vim: tw=0 wm=0
@@
     %\numberwithin{table}{1}
-    \mainmatter  % start of an individual contribution
+    %\mainmatter  % start of an individual contribution
 
     % first the title is needed
-    \title{Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem}
+    \title{On Solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization by greedy methods and their hybridizations}
 
     %
-    \author{--}
+  %  \author{--}
     %
 
-    \institute{%$^1$Institute of Logic and Computation, TU Wien,
+  %  \institute{%$^1$Institute of Logic and Computation, TU Wien,
     %Vienna, Austria,\\
@@
     %\url{http://www.springer.com/lncs}
-    }
-
+    %}
+    \begin{abstract}
+    In this paper...
+    \end{abstract}
     \maketitle
@@
 In the solution phase, the discretized instance is iteratively refined and solved, until the solution becomes viable.
+\subsection{Problem definition}
+
+\subsection{Main contributions}
+The main contributions of this paper are:
+\begin{itemize}
+\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guard costs and the total number of uncovered points.
+\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others \fxnote{TODO: popraviti}
+\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP
+\item We considered different types of weights, based on a \fxnote{TODO}
+\end{itemize}
 
      \fxnote{TODO: work on literature approaches}
-     \section{Preliminaries}
+     %\section{Preliminaries}
+
+     \subsection{Discretization}\fxnote{TODO: Milan}
+
+     \section{Exact methods}\fxnote{TODO: Marko}
+     \subsection{Integer linear programming method}
      Solvers which solves IP model for OAGP problem are one of the most efficient techniques to approach this problem.
@@
       In order to solve this model, we use a general purpose solver \textsc{Cplex}.
+       \subsection{Constraint programming method}\fxnote{TODO: Marko}
+
      \section{Algorithmic Approaches for WOAGP}
+     \subsection{Greedy approaches for solving WOAGP}
+     \subsubsection{An existing greedy method}\fxnote{TODO: Milana}
           Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance \fxerror{TODO: Milan treba da ovo objasni (proces transformacije -- neka uzme citavu jednu pod-sekciju za ovo...) }and then
@@
           \end{algorithm}
-      \subsection{Greedy Criterion based on Price-per-Unit}
+    %  \subsection{Greedy Criterion based on Price-per-Unit}
+    \fxnote{TODO: izbaciti ovo!}
        This greedy criterion to extend current partial solution $s^P$  is based on exploiting the characteristics of the  WOAGP, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$.
@@
 
-        \subsection{An Novel Greedy Heuristic}
-          We proposed greedy criterion based on the following steps::
+        \subsubsection{An Novel Greedy Heuristic}\fxnote{TODO: Dragan}
+        In this subsection we present a novel greedy function, which is used in the greedy algorithm.
+Let us introduce a term  ``incorrect point''.
+For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
+Let $incorrect_{total}$ be the total number of incorrect points from discretization $D(P)$ for the current partial solution and let $w_{total}$ be the total sum of all weights among all vertices.
+Then, the greedy function for the given partial solution $s^{ps}$ and the guard $v$ is defined as:
+        \begin{equation}\label{eq:greedyfun2}
+				%$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
+				obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}\fxnote{moguce i skaliranje ove dvije vrijednosti?}
+		\end{equation}	
+            From Equation (\ref{eq:greedyfun2}) one can see that the greedy function mainly depends on the second term, since the value of the first one is not greater than 1.
+Other words, this function prefers such guards  whose inclusion in the partial solution more points will be covered.
+On the other side, if the inclusion of some two guards covers the same number of points, then the function suggest  the guard with lower cost.
+In the early stage of the greedy algorithm this approach enables that the guards which covers more points are preferable, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
+
+            In the Equation.. the trade off between two terms is more balanced. In this case, the algorithm do not prefer ultimately 
             \begin{itemize}
-			\item introduce a penalty function
-          	\item introduce a term ``incorrect point''. For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-			\item let $incorrect_{total}$ be the total number of incorrect points from discretization $D(P)$
-			\item let $w_{total}$ be the total sum of all weights among all verteces
-			\item involve the penalty function in the objective function
-				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
-				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
+
 \item start Greedy with empty solution
@@
       Ties occurred in the search are broken by using  price-per-unit heuristic.
-      \subsection{An improvement of Greedy Solution}
-      Local search and Large Neighborhood search \fxnote{TODO: izbaciti ovo!}
-      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
-      The first configuration of neighborhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t.
-value $obj(;)$.
-
-      \subsection{Hybrid of the Greed Heuristic and Local Search}\fxnote{TODO: izbaciti i ovo!}
+     \subsubsection{Partial calculation of objective function}
+      \subsection{Hybrids of the Greedy algorithm}
 
@@
     \end{comment}
-    \subsection{A hybrid of the Greedy and shaking}
+    \subsubsection{A hybrid of the Greedy and shaking}
     \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
-    \subsection{A Hybrid of the Greedy + CPLEX}
+    \subsubsection{A Hybrid of the Greedy + CPLEX}
         CPLEX will soon or later degrades its performance w.r.t.
@@
             \item return $f(C')$.
-        \end{enumerate}
+        \end{enumerate}\fxnote{TODO: Mozemo li uciti iz uzimanja nekih parcijalnih rjesenja koja komponenta je bolja, a koja nije?}
       \begin{comment}

### 2020-10-02 doc/paper.tex
paper polishing

@@
 \item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP
-\item We considered different types of weights, based on a \fxnote{TODO}
+\item We considered different types of weights, based on a... \fxnote{TODO}
 \end{itemize}
@@
 
-     \subsection{Discretization}\fxnote{TODO: Milan}
+     \subsection{Discretization}  \fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
+Proces transfomracije objasniti kratko (mozda i pseudokod ako je moguce da se prikaze)...
+}
 
@@
      \subsubsection{An existing greedy method}\fxnote{TODO: Milana}
-          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance \fxerror{TODO: Milan treba da ovo objasni (proces transformacije -- neka uzme citavu jednu pod-sekciju za ovo...) }and then
+          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
           apply greedy algorithms to solve WOAGP.
@@
     %  \subsection{Greedy Criterion based on Price-per-Unit}
-    \fxnote{TODO: izbaciti ovo!}
-       This greedy criterion to extend current partial solution $s^P$  is based on exploiting the characteristics of the  WOAGP, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$.
-For each not yet considered guards $p_i$, we assign the region which is able to see by $S_{p_i}$.
-As the next candidate to extend $s^P$, we choose that guard $p^*$ which is able to cover set $S_{p_i}$ by smallest price per unit, among the other not considered guards.
-More precisely, greedy criterion $g$ is given as:
-       \begin{align}
-            g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
-       \end{align}
-       and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
-       Afterwards, the region $S_{p^*}$ is then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and we update $s^p= s^p \cup \{p^*\}$.
-These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (polygon $P$ is covered by the guards from $s^P$).
-
-       Concerning the literature for WSC problem (\fxnote{citirati}), the most known greedy heuristic was based on the following greedy heuristic:
+      Concerning the literature for WSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
      \begin{align}
@@
      where $f(s^p) = |\bigcup_{s \in s^p} s |$.
+     This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.
 
-      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and
-      and the other sets $S_{p_j}$, $j \neq i$ as follow (\fxerror{Izbaciti ovaj kriterij}):
-      \begin{align}\label{eq:intersection-heuristic}
-      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
-      \end{align}
-      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two
-      visible regions.
-If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard.
-So, based on it, we always try to  add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc.
-to formula~(\ref{eq:intersection-heuristic})
-
-        \subsubsection{An Novel Greedy Heuristic}\fxnote{TODO: Dragan}
+        \subsubsection{A Novel Greedy Heuristic}\fxnote{TODO: Dragan}
         In this subsection we present a novel greedy function, which is used in the greedy algorithm.
@@
 For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-Let $incorrect_{total}$ be the total number of incorrect points from discretization $D(P)$ for the current partial solution and let $w_{total}$ be the total sum of all weights among all vertices.
+Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution and let $w_{total}$ be the total sum of all weights among all vertices.
 Then, the greedy function for the given partial solution $s^{ps}$ and the guard $v$ is defined as:
@@
 				%$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
-				obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}\fxnote{moguce i skaliranje ove dvije vrijednosti?}
+				obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
 		\end{equation}	
             From Equation (\ref{eq:greedyfun2}) one can see that the greedy function mainly depends on the second term, since the value of the first one is not greater than 1.
-Other words, this function prefers such guards  whose inclusion in the partial solution more points will be covered.
+On other words, this function prefers such guards  which inclusion in the partial solution will cover more points.
 On the other side, if the inclusion of some two guards covers the same number of points, then the function suggest  the guard with lower cost.
@@
 
-            In the Equation.. the trade off between two terms is more balanced. In this case, the algorithm do not prefer ultimately 
+            In the Equation.. the trade off between two terms is more balanced. In this case, the algorithm do not prefer ultimately \fxnote{TODO...}
             \begin{itemize}
@@
           \end{itemize}
-      Ties occurred in the search are broken by using  price-per-unit heuristic.
+      Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows. 
+       For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $S(p_j)$.
+As the next candidate to extend $s^P$, we choose a guard $p^*$ which covers set $V(j)$ by smallest price per unit, among the other candidate to extend $s^P$.
+More precisely, greedy criterion $g$ is given as:
+      \begin{align}
+      g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
+      \end{align}
+      and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
+      In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics.
      \subsubsection{Partial calculation of objective function}
-      \subsection{Hybrids of the Greedy algorithm}
 
-       In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method.
-       The pseudocode is given in Algorithm~\ref{alg:hybrid-ls-greedy}.
-        \begin{algorithm}[!t]
-       	\caption{Local Search + Greedy}\label{alg:hybrid-ls-greedy}
-       	\begin{algorithmic}
-       		   	\State \textbf{Input:} and Instance of the problem; $pct\in (0,1)$:percentage
-       		    \State \textbf{Output:} a complete solution $s$
-       		    \State $s_{greedy} \gets \emptyset$
-       		    \While{ $s_{greedy}$ is not complete}
-       		        \State $s_{greedy} \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot pct \rfloor$ guards
-       		        \State $s_{greedy} \gets$ LS($s_{greedy}$)
-       		    \EndWhile
-       \end{algorithmic}
-       \end{algorithm}
-
-       \begin{algorithm}[!t]
-      	\caption{Local Search}\label{alg:local-search}
-      	\begin{algorithmic}[1]
-      		\State \textbf{Input:} a (partial) solution $s_{greedy}=\{v_1,...,v_k\}$, $iter_{allow}>0., $ probability $p$
-      		\State \textbf{Output:} and improved solution $s$
-      		\While{$iter < iter_{allow}$}
-      		     \State $D(P)_s$ the number of points covered by $s_{greedy}$
-      		      \If{$|D(P)_s| == |D(P)|$} // a complete solution
-      		          \State return $s_{greedy}$
-      		      \EndIf
-      		     \State choose random vertex $v_{i'}$ from $s_{greedy}$
-      		     \State $v_{i''},v_{i'''} \gets$ two neighbor vertices of vertex  $v_{i'}$
-      		     \State $s^1_{greedy} \gets$ $s_{greedy} \cup \{v_{i''} \} \setminus \{v_{i'}\}$
-                 \State $s^2_{greedy} \gets$ $s_{greedy} \cup \{v_{i'''} \} \setminus \{v_{i'}\}$
-      		      \If{$|D(P)_{s^1_{greedy}}|>|D(P)_{s_{greedy}}|$ }
-                        \State $s_{greedy} \gets s^1_{greedy}$
-      \EndIf
-                    \If {$|D(P)_{s^1_{greedy}}|==|D(P)_{s_{greedy}}|$ }
-                        \State $s_{greedy} \gets s^1_{greedy}$ with probability $p$
-
-      		      \EndIf
-      		       \If{$|D(P)_{s^2_{greedy}}|>|D(P)_{s_{greedy}}|$ }
-                        \State $s_{greedy} \gets s^2_{greedy}$
-      		      \EndIf
-
-            \If {$|D(P)_{s^2_{greedy}}|==|D(P)_{s_{greedy}}|$ }
-                        \State $s_{greedy} \gets s^2_{greedy}$ with probability $p$
-                    \EndIf
-      		     \State $iter \gets iter +1 $
-      		\EndWhile
-      		 \State return $s_{greedy}$
-      	\end{algorithmic}
-      \end{algorithm}
-    \begin{comment}
-
-     \subsection{Beam Search (BS)}
-        Beam Searxh is an incomplete BFS heuristic search algorithm.
-At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$.
-all nodes are then expanded in all possible ways.
-Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level.
-        The search is processed in the same manner until $B$ is empty.
-The main question concerns of the criterion of choosing the nodes for a beam.
-This is done by means of a heuristic evaluation of the nodes.
-The heuristic is a problem-specific aspect of each problem that is considered for solving.
-\fxnote{work in progress...}
-    \end{comment}
     \subsubsection{A hybrid of the Greedy and shaking}
@@
             \item return $f(C')$.
-        \end{enumerate}\fxnote{TODO: Mozemo li uciti iz uzimanja nekih parcijalnih rjesenja koja komponenta je bolja, a koja nije?}
+        \end{enumerate}
+
       \begin{comment}

### 2020-10-02 doc/paper.tex
some re-phrasing and comments

@@
 This problem was stated by Victor  Klee in 1973.~\cite{o1987art}.
-The problem is motivated from installing the cameras in a building (or gallery) such that the whole surface of the building is covered.
-Orthogonality constraint naturally comes out from the orthogonality of the walls in a building.
+The problem is motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
+Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings.
 
@@
 Actually, we are looking for minimum vertex guards needed to cover an orthogonal polygon.
-This problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.
+This restricted problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.
 
-     By discretization $D(P)$ the set of points of the polygon $P$, the art gallery problem can be reduced to the well-known Min Set Cover Problem.
-For each vertex of the polygon $P$, a set of points of visibility is determined.
-On that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets.
+     By discretization $D(P)$ the set of points of the polygon $P$, the art gallery problem can be reduced to the well-known Min Set Cover Problem.\fxnote{Marko: ovdje fali motivacija zasto radimo diskretizaciju poligona} For each vertex of the polygon $P$, a set of points of visibility is determined.
+In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets.
 
      In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal, is presented for simple polygon with $n$ vertices.
-Firstly, this algorithm partition the polygonal region into convex components and construct sets consisting of these convex components.
+Firstly, this algorithm do a partitioning the polygonal region into convex components and construct sets consisting of these convex components.
 After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the Minimum set-covering problem (MSC) is applied to get solution.
@@
 In the solution phase, the discretized instance is iteratively refined and solved, until the solution becomes viable.
+\fxnote{Marko: ja bih ovdje samo rekao:  Couto et al.
+an efficient exact algorithm  for OAGP  based on preprocessing and refinement phases of the the discretized instance.
+}
 \subsection{Problem definition}
@@
 \begin{itemize}
-\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guard costs and the total number of uncovered points.
-\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others \fxnote{TODO: popraviti}
+\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
+\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others based on a distance measure.\fxnote{TODO: popraviti}
 \item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP
-\item We considered different types of weights, based on a... \fxnote{TODO}
+\item We considered different types of weights for our benchmarks, based on a... \fxnote{TODO}
 \end{itemize}

### 2020-10-03 doc/paper.tex
rad na tekstu

@@
      \subsection{Greedy approaches for solving WOAGP}
-     \subsubsection{An existing greedy method}\fxnote{TODO: Milana}
       Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
@@
           \end{algorithm}
+     \subsubsection{An existing greedy method}\fxnote{TODO: Milana}
+
     %  \subsection{Greedy Criterion based on Price-per-Unit}
@@
 For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution and let $w_{total}$ be the total sum of all weights among all vertices.
-Then, the greedy function for the given partial solution $s^{ps}$ and the guard $v$ is defined as:
+Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
+Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be total number of discretization set.
+The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution if $v$ is included in it and the total number of incorrect points, given by the formula:
         \begin{equation}\label{eq:greedyfun2}
-				%$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
-				obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
+				%$$obj(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}$$ 
+				g(s^{ps}; v) = \alpha \cdot \sum_{i \in s^{ps} \cup \{v\}} w_i+ \beta \cdot {incorrect_{total}}
 		\end{equation}
-            From Equation (\ref{eq:greedyfun2}) one can see that the greedy function mainly depends on the second term, since the value of the first one is not greater than 1.
+where $\alpha$ and $\beta$ are positive real parameters.
+
+            Although many combination of parameters $ \alpha $ and $\beta$ may be used, in our investigation we used parameter $\alpha$  only to normalize the sum of prices, i.e.
+$\alpha = \frac{1}{w_{total}}$ and two values for $\beta$: $\beta = 1$ and $\beta = \frac{1}{|D(P)|}$.
+Thus, we consider two variants of the greedy function:
+                    \begin{equation}\label{eq:greedyfun3}
+				g_2(s^{ps}; v)  =  \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}
+		\end{equation}
+and 
+        \begin{equation}\label{eq:greedyfun4}
+				g_3(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
+		\end{equation}
+            From Equation (\ref{eq:greedyfun3}) one can see that the greedy function $g_2$ mainly depends on the second term, since the value of the first one is not greater than 1.
 On other words, this function prefers such guards  which inclusion in the partial solution will cover more points.
@@
 
-            In the Equation.. the trade off between two terms is more balanced. In this case, the algorithm do not prefer ultimately \fxnote{TODO...}
+            In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
+            In this case, the algorithm does not  ultimately prefer any of criteria\fxnote{TODO...}
             \begin{itemize}
@@
     \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
+
     \subsubsection{A Hybrid of the Greedy + CPLEX}

### 2020-10-03 doc/paper.tex
work on section 2.1

@@
      \subsection{Integer linear programming method}
-     Solvers which solves IP model for OAGP problem are one of the most efficient techniques to approach this problem.
-It is known that the problem is related to the known Minimal-Set-Cover (MSC) problem.
-
-     Let us suppose we are given a discretization $D(P)$ of the polygon $P$ (with a family of rectangles). Then we relate the OAGP with the known MSC problem.
-     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets is given as: $S_i \in \mathcal{F}$ iff it includes any point from $D(P)$ which is visible from guard $i\in V$.
-Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $j\in V$, $i \neq j$.
-So, the task of OAPG becomes finding a minimal cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of set $D(P)$, that is
-     $$ \bigcup_{c \in \mathcal{C}} c = D(P).$$ The IP  model for the Set Cover problem is well-known, and based on it the following model
+     Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
+Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized.
+     The problem is related to the known Minimal Weighted Set-Cover (MWSC) problem. 
+     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets consists of sets
+      $S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.
+Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$.
+In this was, the task is equivalent of  finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+     $$ \bigcup_{C \in \mathcal{C}} C = D(P).$$ The IP  model for the Weighted Set Cover problem is well-known in the literature, and is here adapted for our task as follows:
      \begin{align}
-        &\sum_{i=1}^n x_i \longrightarrow \min \\
+        &\sum_{i=1}^n w_ix_i \longrightarrow \min \\
         &\mbox{s.t.} \\
@@
      and $x_i = \begin{cases}
-     	 1, \mbox{ if } \mbox{ the point } i \in \mathcal{C},\\
+     	 1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
      	 0, \mbox{otherwise},
      \end{cases}$ \\
-      presents a MIP model to solve OAGP where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
-     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discrete relaxation $D$ of the polygon.
+      where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
+     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
      Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
 
-     If we want to add weights into the OAGP problem such that all guards have no equal weight (of 1), we obtained the weighted variant of OAGP, labelled by WOAGP problem.
-Introducing prices into the basic problem can be augmented by the fact that the prices of cameras do not need to be equal and these prices might be different due to the quality (respecting the range of spectrum of view) of the cameras that are installed at some specific corners.
-Let us suppose that for any guard $p_i$, we assign a price $w_i>0$, $i=1,...,n$.
-Then, the above model is may be extended to its weighted version where the objective function has to be replaced by
-     $$ \sum_{i} x_i w_i,$$
-      and all other constraints remain the same.
+    Introducing the prices into the basic problem can be augmented by the fact that prices of cameras are usually not equal and they are related to their quality (respecting the range of spectrum of view) or due to the fact that installing cameras at some specific corners is much harder than to some other areas.
 
-      In order to solve this model, we use a general purpose solver \textsc{Cplex}.
+      In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
        \subsection{Constraint programming method}\fxnote{TODO: Marko}

### 2020-10-03 doc/paper.tex
Section 2
description of benchmarks

@@
       In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
-       \subsection{Constraint programming method}\fxnote{TODO: Marko}
-
+       \subsection{Constraint programming method} An equivalent CP model was implemented and tested by CP Optimizer. In this case,  Constraint~(\ref{eq:const-3}) is transformed into 
+       \begin{equation}
+           \bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1, 
+       \end{equation}
+      whereas the other constraints and the objective function are the same like in the above MIP model. 
      \section{Algorithmic Approaches for WOAGP}
@@
      \section{Computational Results}
-       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
+       We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
        \begin{itemize}
-       	  \item \emph{random benchmarks}.
-For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$  as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
        	  \item \emph{topologically-based benchmarks}.
@@
 This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
-       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon).
-       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$.
-Based on this measure, we assign prices to the vertices.
-If |V(j)| is larger, the large is the price of the vertex $j$.
+       	 \item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
+Based on this number, we assign prices to the vertices on the following way:
+       	 \begin{equation}
+       	   w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n. 
+       	 \end{equation}
        \end{itemize}

### 2020-10-04 doc/software/milan/pretprocesiranje.cpp
dodao motivaciju

@@ -408,8 +408,8 @@ Traits_2::FT area_set_polygons(Polygon_set_2 S)
 
 int main(int argc, char const *argv[])
 {
-  for(int file_number=2250; file_number<2251; file_number+=2) // start = 8
-  for(int file_order=1; file_order<=3; file_order++) // file_order<=file_number
+  for(int file_number=2500; file_number<2501; file_number+=2) // start = 8
+  for(int file_order=2; file_order<=3; file_order++) // file_order<=file_number
   {
     const string category = "random-big";
     string filename = "random-" + std::to_string(file_number) + "-" + std::to_string(file_order);

### 2020-10-04 doc/paper.tex
update
dodao motivaciju

@@
     \section{Introduction}\label{sec:introduction}
-     \emph{The Orthogonal Art Gallery Problem} (OAGP) is one of many variants of Art Gallery Problem (AGP).
-AGP asks for a set of points $G$ of minimal cardinality on some polygon $P$ such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
+
+    For a given polygon $P$, Art Gallery Problem (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
+We say that the point $y$ is covered by the point $x$, or $y$ is visible from $x$.
 Set $G$ is called guard set of $P$ and the points from $G$ as guards.
-The orthogonal AGP consider on arbitrary polygon but whose angles are $90^{\circ}$ and $270^{\circ}$.
-This problem was stated by Victor  Klee in 1973.~\cite{o1987art}.
-The problem is motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
+In \emph{The Orthogonal Art Gallery Problem} (OAGP) edges of the polygon are only horizontal and vertical, i.e.
+angles between adjacent edges are  $90^{\circ}$ or $270^{\circ}$.
+The original AGP was stated by Victor  Klee in 1973.~\cite{o1987art}.
+The problem can be motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
 Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings.
-
 Kahn et al.
 in ~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.
-A variant of the OAGP for which we are interested in this study allows only that guards are positioned at the vertices of polygon $P$.
-Actually, we are looking for minimum vertex guards needed to cover an orthogonal polygon.
+In this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$.
 This restricted problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.
+In real situations (like installing the cameras in a building) , it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting the range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
+In Weighted Orthogonal Art Gallery Problem (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to all chosen vertices is minimal.
 
-     By discretization $D(P)$ the set of points of the polygon $P$, the art gallery problem can be reduced to the well-known Min Set Cover Problem.\fxnote{Marko: ovdje fali motivacija zasto radimo diskretizaciju poligona} For each vertex of the polygon $P$, a set of points of visibility is determined.
-In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets.
+     It is well known that AGP can be reduced to the Minimum Set Cover Problem (MSCP) by a discretization of the set of all points of the polygon $P$.
+The appropriate discretization should be performed in such a way that if each point from the discretized set $D(P)$ is covered, then the whole polygon $P$ is covered.
+After the discretization is made, for each vertex of the polygon $P$, a set of visible points from $D(P)$ is determined.
+In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets, which is MSCP.
+Analogously, WOAGP can be reduced to the Weighted Minimum Set Cover Problem (WMSCP).
 
-     In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal, is presented for simple polygon with $n$ vertices.
-Firstly, this algorithm do a partitioning the polygonal region into convex components and construct sets consisting of these convex components.
-After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the Minimum set-covering problem (MSC) is applied to get solution.
-
+     Couto et al.
+presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
+in ~\cite{couto2007exact}.
+In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal.
+After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the MSCP is applied.
 An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in ~\cite{tomas2003approximation}.
@@
 more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
-
 Tozoni et a.
 ~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact Integer linear programming  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
+Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
+Analysis of many greedy-like heuristic for the WMSCP was presented in \cite{vasko2016best}.
+More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
 
-More detailed overview of the results on art gallery problems is out the scope of this paper and can be found in a survey paper  ~\cite{ghosh2010approximation2}.
-
-    Couto et al.
-presented an exact and efficient algorithm for the Orthogonal Art Gallery Problem in ~\cite{couto2007exact}.
-The algorithm is divided into two phases.
-In the preprocessing phase an initial discretization is constructed and the Integer Programming model for solving MSC is applied.
-In the solution phase, the discretized instance is iteratively refined and solved, until the solution becomes viable.
-\fxnote{Marko: ja bih ovdje samo rekao:  Couto et al.
-an efficient exact algorithm  for OAGP  based on preprocessing and refinement phases of the the discretized instance.
-}
 \subsection{Problem definition}
+\fxnote{TODO: Ovo mozda sad i ne treba?}
 
@@
 \item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
-\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others based on a distance measure.\fxnote{TODO: popraviti}
-\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP
-\item We considered different types of weights for our benchmarks, based on a... \fxnote{TODO}
+\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others, where the replacement is based on measuring  distances between points in the polygon.\fxnote{TODO: popraviti}
+\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP.
+\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
+\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested and analysed.
 \end{itemize}
-
-     \fxnote{TODO: work on literature approaches}
-     %\section{Preliminaries}
 
@@
      \section{Exact methods}\fxnote{TODO: Marko}
+     In this section we present the known exact ILP and constraint programming (CP) methods for solving WMSCP, which are used  in the rest of the paper.
      \subsection{Integer linear programming method}
@@
 
-    Introducing the prices into the basic problem can be augmented by the fact that prices of cameras are usually not equal and they are related to their quality (respecting the range of spectrum of view) or due to the fact that installing cameras at some specific corners is much harder than to some other areas.
-
       In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
@@
       whereas the other constraints and the objective function are the same like in the above MIP model.
+Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and domain filtering~\ref{}.
      \section{Algorithmic Approaches for WOAGP}
      \subsection{Greedy approaches for solving WOAGP}
-      Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
+      Since the WOAGP can be seen as the WMSCP and since the best known heuristics to solve WSCP is an enhanced greedy heuristic \fxnote{Marko, treba nam referenca da je greedy najbolja heuristika}, our idea is to transform a WOAGP instance into a WSC problem instance and then
           apply greedy algorithms to solve WOAGP.
@@
     %  \subsection{Greedy Criterion based on Price-per-Unit}
-      Concerning the literature for WSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
+      Concerning the literature for WMSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
      \begin{align}
@@
             In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
-            In this case, the algorithm does not  ultimately prefer any of criteria\fxnote{TODO...}
-            \begin{itemize}
+            In this case, the algorithm does not  ultimately prefer any of criteria for choosing next vertex. Instead,  \fxnote{TODO...}
 
-\item start Greedy with empty solution
-			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
-			\item end when $incorrect_{total}$ becomes 0
-          \end{itemize}
       Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows.
@@
      \subsubsection{Partial calculation of objective function}
+
+     In order to enable fast calculation of greedy functions described in previous subsections, we introduce several useful structures and auxiliary functions:
+      \begin{itemize}
+      \item structure \texttt{map<Point,list<Point>> Visibility} -- for each point, we provide the list od guards which see that point; 
+      \item structure \texttt{map<Point,int> numberOfGuards} -- for each point we keep the number of Guards in solution which see that point;
+       \item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
+       \item function \texttt{updateCoveredPointsAdd (vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution;
+       \item fucntion \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from solution.
+      \end{itemize}
 
@@
        \end{itemize}
+       \subsection{Results on exact methods}
+       ovo za cp i 5min, što je Marko pominjao
      \section{Conclusions and Future Work}

### 2020-10-04 doc/paper.tex
work on concept

@@
 	\subsection{Integer linear programming method}
-     Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
-Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized.
+	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized.
 	The problem is related to the known Minimal Weighted Set-Cover (MWSC) problem.
@@
 	\subsection{Greedy approaches for solving WOAGP}
-      Since the WOAGP can be seen as the WMSCP and since the best known heuristics to solve WSCP is an enhanced greedy heuristic \fxnote{Marko, treba nam referenca da je greedy najbolja heuristika}, our idea is to transform a WOAGP instance into a WSC problem instance and then
-          apply greedy algorithms to solve WOAGP.
+	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic \fxnote{Marko, treba nam referenca da je greedy najbolja heuristika}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP.
 These algorithms produce a solution of reasonable quality within a short interval of time.
@@
 
-    \subsubsection{A Hybrid of the Greedy + CPLEX}
+	\subsubsection{A Hybrid of the Greedy + CPLEX} \fxnote{TODO: Marko}
 	CPLEX will soon or later degrades its performance w.r.t.
@@
 	\subsection{Results on exact methods}
-       ovo za cp i 5min, što je Marko pominjao
+\fxnote{Marko: Solving of CP i MIP solvers are limited to 5 mins. }
 	\section{Conclusions and Future Work}

### 2020-10-04 doc/paper.tex
def discretization and add pseudocode

@@
 
-	\subsection{Discretization}  \fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
+	\subsection{Discretization}  
+	The discretization $D(P)$ of the polygon $P$ is builded as follows.
+Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of P, where \\
+$ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
+$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
+
+	\begin{algorithm}[!t]
+		\caption{Discretization $D(P)$ of the polygon $P$}\label{alg:discret}
+		\begin{algorithmic}[1]
+			\State \textbf{Input:} The set of vertices V of the polygon $P$
+			\State \textbf{Output:} The discretization $D(P)$ of the polygon $P$
+			\State $BB \gets bounding\_box(P);$
+			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
+			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
+			\State $D(P) \gets D(BB) \cap P;$
+			\State $D(P) \gets D(P) \cup V;$
+		\end{algorithmic}
+	\end{algorithm}
+
+	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+
+	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenssti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
+
+	\fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
 Proces transfomracije objasniti kratko (mozda i pseudokod ako je moguce da se prikaze)...

### 2020-10-05 doc/paper.tex
concept: text polishing

--- 2020-10-04 doc/paper.tex
@@
 	% first the title is needed
-	\title{On Solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization by greedy methods and their hybridizations}
+	\title{Measuring efficiency of the greedy-like heuristics for solving  the Weighted Orthogonal Art Gallery Problem under regular grid discretization}
 
@@
 
-	For a given polygon $P$, Art Gallery Problem (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
+	For a given polygon $P$, \emph{Art Gallery Problem} (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
 We say that the point $y$ is covered by the point $x$, or $y$ is visible from $x$.
-Set $G$ is called guard set of $P$ and the points from $G$ as guards.
-In \emph{The Orthogonal Art Gallery Problem} (OAGP) edges of the polygon are only horizontal and vertical, i.e.
-angles between adjacent edges are  $90^{\circ}$ or $270^{\circ}$.
+Set $G$ is called \emph{guard set} of $P$ and the points from $G$ as \emph{guards}.
+In \emph{The Orthogonal Art Gallery Problem} (OAGP) edges of the polygon are only horizontal and vertical w.r.t.
+the axis, i.e.
+the angles allowed between adjacent edges are  $90^{\circ}$ or $270^{\circ}$.
 The original AGP was stated by Victor  Klee in 1973.~\cite{o1987art}.
-The problem can be motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
+The problem might be motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
 Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings.
-Kahn et al.
-in ~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.
+Kahn et al.~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.
 In this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$.
-This restricted problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.
-In real situations (like installing the cameras in a building) , it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting the range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
-In Weighted Orthogonal Art Gallery Problem (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to all chosen vertices is minimal.
+This restricted problem is known to be $\mathcal{NP}$--hard~\cite{schuchardt1995two,katz2008guarding}.
+When comes to real situations (like installing the cameras in a building) , it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting the range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
+In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
 
-	It is well known that AGP can be reduced to the Minimum Set Cover Problem (MSCP) by a discretization of the set of all points of the polygon $P$.
+	It is well known that AGP can be reduced to \emph{the Minimum Set Cover Problem} (MSCP) by a discretization of the set of all points of the polygon $P$.
 The appropriate discretization should be performed in such a way that if each point from the discretized set $D(P)$ is covered, then the whole polygon $P$ is covered.
@@
 In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets, which is MSCP.
-Analogously, WOAGP can be reduced to the Weighted Minimum Set Cover Problem (WMSCP).
+Analogously, WOAGP can be reduced to the \emph{Weighted Minimum Set Cover Problem} (WMSCP).
 
-	Couto et al.
-presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
-in ~\cite{couto2007exact}.
+	Concerning the exact and heuristic techniques to solve AGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
 In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal.
@@
 	Tozoni et a.
-~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact Integer linear programming  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
+~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact \emph{Integer Linear Programming}  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
-	Analysis of many greedy-like heuristic for the WMSCP was presented in \cite{vasko2016best}.
+	A comprehensive analysis of many greedy-like heuristic for the WMSCP was presented in \cite{vasko2016best}.
 	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
-
-	\subsection{Problem definition}
-	\fxnote{TODO: Ovo mozda sad i ne treba?}
 
@@
 		\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
-		\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested and analysed.
+		\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested, analysed, and their efficiency checked.
+The methods are then compared to the exact approaches ILP and \emph{Constraint Programming} (CP).
 	\end{itemize}
@@
 	\section{Exact methods}\fxnote{TODO: Marko}
-	In this section we present the known exact ILP and constraint programming (CP) methods for solving WMSCP, which are used  in the rest of the paper.
+	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP, which are used  in the rest of the paper.
 	\subsection{Integer linear programming method}
-	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized.
-	The problem is related to the known Minimal Weighted Set-Cover (MWSC) problem.
-	Family $\mathcal{F}\subseteq D(P)$ of nonempty sets consists of sets
+	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
+The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
+	The problem is related to the known MWSC problem.
+	Family $\mathcal{F}$ of nonempty sets consists of sets
 	$S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.
 Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$.
-In this was, the task is equivalent of  finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
-	$$ \bigcup_{C \in \mathcal{C}} C = D(P).$$ The IP  model for the Weighted Set Cover problem is well-known in the literature, and is here adapted for our task as follows:
+To each set set $S_i$, a cost $c(S_i) = w_i$ is assigned.
+In this way, our starting task is then equivalent of finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+	$$ \bigcup_{C \in \mathcal{C}} C = D(P)$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
+The ILP  model for the WSCP is known from the literature, and is here adapted to WOAGP  as follows:
 	\begin{align}
@@
 
-	In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
-	\subsection{Constraint programming method} An equivalent CP model was implemented and tested by CP Optimizer. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
+	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
+	\subsection{Constraint programming method} An equivalent CP model was implemented and tested by ILOG IBM CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
 	\begin{equation}
@@
 	whereas the other constraints and the objective function are the same like in the above MIP model.
-Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and domain filtering~\ref{}.
+Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and variable domain filtering~\cite{laborie2018ibm}.
 	\section{Algorithmic Approaches for WOAGP}
 	\subsection{Greedy approaches for solving WOAGP}
-	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic \fxnote{Marko, treba nam referenca da je greedy najbolja heuristika}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP.
-These algorithms produce a solution of reasonable quality within a short interval of time.
+	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP.
+Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement.
 Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
-Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
+Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution until it is complete (i.e., it covers all  points from $D(P)$).
 	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}
@@
 			\While{$\text{Extend}(s^{P}) \neq \emptyset$}
-			\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
+			\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion $g$
 			\State Extend $s^{P}$ by $e$
@@
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the literature for WMSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
+	Concerning the literature for WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
 	\begin{align}
@@
 For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
-Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be total number of discretization set.
+Let us denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
+Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be the cardinality of discretization set.
 The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution if $v$ is included in it and the total number of incorrect points, given by the formula:
@@
 On other words, this function prefers such guards  which inclusion in the partial solution will cover more points.
-On the other side, if the inclusion of some two guards covers the same number of points, then the function suggest  the guard with lower cost.
-In the early stage of the greedy algorithm this approach enables that the guards which covers more points are preferable, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
+On the other side, if the inclusion of some two guards covers the same number of points, then the function suggests  the guard with lower cost.
+In the early stage of the greedy algorithm this approach will prefer those guards which covers more points of the not-yet-covered points from $D(P)$, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
 
@@
 	Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows.
-	For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $S(p_j)$.
-As the next candidate to extend $s^P$, we choose a guard $p^*$ which covers set $V(j)$ by smallest price per unit, among the other candidate to extend $s^P$.
-More precisely, greedy criterion $g$ is given as:
+	For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $Surf(v_j)$.
+As the next candidate to extend $s^P$, we choose a guard $v^*$ which covers set $V(j)$ by the smallest price per unit, among the other candidate to extend $s^P$.
+More precisely, this greedy criterion $g$ is given as:
 	\begin{align}
-	g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
+	g(s^p, v_i) = \frac{w_{i}}{|Surf({v_i})|},
 	\end{align}
-	and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
-	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics.
+	and vertex $v^*$ that minimizes $g(s^p, v_i)$ is chosen as an extension of the current partial solution.
+	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes~(\ref{eq:greedyfun3}) and (\ref{eq:greedyfun4}).
 	\subsubsection{Partial calculation of objective function}
@@
 	\begin{itemize}
-		\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point, we provide the list od guards which see that point; 
-		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point we keep the number of Guards in solution which see that point;
+		\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point; 
+		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of Guards in solution which are visible from that point;
 		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
 		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution;
-		\item fucntion \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from solution.
+		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
 	\end{itemize}
@@
 On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.
-So it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX up to completion of the partial solution.
+So, it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX to do the completion of the partial solution.
 Our approach consists of the following steps:
 	\begin{enumerate}
-		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|C| = K$);
-		\item Take solution $C$ and make it complete via. CPLEX model.
+		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|s^p| = K$);
+		\item Take solution $s^p$ and make it complete by solving a corresponding submodel via CPLEX:
 		\begin{itemize}
-			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
-			\item we obtain a complete solution $C'$;
+			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^p$ into the existing WOAGP model;
+			\item we obtain a complete solution $\bar {s^p}$;
 		\end{itemize}
-		\item return $f(C')$.
+		\item Return $f(\bar {s^p})$.
 	\end{enumerate}

### 2020-10-05 doc/paper.tex

@@
 
-	\subsection{Discretization}  \fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
+	\subsection{Discretization}  
+	The discretization $D(P)$ of the polygon $P$ is builded as follows.
+Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of P, where \\
+$ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
+$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
+
+	\begin{algorithm}[!t]
+		\caption{Discretization $D(P)$ of the polygon $P$}\label{alg:discret}
+		\begin{algorithmic}[1]
+			\State \textbf{Input:} The set of vertices V of the polygon $P$
+			\State \textbf{Output:} The discretization $D(P)$ of the polygon $P$
+			\State $BB \gets bounding\_box(P);$
+			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
+			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
+			\State $D(P) \gets D(BB) \cap P;$
+			\State $D(P) \gets D(P) \cup V;$
+		\end{algorithmic}
+	\end{algorithm}
+
+	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+
+	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenssti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
+
+	\fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
 Proces transfomracije objasniti kratko (mozda i pseudokod ako je moguce da se prikaze)...
 }
+>>>>>>> f0de2fe1c485200c1405558b9629e06f459b82e4
 

### 2020-10-05 doc/paper.tex
Section 1.2: fix and comments

@@
 $ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
-$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
+$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$. \fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm}
 
@@
 
-	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod?} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
 
-	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenssti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
-
-	\fxerror{TODO: Milan treba da ovo objasni proces transofrmacije, zasto uzimamo ovakav tip diskretizacije, kako se onda problem svodi na SC, da obajsni zasto diskretni grid ne mora dati potpunu pokrivenost poligona -- dvije slike.
-Proces transfomracije objasniti kratko (mozda i pseudokod ako je moguce da se prikaze)...
-}
->>>>>>> f0de2fe1c485200c1405558b9629e06f459b82e4
+	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
 

### 2020-10-05 doc/paper.tex
Section 1.2: a comment
update

@@
 $ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
-$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$. \fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm}
+$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
+\fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm, min je naredba u latexu  "min", mjesto $"|"$ korisititi naredbu "mid" }
 
@@
 
-	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod?} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod?
+Referisi u odnosu na Pseudokod} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
 
-	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
+	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
 

### 2020-10-05 doc/paper.tex
more comments

@@
 $ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
-\fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm, min je naredba u latexu  "min", mjesto $"|"$ korisititi naredbu "mid" }
+\fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm, min je naredba u latexu  "min", mjesto $"|"$ korisititi naredbu "mid"; koristis nedefinisane simbole $u_x$ i $u_y$ }
 
@@
 
-	\section{Exact methods}\fxnote{TODO: Marko}
+	\section{Exact methods}
 	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP, which are used  in the rest of the paper.
-	\subsection{Integer linear programming method}
+	\subsection{Integer linear programming model}
 	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
@@
 	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
-	\subsection{Constraint programming method} An equivalent CP model was implemented and tested by ILOG IBM CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
+	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by ILOG IBM CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
 	\begin{equation}
@@
 	\end{itemize}
+     We used three different kind of benchmarks:
+     \begin{itemize}
+     	\item \emph{random} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
+     	\item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
+     	\item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
+     \end{itemize}
 	\subsection{Results on exact methods}

### 2020-10-05 doc/paper.tex
work on Computational section

@@
 	\end{itemize}
-     We used three different kind of benchmarks:
+     We used three different kind of benchmark sets:
      \begin{itemize}
@@
      \end{itemize}
+     Fro small and large instances, one polygon with $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set.
+For random set, we took a subset of 200 instances.
+In overall, we have 400 polygons which vertices are weighted by two different weights, which gives us, in overall, 800 instances.
 	\subsection{Results on exact methods}

### 2020-10-06 doc/paper.tex

@@
 	The discretization $D(P)$ of the polygon $P$ is builded as follows.
-Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of P, where \\
-$ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
-$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$.
-\fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm, min je naredba u latexu  "min", mjesto $"|"$ korisititi naredbu "mid"; koristis nedefinisane simbole $u_x$ i $u_y$ }
+Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of $P$, where \\
+$ \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\}$ and\\
+$ \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\}$,\\
+where $ (u_{x},u_{y}),(v_{x},v_{y})$ adjacent vertices of the polygon $P$.
 

### 2020-10-06 doc/paper.tex
work on Section 1.2

@@
 	\subsection{Discretization}  
-	The discretization $D(P)$ of the polygon $P$ is builded as follows.
-Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of $P$, where \\
-$ \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\}$ and\\
-$ \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\}$,\\
-where $ (u_{x},u_{y}),(v_{x},v_{y})$ adjacent vertices of the polygon $P$.
+	The discretization $D(P)$ of the polygon $P$ is built as follows.
+Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow:
+	\begin{equation}
+         \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\} \mbox{ and }
+         \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\},
+ 	\end{equation}
+where $ (u_{x},u_{y}),(v_{x},v_{y})$ are adjacent vertices of polygon $P$.
 
 	\begin{algorithm}[!t]
-		\caption{Discretization $D(P)$ of the polygon $P$}\label{alg:discret}
+		\caption{Discretization $D(P)$ of polygon $P$}\label{alg:discret}
 		\begin{algorithmic}[1]
-			\State \textbf{Input:} The set of vertices V of the polygon $P$
-			\State \textbf{Output:} The discretization $D(P)$ of the polygon $P$
+			\State \textbf{Input:} The set of vertices $V$ of polygon $P$
+			\State \textbf{Output:} The discretization $D(P)$ of polygon $P$
 			\State $BB \gets bounding\_box(P);$
@@
 
-	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod?
-Referisi u odnosu na Pseudokod} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+	All intersection points of this regular grid with polygon $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
+The pseudocode which presents the building steps of the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
 
-	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
+	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike dodaj gdje optimalan izbor cvorova pokriva poligon, i gdje optimalni izbor cvorova ne pokriva poligon...}
 

### 2020-10-06 doc/paper.tex
Ubaceni dijelovi iz draganovog greedy i shaking-a

@@
 	\end{itemize}
+	\begin{algorithm}[!t]
+          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsAdd}
+          	\begin{algorithmic}[1]
+          		\State \textbf{Input:} vertex v
+          		\State \textbf{Output:} updated structures ||coveredPoints and numberOfGuards
+          		\For{Point p in S[v]}
+          		\State coveredPoints.insert(p)
+          		\State numberOfGuards.find(p).second++
+          		\EndFor
+          	\end{algorithmic}
+          \end{algorithm}
+                    \begin{algorithm}[!t]
+          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsRemove}
+          	\begin{algorithmic}[1]
+          		\State \textbf{Input:} vertex v
+          		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
+          		\For{Point p in S[v]}
+          		\State numberOfGuards.find(p).second-- --
+                \If {numberOfGuards.find(p).second==0}
+                    \State coveredPoints.remove(p)
+                    \EndIf
+          		\EndFor
+          	\end{algorithmic}
+          \end{algorithm}
 
@@
 	\fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
+The idea of shaking procedure is to improve the quality of the overall search process by examining other (partial) solutions from the neighborhoods of the current (partial) solution.
+The main principle  is to remove some vertices from the current solution and to add some others, with the hope that the overall quality of the solution is improved.
+More precisely,
+shaking procedure creates a system of neighborhoods which is used for deriving new partial solutions based on the current one.
+ The overall shaking procedure is shown in Figure XXX.
+In the $k$th neighborhood, the procedure choose some $k$ vertices according to the specific criteria and remove them from the current solution.
+After that, the procedure is trying to add (not necessarily new) $k$ vertices to the solution, by using the same criterion as in the greedy function.
+After the process of removing and adding the vertices is finished, the algorithm examines the quality of the obtained new partial solution.
+Two criteria are considered: the value of the objective function (i.e.
+the sum of vertex weights in the solution) and the total number of uncovered points.
+If both values of the new partial solution less than of the current one, than the new solution becomes the current partial solution and the algorithm continues with the next neighborhood.
+If any of values of the new solution is not less than of the current one, than no changes are made and the algorithm continues with the next neighborhood.
+The algorithm stops when all neighborhoods are examined.
+In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum is set to $solution.size()$.
+
+The choice of vertices to be removed is carefully designed and depends on the geometrical properties of the considered polygon.
+In order to remove $k$ vertices, the algorithm iteratively call the function removeVertex which uses two parameters: DIST and OFFSET.
+This function chooses a random vertex from the solution and forms a list of candidates for removing from the solution.
+This list is formed as follows.
+Let $V$ be a random vertex of the polygon.
 

### 2020-10-06 doc/paper.tex
update in the concept

@@
 	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
-The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
+The task we consider is covering all points from $D(P)$ by a subset vertices $V=\{v_1,...,v_n\}$ of $P$ such that sum of the weights of vertices in the subset is minimized.
 	The problem is related to the known MWSC problem.
-	Family $\mathcal{F}$ of nonempty sets consists of sets
-	$S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.
-Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$.
-To each set set $S_i$, a cost $c(S_i) = w_i$ is assigned.
-In this way, our starting task is then equivalent of finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
-	$$ \bigcup_{C \in \mathcal{C}} C = D(P)$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
-The ILP  model for the WSCP is known from the literature, and is here adapted to WOAGP  as follows:
+	Family $\mathcal{F}$ of nonempty sets consists of the sets
+	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.
+Note that set $S_i$ includes points $p_i\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$.
+For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
+In this way, our starting task is then equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
+The ILP  model for the WSCP is already known from the literature, where  here adapted to WOAGP  as follows:
 	\begin{align}
@@
 	\end{cases}$ \\
-	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
+	and $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
 	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
@@
 	\end{equation}
-	whereas the other constraints and the objective function are the same like in the above MIP model.
-Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and variable domain filtering~\cite{laborie2018ibm}.
+	whereas the other constraints and the objective function correspond to above MIP model.
+Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{laborie2018ibm}.
 	\section{Algorithmic Approaches for WOAGP}
@@
 Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement.
-Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
-Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution until it is complete (i.e., it covers all  points from $D(P)$).
+Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to make it complete.
+Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution, and repeating the step until it becomes complete (i.e., it covers all  points from $D(P)$).
 	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}
@@
 	\subsubsection{A Hybrid of the Greedy + CPLEX} \fxnote{TODO: Marko}
-	CPLEX will soon or later degrades its performance w.r.t.
+	CPLEX as an exact solver will soon or later degrade in its performance w.r.t.
 instance size.
-On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.
-So, it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX to do the completion of the partial solution.
+On the other hand, the later stages of a Greedy procedure increase the chance to worsen the final greedy solution since it is noticed that factor of similarity of the remaining nodes becomes high and it becomes hard to recognize more promising nodes from those which are less promising.
+So, it makes sense to combine  partial solutions generated by  Greedy within a few interactions and then to use CPLEX to make the completion of the partial solution.
 Our approach consists of the following steps:
 	\begin{enumerate}
-		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|s^p| = K$);
+		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|s^p| = K$); K is set to $K=\lceil n \cdot partial \rceil$, where $partial \in (0, 1)$ is a parameter of the algorithm;
 		\item Take solution $s^p$ and make it complete by solving a corresponding submodel via CPLEX:

### 2020-10-06 doc/paper.tex
TODO added
fix in title

@@
 	% first the title is needed
-	\title{Measuring efficiency of the greedy-like heuristics for solving  the Weighted Orthogonal Art Gallery Problem under regular grid discretization}
+	\title{Measuring Efficiency of the Greedy-like Heuristics for Solving  the Weighted Orthogonal Art Gallery Problem under Regular Grid Discretization}
 
@@
 shaking procedure creates a system of neighborhoods which is used for deriving new partial solutions based on the current one.
- The overall shaking procedure is shown in Figure XXX.
+ The overall shaking procedure is shown in Figure XXX \fxnote{TODO: Milan dodati sliku}.
 In the $k$th neighborhood, the procedure choose some $k$ vertices according to the specific criteria and remove them from the current solution.

### 2020-10-06 doc/software/milan/pokrivenost.cpp
cover

@@ -1,0 +1,382 @@
+#include <CGAL/Exact_predicates_inexact_constructions_kernel.h>
+#include <CGAL/Polygon_2.h>
+#include <CGAL/Bbox_2.h>
+#include <CGAL/Exact_predicates_exact_constructions_kernel.h>
+#include <CGAL/Simple_polygon_visibility_2.h>
+#include <CGAL/Triangular_expansion_visibility_2.h>
+#include <CGAL/Arrangement_2.h>
+#include <CGAL/Arr_segment_traits_2.h>
+#include <CGAL/Arr_naive_point_location.h>
+#include <CGAL/Boolean_set_operations_2.h>
+#include <CGAL/General_polygon_set_2.h>
+#include <CGAL/Gps_segment_traits_2.h>
+#include <CGAL/centroid.h>
+#include <list>
+#include <minisat/core/Solver.h>
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <sstream>
+#include <chrono>
+#include <bits/stdc++.h>
+
+typedef CGAL::Exact_predicates_inexact_constructions_kernel             K;
+typedef CGAL::Polygon_2<K>                                              Polygon;
+typedef CGAL::Point_2<K>                                                Point;
+typedef CGAL::Exact_predicates_exact_constructions_kernel               Kernel;
+typedef Kernel::Point_2                                                 Point_2;
+typedef CGAL::Polygon_2<Kernel>                                         Polygon_2;
+typedef Kernel::Segment_2                                               Segment_2;
+typedef CGAL::Arr_segment_traits_2<Kernel>                              Traits_2;
+typedef CGAL::Arrangement_2<Traits_2>                                   Arrangement_2;
+typedef Arrangement_2::Edge_const_iterator                              Edge_const_iterator;
+typedef Arrangement_2::Halfedge_const_handle                            Halfedge_const_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef Arrangement_2::Halfedge_handle                                  Halfedge_handle;
+typedef CGAL::Simple_polygon_visibility_2<Arrangement_2,CGAL::Tag_true> RSPV;
+typedef CGAL::Polygon_with_holes_2<Kernel>                              Polygon_with_holes_2;
+typedef std::list<Polygon_with_holes_2>                                 Pwh_list_2;
[…]

### 2020-10-07 doc/paper.tex
Dopunjen shaking

--- 2020-10-06 doc/paper.tex
@@
 	\fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
-The idea of shaking procedure is to improve the quality of the overall search process by examining other (partial) solutions from the neighborhoods of the current (partial) solution.
+The idea of shaking procedure is to improve the quality of the overall search process by examining other (partial) solutions from the neighborhoods of the current (partial) solution. More precisely,
+shaking procedure creates a system of neighborhoods which is used for deriving new partial solutions based on the current one.
 The main principle  is to remove some vertices from the current solution and to add some others, with the hope that the overall quality of the solution is improved.
-More precisely,
-shaking procedure creates a system of neighborhoods which is used for deriving new partial solutions based on the current one.
- The overall shaking procedure is shown in Figure XXX.
-In the $k$th neighborhood, the procedure choose some $k$ vertices according to the specific criteria and remove them from the current solution.
+ The overall procedure is shown in Figure XXX.
+In the $k$th neighborhood, the procedure chooses some $k$ vertices according to the specific criteria and removes them from the current solution.
 After that, the procedure is trying to add (not necessarily new) $k$ vertices to the solution, by using the same criterion as in the greedy function.
@@
 the sum of vertex weights in the solution) and the total number of uncovered points.
-If both values of the new partial solution less than of the current one, than the new solution becomes the current partial solution and the algorithm continues with the next neighborhood.
+If both values of the new partial solution less than of the current one, then the new solution becomes the current partial solution and the algorithm continues with the next neighborhood.
 If any of values of the new solution is not less than of the current one, than no changes are made and the algorithm continues with the next neighborhood.
-The algorithm stops when all neighborhoods are examined.
-In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum is set to $solution.size()$.
+The algorithm stops when all neighborhoods are examined and the overall search continues with the greedy heuristic.
+In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum is set to $solution.size()/3$.
 
-The choice of vertices to be removed is carefully designed and depends on the geometrical properties of the considered polygon.
-In order to remove $k$ vertices, the algorithm iteratively call the function removeVertex which uses two parameters: DIST and OFFSET.
-This function chooses a random vertex from the solution and forms a list of candidates for removing from the solution.
-This list is formed as follows.
-Let $V$ be a random vertex of the polygon.
+The choice of vertices to be removed is carefully designed and depends on geometrical properties of the considered polygon.
+In order to remove $k$ vertices, the algorithm iteratively call the function \texttt{removeVertex} which uses two parameters: \texttt{DISTANCE} and \texttt{OFFSET}.
+In each call, function \texttt{removeVertex} chooses a random vertex $v$ from the solution and forms a list of candidates for removing from the solution.
+The list is formed as follows.
+Moving along the \texttt{OFFSET} edges of the polygon from the vertex $v$ in both directions (clockwise and counterclockwise), all vertices belonging to the partial solution are initially added to the list.
+Further, all such vertices, which are on the Euclidean distance less than \texttt{DISTANCE} are removed.
+Other words, candidate for the removing are relatively close to the vertex $v$ in the sense of adjacent edges in the polygon, but far from $v$ with respect to Euclidean distance.
+By this approach, shaking effect is stronger, since we remove vertices which are more distant from the current one, but still related to it with respect of the polygon structure.
+In such strategy leads to the empty list, then a random vertex from the solution is removed.
+\fxnote{Negdje navesti kako se racunaju ove DISTANCE and OFFSET}
 

### 2020-10-07 doc/paper.tex
work on the concept: up to Section 3.1

--- 2020-10-06 doc/paper.tex
@@
 
-	For a given polygon $P$, \emph{Art Gallery Problem} (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
+	For a given polygon $P$, the \emph{Art Gallery Problem} (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
 We say that the point $y$ is covered by the point $x$, or $y$ is visible from $x$.
 Set $G$ is called \emph{guard set} of $P$ and the points from $G$ as \emph{guards}.
-In \emph{The Orthogonal Art Gallery Problem} (OAGP) edges of the polygon are only horizontal and vertical w.r.t.
-the axis, i.e.
+In the \emph{Orthogonal Art Gallery Problem} (OAGP) we suppose that edges of the polygon are only horizontal and vertical w.r.t.
+the axes, i.e.
 the angles allowed between adjacent edges are  $90^{\circ}$ or $270^{\circ}$.
-The original AGP was stated by Victor  Klee in 1973.~\cite{o1987art}.
-The problem might be motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
+The original AGP was initially stated by Victor  Klee in 1973.~\cite{o1987art}.
+The problem is motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered.
 Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings.
@@
 This restricted problem is known to be $\mathcal{NP}$--hard~\cite{schuchardt1995two,katz2008guarding}.
-When comes to real situations (like installing the cameras in a building) , it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting the range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
+When it comes to the real situations (like installing the cameras in a building), it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting its range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
 In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
+\fxnote{Marko: Ovo nije nas problem, nas je relaksiraniji, posmatramo ga nad diskretizacijom.
+Mislim da to treba odmah naglasiti ovdje i razlog asto uzimamo ovu diskretizaciju...}
 
@@
 
-	Concerning the exact and heuristic techniques to solve AGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
+	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
 In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal.
@@
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
-	A comprehensive analysis of many greedy-like heuristic for the WMSCP was presented in \cite{vasko2016best}.
+	A comprehensive analysis of various greedy-like heuristics for the WMSCP was presented in \cite{vasko2016best}.
 	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
@@
 
-	\subsection{Discretization}  
+	\subsection{The Regular Discretization of Polygon}  
 	The discretization $D(P)$ of the polygon $P$ is built as follows.
@@
 	\section{Exact methods}
-	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP, which are used  in the rest of the paper.
+	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP  under regular grid discretization, which are used  in the rest of the paper.
 	\subsection{Integer linear programming model}
@@
 	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.
-Note that set $S_i$ includes points $p_i\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$.
+Note that set $S_i$ includes points $p\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$.
 For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
-In this way, our starting task is then equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+In this way, our starting task is equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
 	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
@@
 	and $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
-	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
+	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t.
+discretization $D(P)$ of polygon $P$.
 	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
@@
 	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
-	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by ILOG IBM CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
+	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by IBM ILOG CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
 	\begin{equation}
@@
 	whereas the other constraints and the objective function correspond to above MIP model.
-Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{laborie2018ibm}.
-	\section{Algorithmic Approaches for WOAGP}
-	\subsection{Greedy approaches for solving WOAGP}
-	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP.
-Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement.
+Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variables' domain filtering~\cite{laborie2018ibm}.
+
+	\section{Algorithmic Approaches to Solve the WOAGP}
+	\subsection{Greedy approaches}
+	Since WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to apply various greedy algorithms to solve WOAGP.
+Greedy algorithms produce a solution of reasonable quality within a short interval of time and, in essence, they are easy to implement.
 Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to make it complete.
-Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution, and repeating the step until it becomes complete (i.e., it covers all  points from $D(P)$).
+Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend a curent partial solution, we choose one with the smallest greedy value and add it to the solution.
+These steps are repeated until the solution becomes complete whcih is this case relates to covering all  points from $D(P)$.
 	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

### 2020-10-07 doc/paper.tex

--- 2020-10-07 doc/paper.tex
@@
 
-	\subsection{Discretization}
+	\subsection{The Regular Discretization of Polygon}  
 	The discretization $D(P)$ of the polygon $P$ is built as follows.
 Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow:
+
 	\begin{equation}
@@
 	The problem is related to the known MWSC problem.
-	Family $\mathcal{F}$ of nonempty sets consists of sets
-	$S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.
-Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$.
-To each set set $S_i$, a cost $c(S_i) = w_i$ is assigned.
-In this way, our starting task is then equivalent of finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
-	$$ \bigcup_{C \in \mathcal{C}} C = D(P)$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
-The ILP  model for the WSCP is known from the literature, and is here adapted to WOAGP  as follows:
+	Family $\mathcal{F}$ of nonempty sets consists of the sets
+	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.
+Note that set $S_i$ includes points $p\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$.
+For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
+In this way, our starting task is equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
+The ILP  model for the WSCP is already known from the literature, where  here adapted to WOAGP  as follows:
+
 	\begin{align}
@@
 	\end{cases}$ \\
+
 	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
@@
 Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
-Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution until it is complete (i.e., it covers all  points from $D(P)$).
+Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend current partial solution,  we choose one with the smallest greedy value and add it to the current solution until it becomes complete (i.e., it covers all  points from $D(P)$).
+
 	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

### 2020-10-07 doc/paper.tex
text polishing

@@
 	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
-	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by IBM ILOG CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
+	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by IBM ILOG CP Optimizer~\cite{laborie2018ibm}.
+In this case,  Constraint~(\ref{eq:const-3}) is transformed into
 	\begin{equation}
@@
 	whereas the other constraints and the objective function are the same like in the above MIP model.
-Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and variable domain filtering~\cite{laborie2018ibm}.
+Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
 	\section{Algorithmic Approaches for WOAGP}
@@
 	\end{algorithm}
-	\subsubsection{An existing greedy method}\fxnote{TODO: Milana}
+	\subsubsection{An existing greedy method}
 
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the literature for WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
+	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
 	\begin{align}
@@
 	where $f(s^p) = |\bigcup_{s \in s^p} s |$.
-	This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.
+	This heuristic is also an approximation algorithm with $O(\log(n))$ approximation factor.
 
-	\subsubsection{A Novel Greedy Heuristic}\fxnote{TODO: Dragan}
+	\subsubsection{A Novel Greedy Heuristic} 
 	In this subsection we present a novel greedy function, which is used in the greedy algorithm.
-Let us introduce a term  ``incorrect point''.
-For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
+First, we introduce a term  ``incorrect point''; for a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
 Let us denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
 Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be the cardinality of discretization set.
-The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution if $v$ is included in it and the total number of incorrect points, given by the formula:
+The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution when guard $v$ is included in $s^{ps}$ and the total number of incorrect points, given by the formula:
 	\begin{equation}\label{eq:greedyfun2}
@@
 	From Equation (\ref{eq:greedyfun3}) one can see that the greedy function $g_2$ mainly depends on the second term, since the value of the first one is not greater than 1.
-On other words, this function prefers such guards  which inclusion in the partial solution will cover more points.
-On the other side, if the inclusion of some two guards covers the same number of points, then the function suggests  the guard with lower cost.
-In the early stage of the greedy algorithm this approach will prefer those guards which covers more points of the not-yet-covered points from $D(P)$, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
+On other words, this function prefers such guards  whose inclusion in the partial solution covers more points.
+On the other hand, if the inclusion of some two guards covers the same number of points, then the function suggests  the guard with lower cost.
+At the earliest stages of the greedy algorithm this approach will prefer those guards which cover more points of the not-yet-covered points from $D(P)$, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
 
@@
 
-	Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows.
-	For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $Surf(v_j)$.
-As the next candidate to extend $s^P$, we choose a guard $v^*$ which covers set $V(j)$ by the smallest price per unit, among the other candidate to extend $s^P$.
+	Ties occurred in the search are broken by using  price-per-unit heuristic which is stated as follows.
+	For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $\emph{Surf}(v_j)$.
+As the next candidate to extend $s^{ps}$, we choose a guard $v^*$ which covers set $V(j)$ by the smallest price per unit, among the other candidate to extend $s^{ps}$.
 More precisely, this greedy criterion $g$ is given as:
 	\begin{align}
-	g(s^p, v_i) = \frac{w_{i}}{|Surf({v_i})|},
+	g(s^{ps}, v_i) = \frac{w_{i}}{|Surf({v_i})|},
 	\end{align}
-	and vertex $v^*$ that minimizes $g(s^p, v_i)$ is chosen as an extension of the current partial solution.
-	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes~(\ref{eq:greedyfun3}) and (\ref{eq:greedyfun4}).
+	and vertex $v^*$ that minimizes $g(s^{ps}, v_i)$ is chosen as an extension of the current partial solution.
+	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes criteria~(\ref{eq:greedyfun3}) and (\ref{eq:greedyfun4}).
 	\subsubsection{Partial calculation of objective function}
@@
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex v
-          		\State \textbf{Output:} updated structures ||coveredPoints and numberOfGuards
-          		\For{Point p in S[v]}
-          		\State coveredPoints.insert(p)
-          		\State numberOfGuards.find(p).second++
+          		\State \textbf{Input:} vertex $v$
+          		\State \textbf{Output:} updated structures: coveredPoints and numberOfGuards
+          		\For{$p$ in $S[v]$}
+          		\State coveredPoints.insert($p$)
+          		\State numberOfGuards.find($p$).second++
           		\EndFor
@@
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex v
+          		\State \textbf{Input:} vertex $v$
           		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
-          		\For{Point p in S[v]}
-          		\State numberOfGuards.find(p).second-- --
-                \If {numberOfGuards.find(p).second==0}
-                    \State coveredPoints.remove(p)
+          		\For{$p \in S[v]$}
+          		\State numberOfGuards.find($p$).second-- --
+                \If {numberOfGuards.find($p$).second$=0$}
+                    \State coveredPoints.remove($p$)
                     \EndIf
@@
 
-	\subsubsection{A hybrid of the Greedy and shaking}
-	\fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
+	\subsubsection{A hybrid of the Greedy and a shaking}
+	\fxnote{TODO: Dragan}
 The idea of shaking procedure is to improve the quality of the overall search process by examining other (partial) solutions from the neighborhoods of the current (partial) solution. More precisely,
@@
 the sum of vertex weights in the solution) and the total number of uncovered points.
-If both values of the new partial solution less than of the current one, then the new solution becomes the current partial solution and the algorithm continues with the next neighborhood.
-If any of values of the new solution is not less than of the current one, than no changes are made and the algorithm continues with the next neighborhood.
-The algorithm stops when all neighborhoods are examined and the overall search continues with the greedy heuristic.
-In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum is set to $solution.size()/3$.
+If the both values of the new partial solution are lower  than the corresponding values of the current one, then the new solution becomes the current partial solution and the algorithm proceeds with the next neighborhood.
+If any of the two values of the new solution is not lower than of the corresponding values of the current one, than no changes are made and the algorithm proceeds with the next neighborhood.
+The algorithm stops once all neighborhoods are examined and the overall search continues with the greedy heuristic.
+In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum size is set to $solution.size()/3$.\fxnote{sta je solution, nigdje prethodno definisano, donji cio dio nedostaje}
 
@@
 The list is formed as follows.
-Moving along the \texttt{OFFSET} edges of the polygon from the vertex $v$ in both directions (clockwise and counterclockwise), all vertices belonging to the partial solution are initially added to the list.
-Further, all such vertices, which are on the Euclidean distance less than \texttt{DISTANCE} are removed.
+Moving along the \texttt{OFFSET} edges of the polygon from the (randomly chosen) vertex $v$ in both directions (clockwise and counterclockwise), all vertices belonging to the partial solution are initially added to the list.
+Further, all such vertices, which are on the Euclidean distance lower than \texttt{DISTANCE} from vertex $v$ are removed.
 Other words, candidate for the removing are relatively close to the vertex $v$ in the sense of adjacent edges in the polygon, but far from $v$ with respect to Euclidean distance.
 By this approach, shaking effect is stronger, since we remove vertices which are more distant from the current one, but still related to it with respect of the polygon structure.
-In such strategy leads to the empty list, then a random vertex from the solution is removed.
+If such strategy leads to an empty list, then a random vertex from the solution has been removed.
 \fxnote{Negdje navesti kako se racunaju ove DISTANCE and OFFSET}
 
-	\subsubsection{A Hybrid of the Greedy + CPLEX} \fxnote{TODO: Marko}
-	CPLEX will soon or later degrades its performance w.r.t.
-instance size.
-On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.
-So, it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX to do the completion of the partial solution.
-Our approach consists of the following steps:
+\subsubsection{A Hybrid of the Greedy + CPLEX}  
+	The performance of \textrm{Cplex}  soon or later degrades w.r.t.
+instance size since the prolem is NP--hard.
+On the other hand, in the later stage, there is an increased chance for Greedy to worsen the final greedy solution due to a high number of components which are similar to be chosen for extension.
+So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few interactions  and only then to use CPLEX to do the completion of the partial solution.
+In details, our approach consists of the following steps:
 	\begin{enumerate}
-		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|s^p| = K$);
-		\item Take solution $s^p$ and make it complete by solving a corresponding submodel via CPLEX:
+		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $s^{ps}$ (therefore, $|s^{ps}| = K$);
+		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via CPLEX:
 		\begin{itemize}
-			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^p$ into the existing WOAGP model;
-			\item we obtain a complete solution $\bar {s^p}$;
+			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
+			\item a complete solution $\bar {s^p}$ is obtained;
 		\end{itemize}
@@
 Then, $w_i := \frac{l_i + l_{i+1}}{2}$.
-This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$.
-This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
+This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$.
+This implies that the range of camera $i$ has to be larger, which again means that it has a higher price.
+In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.
 		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
@@
 	\end{itemize}
-     We used three different kind of benchmark sets:
+     We used two different kind of benchmark sets:
      \begin{itemize}
-     	\item \emph{random} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
      	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
@@
      \end{itemize}
-     Fro small and large instances, one polygon with $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set.
-For random set, we took a subset of 200 instances.
-In overall, we have 400 polygons which vertices are weighted by two different weights, which gives us, in overall, 800 instances.
+     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set.
+In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
+     \subsection{Settings and the Parameters' choice}
+     \fxnote{TODO: Marko}
+
 	\subsection{Results on exact methods}

### 2020-10-07 doc/paper.tex
Computational section: started

@@
 In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
-     \subsection{Settings and the Parameters' choice}
-     \fxnote{TODO: Marko}
+     \subsection{Settings and the choice of the Parameters}
+      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB.
+The maximum computation time of each of our algorithms was set to 5 min.
 
-	\subsection{Results on exact methods}
-\fxnote{Marko: Solving of CP i MIP solvers are limited to 5 mins. }
+      After conducting preliminary results, we decided to use the following parameters for our algorithms:
+      \begin{itemize}
+      	\item Greedy + Shaking parameters:  $\mathrm{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\mathrm{OFFSET} = 0.3$,
+        \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
+      \end{itemize}
+	\subsection{Results and Discussion}
+
 	\section{Conclusions and Future Work}

### 2020-10-07 doc/paper.tex
work on C. section

@@
 	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
-	\begin{align}
-	g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
+	\begin{align}\label{eq:Lovasz}
+	q_1(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
 	\end{align}
@@
       \begin{itemize}
-      	\item Greedy + Shaking parameters:  $\mathrm{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\mathrm{OFFSET} = 0.3$,
+      	\item Greedy + Shaking parameters:  $\texttt{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\texttt{OFFSET} = 0.3$,
         \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
       \end{itemize}
+     The benchmark sets and the executable file of this project are provided at \href{link}{link}.
 	\subsection{Results and Discussion}
+        The following algorithms are included in our computation:
+        \begin{itemize}
+        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{CPLEX};
+        \end{itemize}  and 9 heuristic approaches: 
+           \begin{itemize}
+           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
+            \item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
+            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+CPLEX, $i=1,2,3$, 
+            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
+           \end{itemize}
 

### 2020-10-08 doc/paper.tex
shaking story removed

--- 2020-10-07 doc/paper.tex
@@
 		\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
-		\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others, where the replacement is based on measuring  distances between points in the polygon.\fxnote{TODO: popraviti}
-		\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP.
+
+		\item Both an existing and the novel greedy algorithms are hybridized with the ILP.
 		\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
 		\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested, analysed, and their efficiency checked.
-The methods are then compared to the exact approaches ILP and \emph{Constraint Programming} (CP).
+The methods are then compared to the exact approaches ILP and \emph{Constraint Programming} (CP) w.r.t.
+the quality of obtained heuristic solutions as well as runtimes.
 	\end{itemize}
@@
 
-	\subsubsection{A hybrid of the Greedy and a shaking}
-	\fxnote{TODO: Dragan}
-The idea of shaking procedure is to improve the quality of the overall search process by examining other (partial) solutions from the neighborhoods of the current (partial) solution. More precisely,
-shaking procedure creates a system of neighborhoods which is used for deriving new partial solutions based on the current one.
-The main principle  is to remove some vertices from the current solution and to add some others, with the hope that the overall quality of the solution is improved.
- The overall procedure is shown in Figure XXX.
-In the $k$th neighborhood, the procedure chooses some $k$ vertices according to the specific criteria and removes them from the current solution.
-After that, the procedure is trying to add (not necessarily new) $k$ vertices to the solution, by using the same criterion as in the greedy function.
-After the process of removing and adding the vertices is finished, the algorithm examines the quality of the obtained new partial solution.
-Two criteria are considered: the value of the objective function (i.e.
-the sum of vertex weights in the solution) and the total number of uncovered points.
-If the both values of the new partial solution are lower  than the corresponding values of the current one, then the new solution becomes the current partial solution and the algorithm proceeds with the next neighborhood.
-If any of the two values of the new solution is not lower than of the corresponding values of the current one, than no changes are made and the algorithm proceeds with the next neighborhood.
-The algorithm stops once all neighborhoods are examined and the overall search continues with the greedy heuristic.
-In the proposed shaking algorithm, the minimum size of the neighborhood is 1 and the maximum size is set to $solution.size()/3$.\fxnote{sta je solution, nigdje prethodno definisano, donji cio dio nedostaje}
-
-The choice of vertices to be removed is carefully designed and depends on geometrical properties of the considered polygon.
-In order to remove $k$ vertices, the algorithm iteratively call the function \texttt{removeVertex} which uses two parameters: \texttt{DISTANCE} and \texttt{OFFSET}.
-In each call, function \texttt{removeVertex} chooses a random vertex $v$ from the solution and forms a list of candidates for removing from the solution.
-The list is formed as follows.
-Moving along the \texttt{OFFSET} edges of the polygon from the (randomly chosen) vertex $v$ in both directions (clockwise and counterclockwise), all vertices belonging to the partial solution are initially added to the list.
-Further, all such vertices, which are on the Euclidean distance lower than \texttt{DISTANCE} from vertex $v$ are removed.
-Other words, candidate for the removing are relatively close to the vertex $v$ in the sense of adjacent edges in the polygon, but far from $v$ with respect to Euclidean distance.
-By this approach, shaking effect is stronger, since we remove vertices which are more distant from the current one, but still related to it with respect of the polygon structure.
-If such strategy leads to an empty list, then a random vertex from the solution has been removed.
-\fxnote{Negdje navesti kako se racunaju ove DISTANCE and OFFSET}
-
-\subsubsection{A Hybrid of the Greedy + CPLEX}  
+\subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}  
 	The performance of \textrm{Cplex}  soon or later degrades w.r.t.
@@
       \begin{itemize}
-      	\item Greedy + Shaking parameters:  $\mathrm{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\mathrm{OFFSET} = 0.3$,
-        \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
+        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
       \end{itemize}
+     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
 	\subsection{Results and Discussion}
+        The following algorithms are included in our computation:
+        \begin{itemize}
+        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
+        \end{itemize}  and 6 heuristic approaches: 
+           \begin{itemize}
+           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
+            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
+            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
+            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
+           \end{itemize}
 

### 2020-10-08 doc/paper.tex
tables prepared

@@
 		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution;
-		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
+		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+Its time complexity is $O(n)$.
+		%\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
 	\end{itemize}
+
 	\begin{algorithm}[!t]
@@
           \end{algorithm}
+
+          \begin{comment}
+
             \begin{algorithm}[!t]
@@
           \end{algorithm}
-
+	  \end{comment} 
 \subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}  
@@
            \end{itemize}
+         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
+
+         \begin{table}
+         \centering
+         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
+         	\hline
+         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
+         	\hline
+            \multicolumn{1}{|c|}{}&
+            \multicolumn{2}{|c|}{$Small$}&
+            \multicolumn{2}{|c|}{$Large$} \\
+            \hline	
+         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
+            \textsc{Cplex} & & & & \\ \hline
+            \textsc{Cp} & & & & \\ \hline
+         	\textsc{Greeedy-1} & & & & \\ \hline
+         	\textsc{Greeedy-2} & & & & \\ \hline
+         	\textsc{Greeedy-3} & & & & \\ \hline
+         	\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
+         	\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
+         	\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
+         	\hline
+         \end{tabular}
+         \caption{Different combinations of the algorithms.}
+        \end{table}
+
+       \begin{table}
+    	\centering
+    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
+    		\hline
+    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
+    		\hline
+    		\multicolumn{1}{|c|}{}&
+    		\multicolumn{2}{|c|}{$Small$}&
+    		\multicolumn{2}{|c|}{$Large$} \\
+    		\hline	
+    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
+    		\textsc{Cplex} & & & & \\ \hline
+    		\textsc{Cp} & & & & \\ \hline
+    		\textsc{Greeedy-1} & & & & \\ \hline
+    		\textsc{Greeedy-2} & & & & \\ \hline
+    		\textsc{Greeedy-3} & & & & \\ \hline
+    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
+    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
+    		\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
+    		\hline
+    	\end{tabular}
+    	\caption{Different combinations of the algorithms.}
+    \end{table}
 

### 2020-10-08 doc/paper.tex
update
some results added

@@
            \end{itemize}
+         From our results, we noticed that there is no significant difference between the results of \textsc{Greedy-2} and \textsc{Greedy-3}.
+Therefore, we report only the results of \textsc{Greedy-2} algorithm.
          Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
@@
          	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
-            \textsc{Cplex} & & & & \\ \hline
-            \textsc{Cp} & & & & \\ \hline
-         	\textsc{Greeedy-1} & & & & \\ \hline
-         	\textsc{Greeedy-2} & & & & \\ \hline
-         	\textsc{Greeedy-3} & & & & \\ \hline
-         	\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
-         	\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
-         	\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
+            \textsc{Cplex} & 15.93 & 0.0 & & \\ \hline
+            \textsc{Cp} &  16.04 & 0.0 & & \\ \hline
+         	\textsc{Greeedy-1} & 22.04  & & & \\ \hline
+         	\textsc{Greeedy-2} & 19.97  & & & \\ \hline
+         	\textsc{Greeedy-1 + Cplex} & 18.49 & & & \\ \hline
+         	\textsc{Greeedy-2 + Cplex} & 18.39 & & & \\ \hline
+
          	\hline
@@
     		\textsc{Greeedy-2} & & & & \\ \hline
-    		\textsc{Greeedy-3} & & & & \\ \hline
+
     		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
     		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
-    		\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
+
     		\hline
@@
     \end{table}
+        From the numerical results, we observe the following conclusions:
+        \begin{itemize}
+        	\item \fxnote{TODO}
+        \end{itemize}
 

### 2020-10-08 doc/paper.tex
work on computational section: numerical results

@@
      \end{itemize}
-     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set.
-In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
+     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set.
+In overall, we have 192 polygons which vertices with two different weights, which gives us, in overall, 384 problem instances.
      \subsection{Settings and the choice of the Parameters}
@@
 Therefore, we report only the results of \textsc{Greedy-2} algorithm.
-         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
-
+         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab: t_w0} and Table~\ref{tab: t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
+Each of the tables is additionally  subdivided by a vertical line into two parts, depending on the case if we consider \emph{small} or \emph{large} polygons for a specific weight.
+         For each of the algorithm  we reported average quality and average standard deviation ($\sigma$) over all instances (96 instances) of the considered subgroup.
+If an asterisk is given, i means taht optimality is proven for all instances of considered subgroup.
          \begin{table}
@@
          	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
-            \textsc{Cplex} & 15.93 & 0.0 & & \\ \hline
-            \textsc{Cp} &  16.04 & 0.0 & & \\ \hline
-         	\textsc{Greeedy-1} & 22.04  & & & \\ \hline
-         	\textsc{Greeedy-2} & 19.97  & & & \\ \hline
-         	\textsc{Greeedy-1 + Cplex} & 18.49 & & & \\ \hline
-         	\textsc{Greeedy-2 + Cplex} & 18.39 & & & \\ \hline
+            \textsc{Cplex} & 15.93* & 8.12 & 2.62* & 1.38 \\ \hline
+            \textsc{Cp} &  16.04 & 8.24 &  2.62*  & 1.38\\ \hline
+         	\textsc{Greeedy-1} & 22.04  & 12.02 & 3.38   & 1.59 \\ \hline
+         	\textsc{Greeedy-2} & 19.97  & 9.60  &  3.51 & 1.80\\ \hline
+         	\textsc{Greeedy-1 + Cplex}  & 18.49 &  9.56  & 3.34 & 1.41 \\ \hline
+         	\textsc{Greeedy-2 + Cplex}  & 18.39 & 8.96 &  3.32 & 1.29 \\ \hline
 
@@
          \end{tabular}
-         \caption{Different combinations of the algorithms.}
+         \caption{Results of different combinations of the algorithms.} \label{tab: t_w0}
         \end{table}
@@
     		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
-    		\textsc{Cplex} & & & & \\ \hline
-    		\textsc{Cp} & & & & \\ \hline
-    		\textsc{Greeedy-1} & & & & \\ \hline
-    		\textsc{Greeedy-2} & & & & \\ \hline
-
-    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
-    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
+    		\textsc{Cplex} & 36.03* & 19.04 & 6.72* & 3.07 \\ \hline
+    		\textsc{Cp} & 36.03* & 19.04 & 6.72* &  3.07 \\ \hline
+    		\textsc{Greeedy-1} &39.28  & 19.55 & 6.76 & 3.06 \\ \hline
+    		\textsc{Greeedy-2} & 40.92 & 19.54 & 6.76 & 3.06 \\ \hline
+    		\textsc{Greeedy-1 + Cplex} & 37.78 & 19.59 &  6.72 & 3.07 \\ \hline
+    		\textsc{Greeedy-2 + Cplex} & 37.31 & 19.13 &  6.72 & 3.07 \\ \hline
 
@@
     	\end{tabular}
-    	\caption{Different combinations of the algorithms.}
+    	\caption{Result of different combinations of the algorithms.} \label{tab: t_w1}
     \end{table}
@@
         \begin{itemize}
-        	\item \fxnote{TODO}
+        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches.
+moreover, Cplex could prove optimallity of all (192) instances, while \textsc{Cp} could not.
+It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.
+        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}.
+        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
         \end{itemize} 
+          \fxnote{TODO: generisati plotove za vremena svakog od algoritama (da se vidi da je greedy brzi -- nadamo se)}
 

### 2020-10-08 doc/paper.tex
minor fix

@@
 	\section{Computational Results}
-	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
+	The instances of the specific OAGP with up to a 200 vertices are used in our experiments to which a weight to each vertex of polygons is assigned.
+We included two kind of weights into these benchmarks:
 	\begin{itemize}

### 2020-10-09 doc/paper.tex
predadjem dio dragan greedy, dodani autori i pocetak abstrakta

@@
 	% first the title is needed
-	\title{Measuring efficiency of the greedy-like heuristics for solving  the Weighted Orthogonal Art Gallery Problem under regular grid discretization}
+	\title{Performance evaluation of two greedy-like heuristics for solving  the Weighted Orthogonal Art Gallery Problem under regular grid discretization}
 
 	%
-	%  \author{--}
-	%
+	\author[1]{Milan Predojevi\'c}
+\author[1]{Marko Djukanovi\'c}
+\author[1]{Milana Grbi\'c}
+\author[1]{Dragan Mati\'c}
+    \address[1]{Faculty of Natural Science and Mathematics, University of Banja Luka, Bosnia and Herzegovina}
 
-	%  \institute{%$^1$Institute of Logic and Computation, TU Wien,
-	%Vienna, Austria,\\
-	%	       $^2$ Artificial Intelligence Research Institute (IIIA-CSIC),\\ \normalsize Campus UAB, Bellaterra, Spain \\
-	%\institute{Springer-Verlag, Computer Science Editorial,\\
-	%Tiergartenstr. 17, 69121 Heidelberg, Germany\\
-	%\mailsa\\
-	%\mailsb\\
-	%\mailsc\\
-	%\url{http://www.springer.com/lncs}
-	%}
 	\begin{abstract}
-		In this paper...
+		In this paper we deal with the Weighted Orthogonal Art Gallery Problem under the regular grid discretization.
+We propose a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
+This new approach and an existing greedy algorithm are further  hybridized with the Integer Linear programming (ILP), originally formulated for the well known Minimum Set Cover problem.
+Experimental results performed on two classes of real--like weighted instances show that the proposed methods \fxnote{treba zavrsiti ovu recenicu}
 	\end{abstract}
@@
 When it comes to the real situations (like installing the cameras in a building), it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting its range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
-In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
-\fxnote{Marko: Ovo nije nas problem, nas je relaksiraniji, posmatramo ga nad diskretizacijom.
-Mislim da to treba odmah naglasiti ovdje i razlog asto uzimamo ovu diskretizaciju...}
+In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP) the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
+In this paper we consider WOAGP problem under the regular grid discretization of $P$, which we describe in Subsection~\ref{sec:regulardiscretization}.
 
@@
 		\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
-		\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested, analysed, and their efficiency checked.
+		\item In a comprehensive computational experiment,  we tested, analysed and check the efficiency of different variants of the considered algorithms.
 The methods are then compared to the exact approaches ILP and \emph{Constraint Programming} (CP) w.r.t.
@@
 
-	\subsection{The Regular Discretization of Polygon}  
+	\subsection{The Regular Grid Discretization of Polygon}\label{sec:regulardiscretization}
 	The discretization $D(P)$ of the polygon $P$ is built as follows.
@@
 	\begin{align}\label{eq:Lovasz}
-	q_1(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
+	g_1(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
 	\end{align}
-	where $f(s^p) = |\bigcup_{s \in s^p} s |$.
+	where 
+\begin{equation}\label{eq:sp}
+    f(s^p) = |\bigcup_{s \in s^p} s |.
+    \end{equation}
 	This heuristic is also an approximation algorithm with $O(\log(n))$ approximation factor.
@@
 First, we introduce a term  ``incorrect point''; for a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-Let us denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
-Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be the cardinality of discretization set.
+Let us denote by $incorrect_{total}(s^{sp})$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
+Note that  $incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps})$, where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is hte cardinality of discretization set .
+Let $w_{total}$ be the total sum of all weights among all vertices.
 The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution when guard $v$ is included in $s^{ps}$ and the total number of incorrect points, given by the formula:
 	\begin{equation}\label{eq:greedyfun2}
-	%$$obj(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}$$
-	g(s^{ps}; v) = \alpha \cdot \sum_{i \in s^{ps} \cup \{v\}} w_i+ \beta \cdot {incorrect_{total}}
+    g_2(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}} w_i}{w_{total}}+ \frac{incorrect_{total}(s^{ps}\cup v)}{|D(P)|}.
 	\end{equation}
-	where $\alpha$ and $\beta$ are positive real parameters.
 
-	Although many combination of parameters $ \alpha $ and $\beta$ may be used, in our investigation we used parameter $\alpha$  only to normalize the sum of prices, i.e.
-$\alpha = \frac{1}{w_{total}}$ and two values for $\beta$: $\beta = 1$ and $\beta = \frac{1}{|D(P)|}$.
-Thus, we consider two variants of the greedy function:
-	\begin{equation}\label{eq:greedyfun3}
-	g_2(s^{ps}; v)  =  \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}
-	\end{equation}
-	and
-	\begin{equation}\label{eq:greedyfun4}
-	g_3(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
-	\end{equation}
-	From Equation (\ref{eq:greedyfun3}) one can see that the greedy function $g_2$ mainly depends on the second term, since the value of the first one is not greater than 1.
-On other words, this function prefers such guards  whose inclusion in the partial solution covers more points.
-On the other hand, if the inclusion of some two guards covers the same number of points, then the function suggests  the guard with lower cost.
-At the earliest stages of the greedy algorithm this approach will prefer those guards which cover more points of the not-yet-covered points from $D(P)$, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.
-
-	In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
-	In this case, the algorithm does not  ultimately prefer any of criteria for choosing next vertex. Instead,  \fxnote{TODO...}
+	In the Equation  (\ref{eq:greedyfun2}) both terms are normalized in order to better balance trade off between two factors which influence on the search.
+The algorithm does not  ultimately prefer any of criteria for choosing next vertex.
+Although it cannot be a rule, it is justified to suppose that the second term has a more influence on the choice of the next vertex in earlier phases of the algorithm execution.
+At the beginning, more points are uncovered and the algorithm will choose such vertices which cover larger area of the polygon.
+At the end of algorithm, it could be expected that the first term plays more significant role, since the total number of uncovered points is small.
 
@@
 	and vertex $v^*$ that minimizes $g(s^{ps}, v_i)$ is chosen as an extension of the current partial solution.
-	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes criteria~(\ref{eq:greedyfun3}) and (\ref{eq:greedyfun4}).
-	\subsubsection{Partial calculation of objective function}
+	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes criterion (\ref{eq:greedyfun2}).
+	\subsubsection{Partial calculation of greedy functions}
 
-	In order to enable fast calculation of greedy functions described in previous subsections, we introduce several useful structures and auxiliary functions:
+	In order to enable fast calculation of greedy functions described in previous subsections, we noticed that it could be useful to allow fast updating of the number of uncovered vertices.
+Therefore, we introduced several useful structures and auxiliary functions:
 	\begin{itemize}
-		\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
+		%\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
 		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of Guards in solution which are visible from that point;
 		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
-Its time complexity is $O(n)$.
-		%\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
+		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by $v$ , when $v$ is removed from partial solution; pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
 	\end{itemize}
-
+ Although the time complexity of both functions is $O(|D(P)|)$, from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove} it can be seen that they only depends on the number of points covered by the current vertex, which is expected to be significantly less than the upper bound.
+These two functions allow fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and the vertex is then removed from the solution.
 	\begin{algorithm}[!t]
@@
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex $v$
+          		\State \textbf{Input:} vertex $v$, $s[v]$:  list of points covered by $v$
           		\State \textbf{Output:} updated structures: coveredPoints and numberOfGuards
@@
 
-          \begin{comment}
+          %\begin{comment}
 
             \begin{algorithm}[!t]
-          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsRemove}
+          	\caption{Function updateCoveredPointsRemove}\label{alg:updateCoveredPointsRemove}
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex $v$
+          		\State \textbf{Input:} vertex $v$, $s[v]$:  list of points covered by $v$
           		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
@@
           \end{algorithm}
-	  \end{comment} 
+	 % \end{comment}
 \subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}

### 2020-10-09 doc/paper.tex
sredjen tekst do exp rezultata

@@
 	% first the title is needed
-	\title{Performance evaluation of two greedy-like heuristics for solving  the Weighted Orthogonal Art Gallery Problem under regular grid discretization}
+	\title{Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?}
 
@@
 This new approach and an existing greedy algorithm are further  hybridized with the Integer Linear programming (ILP), originally formulated for the well known Minimum Set Cover problem.
-Experimental results performed on two classes of real--like weighted instances show that the proposed methods \fxnote{treba zavrsiti ovu recenicu}
+Experimental results show that the proposed greedy methods can achieve most of the optimal solution for a class of large area polygons, while for small area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
 	\end{abstract}
@@
 In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP) the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
-In this paper we consider WOAGP problem under the regular grid discretization of $P$, which we describe in Subsection~\ref{sec:regulardiscretization}.
+In this paper we consider WOAGP problem under the regular grid discretization of $P$, described in Subsection~\ref{sec:regulardiscretization}.
 
@@
 
-		\item Both an existing and the novel greedy algorithms are hybridized with the ILP.
+		\item The  greedy algorithm from \cite{chvatal1979greedy} and the novel greedy algorithm are hybridized with the ILP.
 		\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
-		\item In a comprehensive computational experiment,  we tested, analysed and check the efficiency of different variants of the considered algorithms.
+		\item In a comprehensive computational experiment,  we tested, analysed and checked the efficiency of the developed algorithms.
 The methods are then compared to the exact approaches ILP and \emph{Constraint Programming} (CP) w.r.t.
@@
 	\subsection{Integer linear programming model}
-	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.
+	Let us suppose we are given a polygon $P$ and the discretization $D(P)$ of $P$.
 The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
-	The problem is related to the known MWSC problem.
+	The problem is related to the known MWSC problem as follows.
 	Family $\mathcal{F}$ of nonempty sets consists of the sets
@@
 	\subsection{Greedy approaches for solving WOAGP}
-	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP.
  Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement.
-Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
+Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
 Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend current partial solution,  we choose one with the smallest greedy value and add it to the current solution until it becomes complete (i.e., it covers all  points from $D(P)$).
 
-	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}
+	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}.
 
@@
 			\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
-			\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
-			\While{$\text{Extend}(s^{P}) \neq \emptyset$}
-			\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion $g$
-			\State Extend $s^{P}$ by $e$
+			\State $s^{ps} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
+			\While{$\text{Extend}(s^{ps}) \neq \emptyset$}
+			\State Select solution component $e \in  \text{Extend}(s^{ps})$ \hspace{0.3cm}//\,w.r.t.\  some criterion $g$
+			\State Extend $s^{ps}$ by $e$
 			\EndWhile
@@
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
+	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following criterion:
 	\begin{align}\label{eq:Lovasz}
-	g_1(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
+	g_1(s^{ps}, v_i) = \frac{w_{i}}{ f(s^{ps} \cup \{v_i\})  - f(s^{ps})},
 	\end{align}
@@
 \begin{equation}\label{eq:sp}
-    f(s^p) = |\bigcup_{s \in s^p} s |.
+    f(s^{ps}) = |\bigcup_{i \in s^{ps}} S_i |.
     \end{equation}
-	This heuristic is also an approximation algorithm with $O(\log(n))$ approximation factor.
+	This heuristic  also ensures an approximation with $O(\log(n))$ approximation factor.
 
 	\subsubsection{A Novel Greedy Heuristic}
-	In this subsection we present a novel greedy function, which is used in the greedy algorithm.
-First, we introduce a term  ``incorrect point''; for a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
-Let us denote by $incorrect_{total}(s^{sp})$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.
-Note that  $incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps})$, where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is hte cardinality of discretization set .
+	In this subsection we present a novel greedy criterion.
+First, we introduce a term  ``incorrect point''.
+For a point from $D(P)$ we say that it is \textit{incorrect} if it is not covered by any guard from the current partial solution $s^{ps}$.
+Let us denote by $incorrect_{total}(s^{sp})$ the total number of incorrect points from discretization $D(P)$ w.r.t.
+$s^{ps}$.
+Note that  $incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps})$, where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set .
 Let $w_{total}$ be the total sum of all weights among all vertices.
-The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution when guard $v$ is included in $s^{ps}$ and the total number of incorrect points, given by the formula:
+The greedy function w.r.t.
+partial solution $s^{ps}$ and  guard $v$ is defined as follows.
 	\begin{equation}\label{eq:greedyfun2}
-    g_2(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}} w_i}{w_{total}}+ \frac{incorrect_{total}(s^{ps}\cup v)}{|D(P)|}.
+    g_2(s^{ps}, v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}} w_i}{w_{total}}+ \frac{incorrect_{total}(s^{ps}\cup v)}{|D(P)|}.
 	\end{equation}
 
-	In the Equation  (\ref{eq:greedyfun2}) both terms are normalized in order to better balance trade off between two factors which influence on the search.
+	In the Equation  (\ref{eq:greedyfun2}) both terms are normalized on order to achieve better balance between the total sum of guards' costs and the total number of not yet covered points from the discretization.
 The algorithm does not  ultimately prefer any of criteria for choosing next vertex.
 Although it cannot be a rule, it is justified to suppose that the second term has a more influence on the choice of the next vertex in earlier phases of the algorithm execution.
-At the beginning, more points are uncovered and the algorithm will choose such vertices which cover larger area of the polygon.
+At the beginning, more points are uncovered and the algorithm  chooses such vertices which cover larger area of the polygon.
 At the end of algorithm, it could be expected that the first term plays more significant role, since the total number of uncovered points is small.
@@
 	Ties occurred in the search are broken by using  price-per-unit heuristic which is stated as follows.
-	For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $\emph{Surf}(v_j)$.
-As the next candidate to extend $s^{ps}$, we choose a guard $v^*$ which covers set $V(j)$ by the smallest price per unit, among the other candidate to extend $s^{ps}$.
-More precisely, this greedy criterion $g$ is given as:
+	For each not yet considered vertex $v_i$, we denote the region of polygon $P$ that is visible from $v_i$ by $\emph{Surf}(v_j)$.
+As the next candidate to extend $s^{ps}$, we choose such a guard,  with the smallest ratio between the price and the visible surface area.
+More precisely, this  criterion is given as:
 	\begin{align}
-	g(s^{ps}, v_i) = \frac{w_{i}}{|Surf({v_i})|},
+	g'(s^{ps}, v_i) = \frac{w_{i}}{|Surf({v_i})|},
 	\end{align}
-	and vertex $v^*$ that minimizes $g(s^{ps}, v_i)$ is chosen as an extension of the current partial solution.
-	In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics which includes criterion (\ref{eq:greedyfun2}).
+
+	In our experimental studies, we found out that this heuristic does not perform well on its own, but it represents a reasonable tie-breaking mechanism which boosts quality of the aforementioned greedy heuristics.
 	\subsubsection{Partial calculation of greedy functions}
@@
 	In order to enable fast calculation of greedy functions described in previous subsections, we noticed that it could be useful to allow fast updating of the number of uncovered vertices.
-Therefore, we introduced several useful structures and auxiliary functions:
+Therefore, we introduced two useful structures and two auxiliary functions:
 	\begin{itemize}
 		%\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
-		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of Guards in solution which are visible from that point;
-		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
-		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by $v$ , when $v$ is removed from partial solution; pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
+		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of guards in solution which cover that point;
+		\item structure \texttt{set<Point> CoveredPoints} -- set of points from $D(P)$ that are covered by the partial solution;
+		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to partial solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by guard $v$ , when $v$ is removed from partial solution; pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
 	\end{itemize}
- Although the time complexity of both functions is $O(|D(P)|)$, from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove} it can be seen that they only depends on the number of points covered by the current vertex, which is expected to be significantly less than the upper bound.
+ Although the time complexity of both functions is $O(|D(P)|)$, from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove} it can be noticed that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
 These two functions allow fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and the vertex is then removed from the solution.
@@
 \subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}
-	The performance of \textrm{Cplex}  soon or later degrades w.r.t.
-instance size since the prolem is NP--hard.
-On the other hand, in the later stage, there is an increased chance for Greedy to worsen the final greedy solution due to a high number of components which are similar to be chosen for extension.
-So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few interactions  and only then to use CPLEX to do the completion of the partial solution.
+	The performance of \textsc{Cplex}  sooner or later degrades w.r.t.
+instance size due to the complexity of the problem.
+On the other hand, in the later stage, there is an increased chance for Greedy to worsen the obtained greedy solution.
+So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few iterations  and only then to make use the \textsc{Cplex} to do the completion of the partial solution.
 In details, our approach consists of the following steps:
@@
 	\section{Computational Results}
+
+ We used two different kind of benchmark sets:
+     \begin{itemize}
+     	 \item \emph{MinArea} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
+     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
+     \end{itemize}
+     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set.
+In overall, we have 192 polygons which vertices with two different weights, which gives us, in overall, 384 problem instances.
 	The instances of the specific OAGP with up to a 200 vertices are used in our experiments to which a weight to each vertex of polygons is assigned.
@@
 	\end{itemize}
-     We used two different kind of benchmark sets:
-     \begin{itemize}
-     	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
-     	 \item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
-     \end{itemize}
-     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set.
-In overall, we have 192 polygons which vertices with two different weights, which gives us, in overall, 384 problem instances.
+
      \subsection{Settings and the choice of the Parameters}

### 2020-10-09 doc/paper.tex
update

@@
 
-	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
+	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of polygon $P$.
 	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
@@
 	\end{equation}
-	whereas the other constraints and the objective function are the same like in the above MIP model.
+	whereas the other constraints and the objective function are the same like in the above ILP model.
 Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
@@
 \begin{equation}\label{eq:sp}
-    f(s^{ps}) = |\bigcup_{i \in s^{ps}} S_i |.
+    f(s^{ps}) = \left|\bigcup_{i \in s^{ps}} S_i \right|.
     \end{equation}
@@
 	\begin{align}
-	g'(s^{ps}, v_i) = \frac{w_{i}}{|Surf({v_i})|},
+	g'(s^{ps}, v_i) = \frac{w_{i}}{|\emph{Surf}({v_i})|},
 	\end{align}
@@
 	\begin{algorithm}[!t]
-          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsAdd}
+          	\caption{Function \texttt{updateCoveredPointsAdd}}\label{alg:updateCoveredPointsAdd}
           	\begin{algorithmic}[1]
@@
             \begin{algorithm}[!t]
-          	\caption{Function updateCoveredPointsRemove}\label{alg:updateCoveredPointsRemove}
+          	\caption{Function \texttt{updateCoveredPointsRemove}}\label{alg:updateCoveredPointsRemove}
           	\begin{algorithmic}[1]
@@
 	 % \end{comment}
-\subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}
+\subsubsection{A Hybrid of the \textsc{Greedy + \textsc{Cplex}}}
 	The performance of \textsc{Cplex}  sooner or later degrades w.r.t.
@@
 		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $s^{ps}$ (therefore, $|s^{ps}| = K$);
-		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via CPLEX:
+		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via \textsc{Cplex}:
 		\begin{itemize}
-			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
+			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
 			\item a complete solution $\bar {s^p}$ is obtained;
@@
      \end{itemize}
-     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set.
-In overall, we have 192 polygons which vertices with two different weights, which gives us, in overall, 384 problem instances.
-	The instances of the specific OAGP with up to a 200 vertices are used in our experiments to which a weight to each vertex of polygons is assigned.
-We included two kind of weights into these benchmarks:
+     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set. In overall, we have 192 polygons. 
+	We included two kind of weights into each of (192) polygons:
 	\begin{itemize}
@@
       \begin{itemize}
-        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$.
+        \item \textsc{Greedy + \textsc{Cplex}} parameters: $K = 0.05 \cdot n$.
       \end{itemize}
@@
          	\textsc{Greeedy-2} & 19.97  & 9.60  &  3.51 & 1.80\\ \hline
-         	\textsc{Greeedy-1 + Cplex}  & 18.49 &  9.56  & 3.34 & 1.41 \\ \hline
-         	\textsc{Greeedy-2 + Cplex}  & 18.39 & 8.96 &  3.32 & 1.29 \\ \hline
+         	\textsc{Greeedy-1 + \textsc{Cplex}}  & 18.49 &  9.56  & 3.34 & 1.41 \\ \hline
+         	\textsc{Greeedy-2 + \textsc{Cplex}}  & 18.39 & 8.96 &  3.32 & 1.29 \\ \hline
 
@@
     		\textsc{Greeedy-2} & 40.92 & 19.54 & 6.76 & 3.06 \\ \hline
-    		\textsc{Greeedy-1 + Cplex} & 37.78 & 19.59 &  6.72 & 3.07 \\ \hline
-    		\textsc{Greeedy-2 + Cplex} & 37.31 & 19.13 &  6.72 & 3.07 \\ \hline
+    		\textsc{Greeedy-1 + \textsc{Cplex}} & 37.78 & 19.59 &  6.72 & 3.07 \\ \hline
+    		\textsc{Greeedy-2 + \textsc{Cplex}} & 37.31 & 19.13 &  6.72 & 3.07 \\ \hline
 
@@
         	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches.
-moreover, Cplex could prove optimallity of all (192) instances, while \textsc{Cp} could not.
+moreover, \textsc{Cplex} could prove optimallity of all (192) instances, while \textsc{Cp} could not.
 It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.

### 2020-10-09 doc/paper.tex
tables added

@@
 	\begin{itemize}
-		\item \emph{topologically-based benchmarks}.
+		\item \emph{topologically-based related weights}.
 For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$.
@@
 In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.
-		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
+		\item \emph{point-based related weights:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
 Based on this number, we assign prices to the vertices on the following way:
@@
 
-      After conducting preliminary results, we decided to use the following parameters for our algorithms:
-      \begin{itemize}
-        \item \textsc{Greedy + \textsc{Cplex}} parameters: $K = 0.05 \cdot n$.
-      \end{itemize}
+      After conducting preliminary results, for
+        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = 0.05 \cdot n$.
+
      The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
@@
         	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
-        \end{itemize}  and 6 heuristic approaches:
+            \item and 4 heuristic approaches:
            \begin{itemize}
-           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
+           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
             %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
-            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$,
-            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
+            \item two \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy-1}+\textsc{Cplex} and 
+            \textsc{Greedy-2}+\textsc{Cplex}. 
         \end{itemize}
-         From our results, we noticed that there is no significant difference between the results of \textsc{Greedy-2} and \textsc{Greedy-3}.
-Therefore, we report only the results of \textsc{Greedy-2} algorithm.
+    \end{itemize}
+
          Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab: t_w0} and Table~\ref{tab: t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
@@
 If an asterisk is given, i means taht optimality is proven for all instances of considered subgroup.
-         \begin{table}
-         \centering
-         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
-         	\hline
-         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
-         	\hline
-            \multicolumn{1}{|c|}{}&
-            \multicolumn{2}{|c|}{$Small$}&
-            \multicolumn{2}{|c|}{$Large$} \\
-            \hline	
-         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
-            \textsc{Cplex} & 15.93* & 8.12 & 2.62* & 1.38 \\ \hline
-            \textsc{Cp} &  16.04 & 8.24 &  2.62*  & 1.38\\ \hline
-         	\textsc{Greeedy-1} & 22.04  & 12.02 & 3.38   & 1.59 \\ \hline
-         	\textsc{Greeedy-2} & 19.97  & 9.60  &  3.51 & 1.80\\ \hline
-         	\textsc{Greeedy-1 + \textsc{Cplex}}  & 18.49 &  9.56  & 3.34 & 1.41 \\ \hline
-         	\textsc{Greeedy-2 + \textsc{Cplex}}  & 18.39 & 8.96 &  3.32 & 1.29 \\ \hline
 
-         	\hline
+     \begin{table}[]
+     	\begin{tabular}{l|lllllll|}
+     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
+     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
+     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
+     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
+     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
      	\end{tabular}
-         \caption{Results of different combinations of the algorithms.} \label{tab: t_w0}
      \end{table}
 
-       \begin{table}
-    	\centering
-    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
-    		\hline
-    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
-    		\hline
-    		\multicolumn{1}{|c|}{}&
-    		\multicolumn{2}{|c|}{$Small$}&
-    		\multicolumn{2}{|c|}{$Large$} \\
-    		\hline	
-    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
-    		\textsc{Cplex} & 36.03* & 19.04 & 6.72* & 3.07 \\ \hline
-    		\textsc{Cp} & 36.03* & 19.04 & 6.72* &  3.07 \\ \hline
-    		\textsc{Greeedy-1} &39.28  & 19.55 & 6.76 & 3.06 \\ \hline
-    		\textsc{Greeedy-2} & 40.92 & 19.54 & 6.76 & 3.06 \\ \hline
-    		\textsc{Greeedy-1 + \textsc{Cplex}} & 37.78 & 19.59 &  6.72 & 3.07 \\ \hline
-    		\textsc{Greeedy-2 + \textsc{Cplex}} & 37.31 & 19.13 &  6.72 & 3.07 \\ \hline
+      \begin{table}[]
+      	\begin{tabular}{l|lllllll}
+      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
+      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
+      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
+      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
+      	\end{tabular}
+      \end{table}
 
-    		\hline
+     \begin{table}[]
+     	\begin{tabular}{l|lllllll}
+     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
+     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
+     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
+     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
      	\end{tabular}
-    	\caption{Result of different combinations of the algorithms.} \label{tab: t_w1}
      \end{table}
+
+    \begin{table}[]
+ 	  \begin{tabular}{l|lllllll}
+ 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+ 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
+ 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
+ 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
+ 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
+ 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
+ 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
+ 	\end{tabular}
+   \end{table}
+
         From the numerical results, we observe the following conclusions:

### 2020-10-10 doc/paper.tex
scaling of tables
some work

@@
       After conducting preliminary results, for
-        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = 0.05 \cdot n$.
+        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$.
 
@@
         	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
-            \item and 4 heuristic approaches:
+            \item 4 heuristic approaches:
            \begin{itemize}
-           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
+           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2}, respectively;
             %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
@@
      \begin{table}[]
-     	\begin{tabular}{l|lllllll|}
+     	\centering
+     	 \scalebox{0.85}{
+     	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
@@
      		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
-     	\end{tabular}
+     	\end{tabular}}
      \end{table}
@@
       \begin{table}[]
-      	\begin{tabular}{l|lllllll}
+      	\centering
+      	\scalebox{0.85}{
+      	\begin{tabular}{l|lllllll} \hline
       		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
@@
       		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
-      	\end{tabular}
+      	\end{tabular}}
       \end{table}
@@
      \begin{table}[]
-     	\begin{tabular}{l|lllllll}
+      \centering
+       \scalebox{0.85}{
+     	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
@@
      		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
-     	\end{tabular}
+     	\end{tabular}}
      \end{table}
@@
     \begin{table}[]
- 	  \begin{tabular}{l|lllllll}
+    	\centering
+    	\scalebox{0.85}{
+ 	  \begin{tabular}{l|lllllll} \hline
  		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
@@
  		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
- 	\end{tabular}
+ 	\end{tabular}}
    \end{table}
@@
         \end{itemize}
-          \fxnote{TODO: generisati plotove za vremena svakog od algoritama (da se vidi da je greedy brzi -- nadamo se)}
+          \fxnote{TODO: Milan: generisati plotove za vremena svakog od algoritama, takodje generisati plotove koji pokazuju procenat pokrivenosti optimalnih rjesenja CPLEX-a...}
 

### 2020-10-10 doc/paper.tex
update

@@
      \end{itemize}
-     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set. In overall, we have 192 polygons. 
-	We included two kind of weights into each of (192) polygons:
+     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons. 
+	We included two kind of weights into each of (194) polygons:
 	\begin{itemize}
-		\item \emph{topologically-based related weights}.
-For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$.
-Then, $w_i := \frac{l_i + l_{i+1}}{2}$.
-This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$.
-This implies that the range of camera $i$ has to be larger, which again means that it has a higher price.
-In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.
-		\item \emph{point-based related weights:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
-Based on this number, we assign prices to the vertices on the following way:
+		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$.
+Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$.
+This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
+This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,.
+a higher price.
+In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
+		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
+Based on this, we assign prices to each vertex on the following way:
 		\begin{equation}
-		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
+		w_i = n \cdot \frac{|V(i)|}{|D(P)|}, i=1,...,n.
 		\end{equation}
@@
       All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB.
-The maximum computation time of each of our algorithms was set to 5 min.
+The maximum computation time of each of our algorithms was set to $5\ min$.
 
@@
      	\end{tabular}}
+        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}
      \end{table}
@@
       	\end{tabular}}
+         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}
       \end{table}
@@
      	\end{tabular}}
+          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.}
      \end{table}
@@
  	\end{tabular}}
+    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}
    \end{table}

### 2020-10-10 doc/paper.tex
update

@@
      \begin{itemize}
-     	 \item \emph{MinArea} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
+     	 \item \emph{MinArea} instances:\fxnote{TODO: Milan: main characteristics, why they differ from others}
      	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
@@
 
-         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab: t_w0} and Table~\ref{tab: t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.
-Each of the tables is additionally  subdivided by a vertical line into two parts, depending on the case if we consider \emph{small} or \emph{large} polygons for a specific weight.
-         For each of the algorithm  we reported average quality and average standard deviation ($\sigma$) over all instances (96 instances) of the considered subgroup.
-If an asterisk is given, i means taht optimality is proven for all instances of considered subgroup.
+         Summarized numerical results for each of our 6 variants of our algorithm are displayed 
+         in Tables~\ref{small_w0} --\ref{large_w1}.
+For each table, the average results are reported for each subset of instances grouped w.r.t.
+a specific kind of instances and a specific weight (97 instances per each group).
+Each of the tables list the considered algorithms in the first column.
+Starting with column two,  each of the lines provide detailed statistics for respective algorithm.
+The statistics report: the average solution quality ($\bar{|s|}$), the average time ($\bar{t}[s]$), the average number of guards which are included in each of the solutions ( $\bar{|g|}$), the number of solutions which match to the optimum solutions (\#hitsMinH), standard deviation of the obtained solutions w.r.t.
+optimal solutions ($\sigma(Opt)$), then the number of minimal solutions w.r.t.
+the four heuristics achieved by the respective algorithm (\#hitsMinH), standard deviation w.r.t.
+best solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).
 
@@
      	\centering
-     	 \scalebox{0.85}{
+     	 \scalebox{0.83}{
      	\begin{tabular}{l|lllllll}    \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
-     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
-     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
-     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
-     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
-     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
+     		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
+     		\textsc{Greedy-1}             & 22.63  & 0.002    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
+     		\textsc{Greedy-2}          & 19.97  & 0.002    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
+     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
+     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.004    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
      	\end{tabular}}
-        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}
+        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}\label{small_wo}
      \end{table}
@@
       	\centering
-      	\scalebox{0.85}{
+      	\scalebox{0.83}{
       	\begin{tabular}{l|lllllll} \hline
       		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
-      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
-      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
-      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
-      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
+      		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
+      		\textsc{Greedy-1}             & 39.28  & 0.001    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
+      		\textsc{Greedy-2}          & 40.92  & 0.001    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
+      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
+      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.003    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
       	\end{tabular}}
-         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}
+         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
       \end{table}
@@
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
-     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
-     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
@@
      	\end{tabular}}
-          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.}
+          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{largel_wo}
      \end{table}
@@
  		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
- 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
- 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
+ 		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
+ 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
  		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
@@
  	\end{tabular}}
-    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}
+    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{small_w1}
    \end{table}
 
-        From the numerical results, we observe the following conclusions:
+        From the numerical results, we observe the following conclusions concerning exact solving:
         \begin{itemize}
-        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches.
-moreover, \textsc{Cplex} could prove optimallity of all (192) instances, while \textsc{Cp} could not.
-It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.
-        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}.
-        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
+        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
+        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with signifficanlty more time than required from \textsc{Cplex};
+        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantly which can be seen  by the respective avg.
+runtime and the number of optimal solutions found (67/97).
         \end{itemize}
-          \fxnote{TODO: Milan: generisati plotove za vremena svakog od algoritama, takodje generisati plotove koji pokazuju procenat pokrivenosti optimalnih rjesenja CPLEX-a...}
-
+     From the numerical results, we observe the following conclusions concerning heuristic solving:
+     \begin{itemize}
+     	\item \fxnote{TODO...}
+     \end{itemize}
 	\section{Conclusions and Future Work}

### 2020-10-10 doc/paper.tex
describing results

@@
 best solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).
+An asterisk in front of a number means that the exact approach  could prove optimality in all cases.
 
@@
         	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantly which can be seen  by the respective avg.
-runtime and the number of optimal solutions found (67/97).
+runtime and the number of proven optimal solutions found (67/97).
         \end{itemize}
@@
      \begin{itemize}
-     	\item \fxnote{TODO...}
+     	\item  In case of the instances that include small-area polygons ($Minarea$) and weight $W0$: A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature  in this case, the best performing heuristic algorithms is  \textsc{Greedy-2+Cplex} which needs two ties time to finish than the pure greedy methods.
+The avg.
+runtimes of all four greedy methods is an order of magnitude lower than the avg.
+runtime of \textsc{Cplex}.
+Pure greedy methods deliver solutions of reasonable quality which quality is within 20\% of the quality of optimal solutions for the runtime which is7-8 times that that of \textsc{Cplex}.
+     	\item  In case of the instances that include small-area polygons and weight $W1$: the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver the solutions which are within 3\% of the optimum ones.
+     	The pure greedy method \textsc{Greedy-1} was able to outperform the results of \textsc{Greedy-2}.
+These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but with 3 times lower runtime.
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$: exact approach \textsc{Cplex} is a clear winner concerning avg solutions' quality as well as the avg.
+runtimes;  the best heuristic algorithm is \textsc{Greedy-2 +Cplex}.
+THe pure \textsc{Greedy-1} outperforms the pure greedy \textsc{Greedy-2}.
+\fxnote{TODO: not finished}
+     	\item abc
      \end{itemize}

### 2020-10-10 doc/paper.tex
work on description of the results

--- 2020-10-10 doc/paper.tex
@@
         	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
-        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with signifficanlty more time than required from \textsc{Cplex};
-        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantly which can be seen  by the respective avg.
-runtime and the number of optimal solutions found (67/97).
+        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with signifficanlty more time than the time required from \textsc{Cplex};
+        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantlly, which can be seen  by the respective avg.
+runtime and the number of proven optimal solutions found (67/97).
         \end{itemize}
@@
      \begin{itemize}
-     	\item \fxnote{TODO...}
+     	\item  In case of the instances that include small-area polygons ($Minarea$) and weight $W0$: A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
+In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs two times lower avg.
+runtime to finish than the pure greedy methods.
+The avg.
+runtimes of all four greedy methods is an order of magnitude lower than the avg.
+runtime of \textsc{Cplex}.
+Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs time which is 7-8 times lower then the avg.
+runtime of \textsc{Cplex}.
+     	\item  In case of the instances that include small-area polygons and weight $W1$: the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
+     	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
+These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less time.
+Te result of \textsc{Greedy-1} match just in two cases to the optimum.
+
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$: exact approach \textsc{Cplex} is a clear winner concerning avg solutions' quality as well as the avg.
+runtimes;  the best heuristic algorithm w.r.t.
+solution quality is \textsc{Greedy-2 +Cplex}.
+It also match in the most cases (on 6 instances) to the optimum results.
+Its avg.
+results are within 22\% of the avg.
+of  optimal solutions.
+The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}.
+The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
+     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$: the best heuristic algorithms w.r.t.
+solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions.
+Slightly worse that it are \textsc{Greedy-1} and \textsc{Greedy-2}.
+The obtained (heuristic) solutions of the two approaches are within 1\% of optimal solutions and they are
+     	able to reach the quality of the optimal solution in 92 instances.
+Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches.
+However, the avg.
+runtime for \textsc{Cp} is a bit higher that the runtime of the heuristic approaches.
+     	\item \fxnote{TODO: pokrivenost...}
      \end{itemize}
+
 	\section{Conclusions and Future Work}

### 2020-10-10 doc/paper.tex
update

@@
          Summarized numerical results for each of our 6 variants of our algorithm are displayed 
-         in Tables~\ref{small_w0} --\ref{large_w1}.
+         in Tables~\ref{small_wo} --\ref{large_w1}.
 For each table, the average results are reported for each subset of instances grouped w.r.t.
@@
  	\end{tabular}}
-    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{small_w1}
+    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{large_w1}
    \end{table}
@@
      \begin{itemize}
-     	\item  In case of the instances that include small-area polygons ($Minarea$) and weight $W0$: A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
+     	\item  In case of the instances that include small-area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
 In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs two times lower avg.
@@
 runtime of \textsc{Cplex}.
-     	\item  In case of the instances that include small-area polygons and weight $W1$: the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
+     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~(\ref{small_w1}): the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
@@
 
-     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$: exact approach \textsc{Cplex} is a clear winner concerning avg solutions' quality as well as the avg.
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): exact approach \textsc{Cplex} is a clear winner concerning avg solutions' quality as well as the avg.
 runtimes;  the best heuristic algorithm w.r.t.
@@
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
-     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$: the best heuristic algorithms w.r.t.
+     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
 solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions.
-Slightly worse that it are \textsc{Greedy-1} and \textsc{Greedy-2}.
+Slightly worse results are \textsc{Greedy-1} and \textsc{Greedy-2}.
 The obtained (heuristic) solutions of the two approaches are within 1\% of optimal solutions and they are

### 2020-10-10 doc/paper.tex
computational section: further work

@@
      \end{itemize}
-     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons. 
-	We included two kind of weights into each of (194) polygons:
+     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set.
+In overall, we have 194 polygons.
+	We included two kind of weights into each of (194) instances:
 	\begin{itemize}
@@
 Starting with column two,  each of the lines provide detailed statistics for respective algorithm.
-The statistics report: the average solution quality ($\bar{|s|}$), the average time ($\bar{t}[s]$), the average number of guards which are included in each of the solutions ( $\bar{|g|}$), the number of solutions which match to the optimum solutions (\#hitsMinH), standard deviation of the obtained solutions w.r.t.
+The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$), the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#hitsMinH), standard deviation of the obtained solutions w.r.t.
 optimal solutions ($\sigma(Opt)$), then the number of minimal solutions w.r.t.
@@
      	\begin{tabular}{l|lllllll}    \hline
-     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
-     		\textsc{Greedy-1}             & 22.63  & 0.002    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
-     		\textsc{Greedy-2}          & 19.97  & 0.002    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
-     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
-     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.004    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
+     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\ \hline
+     		\textsc{Greedy-1}             & 22.63  & \textbf{0.002}    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
+     		\textsc{Greedy-2}          & 19.97  & \textbf{0.002}    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
+     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & \textbf{2/97}      & 0.30    & \textbf{57/97}      & \textbf{0.06}     \\
+     		   \textsc{Greedy-2+Cplex} & \textbf{18.39}  & 0.004    & \textbf{19.59}     & 0/97      & \textbf{0.26}    & 53/97      & 0.04  \\ \hline 
      	\end{tabular}}
@@
       	\begin{tabular}{l|lllllll} \hline
-      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+      		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
       		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
-      		\textsc{Greedy-1}             & 39.28  & 0.001    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
-      		\textsc{Greedy-2}          & 40.92  & 0.001    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
-      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
-      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.003    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
+      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\ \hline
+      		\textsc{Greedy-1}             & 39.28  & \textbf{0.001}    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
+      		\textsc{Greedy-2}          & 40.92  & \textbf{0.001}    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
+      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & \textbf{4/97}      & 0.21    & 19/97      & \textbf{0.08}     \\
+      		   \textsc{Greedy-2+Cplex} & \textbf{37.31}  & 0.003    & \textbf{19.58}     & 2/97      & \textbf{0.15}    & \textbf{81/97}     & {0.19}   \\ \hline  
       	\end{tabular}}
@@
      	\begin{tabular}{l|lllllll} \hline
-     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
-     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
+     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
      		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
-     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
-     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
-     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
+     		\textsc{Greedy-2}          & 3.52   & \textbf{0.32}    & 6.61      & 2/97      & 0.10    & \textbf{28/97}      & 0.08     \\
+     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & \textbf{0.08}    & 25/97      & \textbf{0.04}     \\
+     		   \textsc{Greedy-2+Cplex} & \textbf{3.32}   & 0.33    & \textbf{6.81}      & \textbf{6/97}      & \textbf{0.08}    & 25/97      & \textbf{0.04}  \\ \hline   
      	\end{tabular}}
-          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{largel_wo}
+          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{large_w0}
      \end{table}
@@
  	  \begin{tabular}{l|lllllll} \hline
- 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+ 		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
  		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
- 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
- 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
- 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
- 		\textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
- 		\textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
+ 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
+ 		\textsc{Greedy-1}             & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
+ 		\textsc{Greedy-2}          & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
+ 		\textsc{Greedy-1+Cplex}  & \textbf{6.73}   & 0.32    & \textbf{6.45}      & \textbf{96/97}     & \textbf{0.01}    & \textbf{96/97}      & \textbf{0.03}     \\
+ 		\textsc{Greedy-2+Cplex} & 7.42   & \textbf{0.31}    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
  	\end{tabular}}
@@
      	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~(\ref{small_w1}): the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
+Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
@@
 The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}.
+It is interesting that \textsc{Greedy-1} chooses in average a  higher number of guards in comparison to the avg.
+number of guards of \textsc{Greedy-2}.
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.

### 2020-10-10 doc/paper.tex
added instances
Conclusions added

@@
 
- We used two different kind of benchmark sets:
+ We used two different kind of benchmark sets from~\cite{tomas2006visibility}:
      \begin{itemize}
@@
 
-     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): exact approach \textsc{Cplex} is a clear winner concerning avg solutions' quality as well as the avg.
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning avg solutions' quality as well as the avg.
 runtimes;  the best heuristic algorithm w.r.t.
@@
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
+Reason for that can be seen in the used discretization of the polygon.
+For the polygons with a larger area, more points is involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller.
      	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
@@
 The obtained (heuristic) solutions of the two approaches are within 1\% of optimal solutions and they are
-     	able to reach the quality of the optimal solution in 92 instances.
+     	able to reach the quality of the optimal solution for 92 instances.
 Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches.
@@
      \end{itemize}
+    \fxnote{Milan: generisati dijagrame za pokrivenst i vrijeme izvrsavanja...}
+	\section{Conclusions and Future Work}
+	  In this work we have considered the Weighted Orthogonal Art Gallery Problem under regular grid discretization. 
+	  We have developed a novel greedy rule which provide a trade-off between the number of guards and the cost of  guards.
+Moreover, a hybrid of a greedy method and \textsc{Cplex} was proposed to make a maximal completion of the greedy solution returned by the greedy method supplemented by solving respective subproblem via \textsc{Cplex}.
+The performances of the heuristic approaches are compared to the exact ILP and CP approaches.
+From the computational experiments, heuristic approaches were highly efficient in terms of obtaining solutions of reasonable quality in an order of magnitude lower runtime than the exact approaches for the small-area polygons.
+For the large--area polygons, heuristic approaches were able to reach the quality of optimal solutions in almost all cases in cost of larger times than the ILP approach.
 
-	\section{Conclusions and Future Work}
+	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets such that considering different discretizations of polygons, for example, by Delaunay triangulation~\ref{lee1980two}.
 

### 2020-10-10 doc/paper.tex
minor fix
dopunjeni opisi eksperimenta.

@@
 Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$.
-This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
+This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
 This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,.
 a higher price.
-In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
+\fxnote{Ova naredna recenica mi je nepotrebna.}In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
 		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
@@
 		\begin{equation}
-		w_i = n \cdot \frac{|V(i)|}{|D(P)|}, i=1,...,n.
+		w_i = n \cdot \frac{|V(i)|}{|D(P)|},\ i=1,...,n.
 		\end{equation}
+    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher quality and thus of a higher price.
 	\end{itemize}
@@
          Summarized numerical results for each of our 6 variants of our algorithm are displayed
-         in Tables~\ref{small_wo} --\ref{large_w1}.
+         in Tables~\ref{small_wo} -- \ref{large_w1}.
 For each table, the average results are reported for each subset of instances grouped w.r.t.
@@
 Starting with column two,  each of the lines provide detailed statistics for respective algorithm.
-The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$), the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#hitsMinH), standard deviation of the obtained solutions w.r.t.
+The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t.
 optimal solutions ($\sigma(Opt)$), then the number of minimal solutions w.r.t.
-the four heuristics achieved by the respective algorithm (\#hitsMinH), standard deviation w.r.t.
-best solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).
+the four heuristics achieved by the respective algorithm (\#hitsMinH) and average standard deviation w.r.t.
+best (minimal) solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).
 An asterisk in front of a number means that the exact approach  could prove optimality in all cases.
+Best values in each column are bolded.
 
@@
         	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
-        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with signifficanlty more time than the time required from \textsc{Cplex};
-        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantlly, which can be seen  by the respective avg.
-runtime and the number of proven optimal solutions found (67/97).
+        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
+        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
         \end{itemize}
@@
      \begin{itemize}
-     	\item  In case of the instances that include small-area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
-In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs two times lower avg.
-runtime to finish than the pure greedy methods.
-The avg.
-runtimes of all four greedy methods is an order of magnitude lower than the avg.
-runtime of \textsc{Cplex}.
-Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs time which is 7-8 times lower then the avg.
-runtime of \textsc{Cplex}.
-     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~(\ref{small_w1}): the best heuristic appraoch is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
+     	\item  In case of the instances that include small--area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
+In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs two times lower average runtime to finish than the pure greedy methods.
+The average runtimes of all four greedy methods is an order of magnitude lower than the average runtime of \textsc{Cplex}.
+Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs time which is 7-8 times lower then the average runtime of \textsc{Cplex}.
+Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t.
+optimal solution is rather small.
+From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation.
+     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
 Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
+As it was the case with the case of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation is rather small.
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
 These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less time.
-Te result of \textsc{Greedy-1} match just in two cases to the optimum.
+The result of \textsc{Greedy-1} match just in two cases to the optimum.
 
-     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning avg solutions' quality as well as the avg.
-runtimes;  the best heuristic algorithm w.r.t.
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t.
 solution quality is \textsc{Greedy-2 +Cplex}.
-It also match in the most cases (on 6 instances) to the optimum results.
-Its avg.
-results are within 22\% of the avg.
-of  optimal solutions.
+It also matches in the most cases (on 6 instances) to the optimum results.
+Its average results are within 22\% of the average of  optimal solutions.
 The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}.
-It is interesting that \textsc{Greedy-1} chooses in average a  higher number of guards in comparison to the avg.
-number of guards of \textsc{Greedy-2}.
+It is interesting that \textsc{Greedy-1} chooses in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}.
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
 Reason for that can be seen in the used discretization of the polygon.
-For the polygons with a larger area, more points is involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller.
+For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller.
      	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
@@
 Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches.
-However, the avg.
-runtime for \textsc{Cp} is a bit higher that the runtime of the heuristic approaches.
+However, the average runtime for \textsc{Cp} is a bit higher that the avg.
+runtimes of the heuristic approaches.
+Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
      	\item \fxnote{TODO: pokrivenost...}

### 2020-10-10 doc/paper.tex
some changes

@@
 An asterisk in front of a number means that the exact approach  could prove optimality in all cases.
-Best values in each column are bolded.
+Best values among heuristic approaches in each column are bolded.
 
@@
      	\item  In case of the instances that include small--area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
-In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs two times lower average runtime to finish than the pure greedy methods.
-The average runtimes of all four greedy methods is an order of magnitude lower than the average runtime of \textsc{Cplex}.
-Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs time which is 7-8 times lower then the average runtime of \textsc{Cplex}.
+In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods.
+The average runtimes of all four heuristic methods are an order of magnitude lower than the average runtime of \textsc{Cplex}.
+Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}.
 Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t.
@@
 Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
-As it was the case with the case of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation is rather small.
+As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation is rather small.
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
-These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less time.
+These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime.
 The result of \textsc{Greedy-1} match just in two cases to the optimum.
@@
 solution quality is \textsc{Greedy-2 +Cplex}.
-It also matches in the most cases (on 6 instances) to the optimum results.
+It also matches in the most cases (on 6 instances) to the optimum results w.r.t.
+other heuristic approaches.
 Its average results are within 22\% of the average of  optimal solutions.
 The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}.
-It is interesting that \textsc{Greedy-1} chooses in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}.
+It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}.
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
-Reason for that can be seen in the used discretization of the polygon.
-For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller.
+Reason for that can be seen in the used regular discretization of the polygon.
+For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
      	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
 solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions.
-Slightly worse results are \textsc{Greedy-1} and \textsc{Greedy-2}.
-The obtained (heuristic) solutions of the two approaches are within 1\% of optimal solutions and they are
+Slightly worse results are delivered by \textsc{Greedy-1} and \textsc{Greedy-2}.
+The obtained (heuristic) solutions of these two approaches are within 1\% of optimal solutions and they are
      	able to reach the quality of the optimal solution for 92 instances.
@@
 	  We have developed a novel greedy rule which provide a trade-off between the number of guards and the cost of  guards.
-Moreover, a hybrid of a greedy method and \textsc{Cplex} was proposed to make a maximal completion of the greedy solution returned by the greedy method supplemented by solving respective subproblem via \textsc{Cplex}.
+Moreover, a hybrid of a greedy method and \textsc{Cplex} was proposed to make a maximal completion of the greedy solution obtained by the greedy method supplemented by solving respective subproblem via \textsc{Cplex}.
 The performances of the heuristic approaches are compared to the exact ILP and CP approaches.
-From the computational experiments, heuristic approaches were highly efficient in terms of obtaining solutions of reasonable quality in an order of magnitude lower runtime than the exact approaches for the small-area polygons.
-For the large--area polygons, heuristic approaches were able to reach the quality of optimal solutions in almost all cases in cost of larger times than the ILP approach.
+From the computational experiments, the heuristic approaches were highly efficient in terms of obtaining solutions of reasonable quality in an order of magnitude lower runtime than the exact approaches for the small-area polygons.
+For the large--area polygons, heuristic approaches were able to reach the quality of optimal solutions in almost all cases but in cost of larger times than the ILP approach.
 
-	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets such that considering different discretizations of polygons, for example, by Delaunay triangulation~\ref{lee1980two}.
+	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets by considering different discretizations of polygons, for example, the Delaunay triangulation~\ref{lee1980two}.
 

### 2020-10-11 doc/paper.tex
add text, picture and chart

@@
 \usepackage{color}
+\usepackage{epsfig}
 
@@
 
-	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike dodaj gdje optimalan izbor cvorova pokriva poligon, i gdje optimalni izbor cvorova ne pokriva poligon...}
+	\fxnote{TODO: Milan: Treba prevesti na engleski}
+
+	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z.
+Na slici 1.1 pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena.
+Trokut na dnu poligona predstavlja nepokrivenu regiju.
+Poligon na slici 1.1 pod b) je pokriven kao i njegova diskretizacija.
+
+	\begin{figure}
+    	\centering
+    	\includegraphics[width=.7\linewidth]{slika1.eps}
+    	\caption{Polygon ...}
+    	\label{fig:covPncovDP}
+    \end{figure}
+
+	Izabrana rezolucija $\bigtriangleup_{x}\times\bigtriangleup_{y}$ predstavlja kompromis izmedju brzine i tacnosti.
+Odnosno, smanjenjem rezolucije povecava se tacnost rjesenje, ali se sporije pronalazi diskretizacija.
+Povecanjem rezolucije smanjuje se tacnost rjesenja, ali i vrijeme pronalazenja diskretizacije.
+
+	Couto et al.~\cite{couto2007exact} koristili su pomenutu diskretizaciju za problem ortogonalne galerije.
+U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282.
+Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivensort poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P).
+Oni su dodavali nove tačke u D(P) iz nepokrivenih regija kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona za sve poligone.
+Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gjde je n broj tjemena poligona.
+Dakle, ili je čitav poligon pokriven ili mali broj regija je nepokriveno optimalnim skupom stražara Z za D(P).
+U sekciji 4 će biti prikazana površina ovih nepokrivenih regija.
 
@@
      \begin{itemize}
-     	 \item \emph{MinArea} instances:\fxnote{TODO: Milan: main characteristics, why they differ from others}
-     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
+     	 \item \emph{MinArea} instances:\fxnote{TODO: Milan: Prevesti na engleski} MinArea poligoni malih povrsina su specificni po tome sto imaju "skucenu/usku" unutrasnjost.
+Ovi poligoni predstavljaju granicni slučaj kardinalnosti diskretizacije.
+Odnosno, mali broj tačaka regularne mreže će biti dodan u D(P) za MinArea poligon P.
+     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: Prevesti na engleski} Poligoni velikih povrsina su specificni po tome sto imaju "prostranu" unutrasnjost.
+Takodje, i ovi poligoni predstavljaju granicni slučaj kardinalnosti diskretizacije.
+Odnosno, veliki broj tačaka regularne mreže će biti dodan u D(P) za FAT poligon P.
      \end{itemize}
@@
      \end{itemize}
-    \fxnote{Milan: generisati dijagrame za pokrivenst i vrijeme izvrsavanja...}
+    \fxnote{Milan: generisati vrijeme izvrsavanja...--- Kog izvrsavanja?}
+
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=\textwidth]{grafikon1.eps}
+    	\caption{Polygon Coverage}
+    	\label{fig:cov}
+    \end{figure}
+
 	\section{Conclusions and Future Work}

### 2020-10-11 doc/paper.tex
komentari na Milanov tekst

@@
 	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z.
-Na slici 1.1 pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena.
+Na slici 1.1\fxnote{pogresna referenca 1.1, mislis na 1...} pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena.
 Trokut na dnu poligona predstavlja nepokrivenu regiju.
-Poligon na slici 1.1 pod b) je pokriven kao i njegova diskretizacija.
+Poligon na slici 1 pod b) je pokriven kao i njegova diskretizacija.
+\fxnote{Milane, mislm da ti slika pod a) ne odgovara svrsi.
+Recimo ovaj poligon se cak moze pokriti sa jednim covrom, jesam u pravu?
+Treba nam poligon koji se ne moze pokriti bilo kojim odabirom cvorova (cuvara)?}
 
@@
 U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282.
-Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivensort poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P).
+Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivenost poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P)\fxnote{Sta je sa ostalim poligonima koji nisu bili pokriveni?
+Koliki je procenat pokrivenosti bio u tom slucaju?
+Kako se ovo odnosi na druge diskretizacije, bilo je puno bolje ili?}.
 Oni su dodavali nove tačke u D(P) iz nepokrivenih regija kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona za sve poligone.
-Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gjde je n broj tjemena poligona.
+Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gdje je n broj tjemena poligona.
 Dakle, ili je čitav poligon pokriven ili mali broj regija je nepokriveno optimalnim skupom stražara Z za D(P).
@@
      \end{itemize}
-    \fxnote{Milan: generisati vrijeme izvrsavanja...--- Kog izvrsavanja?}
+    \fxnote{Milan: generisati vrijeme izvrsavanja svakog od algoritama, dakle, $x$-osa predstavlja sljedece parove: (Smallarea, W0), (Smllarea, W1), (FAT, W0), (FAT, W1), i onda za svaku od ovih kategorija, prikazi box-plotove za 6 nasih algoritama koji prikazuju njihova vremena izvrsavnja na $y$ osi (predstavi ih razlicitim bojama, ubaci i liegendu u gornjem desnom uglu) -- ove brojeve nadji u Tabelama 1-4,  kolona 3 ($t[s]$).
+U zavisnosti od prikaza, koristiti log skaliranje za y-osu....
+}
 
@@
     	\includegraphics[width=\textwidth]{grafikon1.eps}
-    	\caption{Polygon Coverage}
+    	\caption{Polygon Coverage \fxnote{Kako si podlijelio instance sa tezinama W0 i W1? Ovo je za Cplex? Ja bih prikazao ovo ipak sa dva dijagrama, jedan za W0, a drugi za W1)}}
     	\label{fig:cov}

### 2020-10-11 doc/paper.tex
update

@@
 Recimo ovaj poligon se cak moze pokriti sa jednim covrom, jesam u pravu?
-Treba nam poligon koji se ne moze pokriti bilo kojim odabirom cvorova (cuvara)?}
+Ubaciti tezine, i tacke diskretizacije}
 
@@
 Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
-As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation is rather small.
+As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation w.r.t.
+optimal solutions is rather small.
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
@@
 runtimes of the heuristic approaches.
-Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
+Again, average standard deviation for each heuristic method is rather small w.r.t.
+optimal solutions, indicating the good quality of the proposed algorithms.
      	\item \fxnote{TODO: pokrivenost...}

### 2020-10-11 doc/software/milan/pokrivenost.cpp
pokrivenost za W1

@@ -319,8 +319,8 @@ int main(int argc, char const *argv[])
   {
     auto start = high_resolution_clock::now();
     // ----------------------------read polygon---------------------------------
-    const string category = "small";
-    string filename = "min-" + std::to_string(file_number) + "-" + std::to_string(file_order);
+    const string category = "large";
+    string filename = "fat-" + std::to_string(file_number) + "-" + std::to_string(file_order);
     string location = "instance/" + category + "/" + filename + + ".pol";
 
     int n;
@@ -330,8 +330,8 @@ int main(int argc, char const *argv[])
     //print_polygon(p);
     
     //------------------------------read solution--------------------------------
-    const string category_s = "small-A-2-W0G0";
-    string filename_s = "woagp-min-" + std::to_string(file_number); //+ "-" + std::to_string(file_order)
+    const string category_s = "large-A-2-W1";
+    string filename_s = "woagp-fat-" + std::to_string(file_number); //+ "-" + std::to_string(file_order)
     
     string location_s = "../figure_output/" + category_s + "/" + filename_s + + ".out";
     string output = "cover/" + category_s + ".txt";

### 2020-10-11 doc/paper.tex
minor fix
dodao novu sliku i grafikone; mala korekcija teksta

--- 2020-10-11 doc/paper.tex
@@
 \usepackage{epsfig}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z.
-Na slici 1.1 pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena.
-Trokut na dnu poligona predstavlja nepokrivenu regiju.
-Poligon na slici 1.1 pod b) je pokriven kao i njegova diskretizacija.
+	Treba primjetiti da iz pokrivenosti diskretizacije D(P) optimalnim skupom stražara iz Z ne mora da slijedi pokrivenost poligona P istim skupom stražara Z.
+Na slici 1 pod a) prikazano je optimalno pokrivanje crvenim tačkam diskretizacije D(P).
+Crvene i bjele tačke na poligonu su tačke iz diskretnog skupa D(P).
+Ovo optimalno rješenje ne pokriva poligon sa slike.
+Poligon na slici 1 pod b) je optimalno pokriven, ali ovo pokrivanje nije optimalno pokrivanje njegove diskretizacije D(P).
 
-	\begin{figure}
+	\begin{figure}[t!]
     	\centering
-    	\includegraphics[width=.7\linewidth]{slika1.eps}
-    	\caption{Polygon ...}
-    	\label{fig:covPncovDP}
+    	\begin{subfigure}[t]{0.49\textwidth}
+        	\centering
+        	\includegraphics[height=1.7in]{slika1a.eps}
+        	\caption{Optimal coverage of discretization $D(P)$}
+    	\end{subfigure}%
+    	~ 
+    	\begin{subfigure}[t]{0.49\textwidth}
+        	\centering
+        	\includegraphics[height=1.7in]{slika1b.eps}
+        	\caption{Optimal coverage of polygon $P$}
+    	\end{subfigure}
+    	\caption{Optimal coverage of discretization $D(P)$ is not comparable to optimal coverage of polygon $P$.}
 	\end{figure}
@@
 U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282.
-Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivensort poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P).
-Oni su dodavali nove tačke u D(P) iz nepokrivenih regija kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona za sve poligone.
-Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gjde je n broj tjemena poligona.
-Dakle, ili je čitav poligon pokriven ili mali broj regija je nepokriveno optimalnim skupom stražara Z za D(P).
-U sekciji 4 će biti prikazana površina ovih nepokrivenih regija.
+Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivenost poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P)\fxnote{Sta je sa ostalim poligonima koji nisu bili pokriveni?} Za ostale poligone je bilo potrebno dodati prosječno 0.003·n+1.1 dodatnih tačaka u diskretizaciju kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona.
+Dakle nad testiranim uzorkom poligona, ili je citav poligon pokriven ili je mali broj regija nepokriveno optimalnim skupom stražara Z za D(P).
+U sekciji 4 će biti prikazane vrijednosti površina ovih nepokrivenih regija.
+\fxnote{Koliki je procenat pokrivenosti bio u tom slucaju?} \fxerror{Do ove info ne mogu da dodjem} \fxnote{Kako se ovo odnosi na druge diskretizacije, bilo je puno bolje ili?} \fxnote{Treba pregledati literaturu.
+Pitanje je koliko je ljudi pokusavalo ovom metodologijom dopunjavati diskretiyaciju kako bi dosli do optimalnog rjesenja - ja bih izbjegao o ovom pricati/pisati}.
 
@@
 a higher price.
-\fxnote{Ova naredna recenica mi je nepotrebna.}In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
 		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
@@
 runtimes of the heuristic approaches.
-Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
+Again, average standard deviation for each heuristic method is rather small w.r.t.
+optimal solutions, indicating the good quality of the proposed algorithms.
      	\item \fxnote{TODO: pokrivenost...}
      \end{itemize}
-    \fxnote{Milan: generisati vrijeme izvrsavanja...--- Kog izvrsavanja?}
+
+    \fxnote{TODO: Da li na dijagramima treba nešto dodatno napisati, smanjiti ih...}
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=\textwidth]{grafikon1.eps}
+    	\caption{Polygon coverage for the type of weight W0.}
+    	\label{fig:covw0}
+    \end{figure}
 
@@
     	\centering
-    	\includegraphics[width=\textwidth]{grafikon1.eps}
-    	\caption{Polygon Coverage}
-    	\label{fig:cov}
+    	\includegraphics[width=\textwidth]{grafikon2.eps}
+    	\caption{Polygon coverage for the type of weight W1.}
+    	\label{fig:covw1}
+    \end{figure}
+    \fxnote{TODO: Vrijeme izvrsavanja je skalirano logaritmaski}
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=\textwidth]{grafikon3.eps}
+    	\caption{Polygon coverage for the type of weight W1.}
+    	\label{fig:timealg}
     \end{figure}

### 2020-10-12 doc/paper.tex
update

@@
     	\end{subfigure}
-    	\caption{Optimal coverage of discretization $D(P)$ is not comparable to optimal coverage of polygon $P$.}
+    	\caption{Optimal coverage of discretization $D(P)$ does not imply a coverage of polygon $P$.}
 	\end{figure}
@@
 For a point from $D(P)$ we say that it is \textit{incorrect} if it is not covered by any guard from the current partial solution $s^{ps}$.
-Let us denote by $incorrect_{total}(s^{sp})$ the total number of incorrect points from discretization $D(P)$ w.r.t.
+Let us denote by $incorrect_{total}(s^{ps})$ the total number of incorrect points from discretization $D(P)$ w.r.t.
 $s^{ps}$.
@@
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex $v$, $s[v]$:  list of points covered by $v$
+          		\State \textbf{Input:} vertex $v$, $S[v]$:  list of points covered by $v$
           		\State \textbf{Output:} updated structures: coveredPoints and numberOfGuards
@@
           	\begin{algorithmic}[1]
-          		\State \textbf{Input:} vertex $v$, $s[v]$:  list of points covered by $v$
+          		\State \textbf{Input:} vertex $v$, $S[v]$:  list of points covered by $v$
           		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
@@
      \begin{itemize}
-     	 \item \emph{MinArea} instances:\fxnote{TODO: Milan: Prevesti na engleski} MinArea poligoni malih povrsina su specificni po tome sto imaju "skucenu/usku" unutrasnjost.
-Ovi poligoni predstavljaju granicni slučaj kardinalnosti diskretizacije.
-Odnosno, mali broj tačaka regularne mreže će biti dodan u D(P) za MinArea poligon P.
-     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: Prevesti na engleski} Poligoni velikih povrsina su specificni po tome sto imaju "prostranu" unutrasnjost.
-Takodje, i ovi poligoni predstavljaju granicni slučaj kardinalnosti diskretizacije.
-Odnosno, veliki broj tačaka regularne mreže će biti dodan u D(P) za FAT poligon P.
+     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas.
+They are specific because they have tiny interior.
+They presents a boundary case for the caardinality of set $D(P)$ which means that a very few points will be added in $D(P)$.
+     	 \item \emph{FAT} instances:  includes polygons of large areas.
+They are specific because their interior is wide.
+In this case, a large number of points of relgular grid will be included into $D(P)$.
      \end{itemize}
@@
 optimal solutions, indicating the good quality of the proposed algorithms.
-     	\item \fxnote{TODO: pokrivenost...}
+     	\item  Concerning the percentage of covering of polygons for the best solutions (found by \textsc{Cplex}) we
+     	noticed that  \textsc{FAT} instances are covered in almost all cases (see Fig.\ref{fig:covw0} and \ref{fig:covw1} and the blue curve).
+Concerning the \textit{Smallarea} instances, it gets harder to cover all polygon and in allmost all cases the whole area of polygon $P$ cannot be covered.
+For these instances, we see that the solutions cover more regions of small--area polygons when weight $W1$ is involved then when $W0$ is considered ($\approx 93 \%$ vs.
+$\approx 85\%$).
+It can be argued by the fact that in weight $W0$ there exists many ties for weights of guards, and, therefore, more solutions with the minimum weight exist.
+     	Notice that this is not so often the case of the weight $W1$.
+
      \end{itemize}
 
-    \fxnote{TODO: Da li na dijagramima treba nešto dodatno napisati, smanjiti ih...}
+    \fxnote{TODO: Da li na dijagramima treba nešto dodatno napisati, smanjiti ih: Ucini da Fig.
+2,3 i 4 stanu na jednu stranu.
+Fig 4 je pogresna, obrnuio si kategorije.
+Treba da grupises rezultate izvrsavanja po tipu instance, a da u legendi stoje algoritmi...
+}
     \begin{figure}

### 2020-10-12 doc/paper.tex
minor fix

@@
 
-	Couto et al.~\cite{couto2007exact} koristili su pomenutu diskretizaciju za problem ortogonalne galerije.
+	%Couto et al.~\cite{couto2007exact} koristili su pomenutu diskretizaciju za problem ortogonalne galerije.
 U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282.
@@
 	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
-	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by IBM ILOG CP Optimizer~\cite{laborie2018ibm}.
+	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by \textit{IBM ILOG CP Optimizer}~\cite{laborie2018ibm}.
 In this case,  Constraint~(\ref{eq:const-3}) is transformed into

### 2020-10-12 doc/paper.tex
update

@@
         	\includegraphics[height=1.7in]{slika1a.eps}
-        	\caption{Optimal coverage of discretization $D(P)$}
+        	\caption{Optimal coverage of discretization $D(P)$. }
     	\end{subfigure}%
@@
 	\begin{align}
-	&\sum_{i=1}^n w_ix_i \longrightarrow \min \\
+	&\sum_{i=1}^n w_ix_i \longrightarrow \min  \label{eq:woagp-min}\\
 	&\mbox{s.t.} \\
@@
 These two functions allow fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and the vertex is then removed from the solution.
+
+ \begin{comment}
+
 	\begin{algorithm}[!t]
@@
           \end{algorithm}
-	 % \end{comment}
+	  \end{comment}
+
 \subsubsection{A Hybrid of the \textsc{Greedy + \textsc{Cplex}}}
@@
 		\begin{itemize}
-			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
+			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model~\ref{eq:woagp-min};
 			\item a complete solution $\bar {s^p}$ is obtained;
@@
 
-    \fxnote{TODO: Da li na dijagramima treba nešto dodatno napisati, smanjiti ih: Ucini da Fig.
-2,3 i 4 stanu na jednu stranu.
-Fig 4 je pogresna, obrnuio si kategorije.
-Treba da grupises rezultate izvrsavanja po tipu instance, a da u legendi stoje algoritmi...
-}
     \begin{figure}
-    	\centering
-    	\includegraphics[width=\textwidth]{grafikon1.eps}
+    	\centering\scalebox{0.9}{
+    	\includegraphics[width=\textwidth]{grafikon1.eps}}
     	\caption{Polygon coverage for the type of weight W0.}
@@
     	\centering
-    	\includegraphics[width=\textwidth]{grafikon2.eps}
+    	\centering\scalebox{0.9}{
+    	\includegraphics[width=\textwidth]{grafikon2.eps}}
     	\caption{Polygon coverage for the type of weight W1.}
@@
     \end{figure}
-    \fxnote{TODO: Vrijeme izvrsavanja je skalirano logaritmaski}
+
     \begin{figure}
@@
     	\includegraphics[width=\textwidth]{grafikon3.eps}
-    	\caption{Polygon coverage for the type of weight W1.}
+    	\caption{Avg. execution time of the compared algorithms.}
     	\label{fig:timealg}

### 2020-10-12 doc/paper.tex
update

@@
 		\item structure \texttt{set<Point> CoveredPoints} -- set of points from $D(P)$ that are covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to partial solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
-		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by guard $v$ , when $v$ is removed from partial solution; pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
+		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to partial solution; %pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by guard $v$ , when $v$ is removed from partial solution; %pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
 	\end{itemize}
- Although the time complexity of both functions is $O(|D(P)|)$, from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove} it can be noticed that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
+ Although the time complexity of both functions is $O(|D(P)|)$, % from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove}
+  it can be noticed that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
 These two functions allow fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and the vertex is then removed from the solution.

### 2020-10-12 doc/paper.tex
update

--- 2020-10-12 doc/paper.tex
@@
 		%\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
-		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of guards in solution which cover that point;
-		\item structure \texttt{set<Point> CoveredPoints} -- set of points from $D(P)$ that are covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex $v$, when $v$  is added to partial solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
-		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by guard $v$ , when $v$ is removed from partial solution; pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
+		\item structure \texttt{numberOfGuards} -- which is a map structure, where each point from $D(P)$ is mapped to the number of guards in solution which cover that point;
+		\item structure \texttt{CoveredPoints} -- which keeps a set of points from $D(P)$ that are covered by the partial solution;
+		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points from $D(P)$ covered by vertex $v$, when $v$  is added to partial solution; %pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by $v$ , when $v$ is removed from partial solution; %pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
 	\end{itemize}
- Although the time complexity of both functions is $O(|D(P)|)$, from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove} it can be noticed that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
-These two functions allow fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and the vertex is then removed from the solution.
+ Although the time complexity of both functions is $O(|D(P)|)$, % from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove}
+  it is easy to notice that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
+These two functions allow also a fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and then being removed from the solution.
 

### 2020-10-12 doc/paper.tex
update in Section 3.1.3

@@
 	In order to enable fast calculation of greedy functions described in previous subsections, we noticed that it could be useful to allow fast updating of the number of uncovered vertices.
-Therefore, we introduced two useful structures and two auxiliary functions:
+Therefore, we introduced two useful structures: %and two auxiliary functions:
 	\begin{itemize}
@@
 		\item structure \texttt{numberOfGuards} -- which is a map structure, where each point from $D(P)$ is mapped to the number of guards in solution which cover that point;
-		\item structure \texttt{CoveredPoints} -- which keeps a set of points from $D(P)$ that are covered by the partial solution;
-		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points from $D(P)$ covered by vertex $v$, when $v$  is added to partial solution; %pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
-		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by $v$ , when $v$ is removed from partial solution; %pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
+		\item structure \texttt{CoveredPoints} -- which is a set structure which keeps the points from $D(P)$ that are covered by the partial solution;
+		%\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures %\texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by vertex $v$, when $v$  is being added to partial solution; %pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
+		%\item function \texttt{updateCoveredPointsRemove(vertex v)} -- does the update of structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by $v$ , when $v$ is removed from partial solution; %pseudocode  is shown in Algorithm \ref{alg:updateCoveredPointsRemove}.
 	\end{itemize}
- Although the time complexity of both functions is $O(|D(P)|)$, % from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove}
-  it is easy to notice that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
+  When vertex $v$ is being added to partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by $v$. 
+  When $v$ is removed from partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by $v$.
 These two functions allow also a fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and then being removed from the solution.
+
+% Although the time complexity of both functions is $O(|D(P)|)$, % from Algorithms \ref{alg:updateCoveredPointsAdd} and \ref{alg:updateCoveredPointsRemove}
+ % it is easy to notice that they only depends on the number of points covered by the current vertex, which is expected to be significantly lower than $|D(P)|$.
 

### 2020-10-12 doc/paper.tex
update
Popravke na tekstu

@@
 	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.
-Note that set $S_i$ includes points $p\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$.
 For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
 In this way, our starting task is equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
-	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.
+	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that
+
+$$f(\mathcal{C}) = \sum_{S_i \in \mathcal{C}} c(S_i)$$
+
+is minimized.
+
 The ILP  model for the WSCP is already known from the literature, where  here adapted to WOAGP  as follows:
@@
 	&\sum_{i=1}^n w_ix_i \longrightarrow \min  \label{eq:woagp-min}\\
-	&\mbox{s.t.} \\
-	&\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
-	& x_j \in \{0,1\}, j \in V,
+	&\mbox{s.t.}\nonumber \\
+	&\sum_{j=1}^n a_{ij}x_j \geq 1,\ (\forall p_i\in D(P)) \label{eq:const-3}\\
+	& x_j \in \{0,1\},\ j\in\{1,2,\ldots,n\}\label{eq:const-4},
 	\end{align}
@@
 	$a_{ij} = \begin{cases}
-	1, p_i \in V(j), \\
-	0, \mbox{otherwise}
+	1, p_i \in S_j, \\
+	0, \mbox{otherwise}.
 	\end{cases}$
-	and $x_i = \begin{cases}
-	1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
-	0, \mbox{otherwise},
-	\end{cases}$ \\
+	 \\
 
-	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of polygon $P$.
-	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
+	Set $Z = \{v_j \in V\mid x_j=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
 	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
@@
 	\end{equation}
-	whereas the other constraints and the objective function are the same like in the above ILP model.
-Note that CP appraoch works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
+	whereas the other constraints and the objective function are the same as in the above ILP model.
+Note that CP approach works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
 	\section{Algorithmic Approaches for WOAGP}
@@
 			\State \textbf{Input:} an instance of a problem
-			\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
+			\State \textbf{Output:} A (feasible) non-expandable solution $s^{ps}$  (or reporting that no feasible solution exists)
 			\State $s^{ps} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
 			\While{$\text{Extend}(s^{ps}) \neq \emptyset$}
-			\State Select solution component $e \in  \text{Extend}(s^{ps})$ \hspace{0.3cm}//\,w.r.t.\  some criterion $g$
+			\State Select solution component $e \in  \text{Extend}(s^{ps})$  \  w.r.t.\  some criterion $g$
 			\State Extend $s^{ps}$ by $e$
@@
 $s^{ps}$.
-Note that  $incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps})$, where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set .
+Note that
+ \begin{equation}\label{eq:incorrect}
+ incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps}),
+ \end{equation}
+
+ where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set .
 Let $w_{total}$ be the total sum of all weights among all vertices.
@@
 	Ties occurred in the search are broken by using  price-per-unit heuristic which is stated as follows.
-	For each not yet considered vertex $v_i$, we denote the region of polygon $P$ that is visible from $v_i$ by $\emph{Surf}(v_j)$.
+	For each not yet considered vertex $v_i$, we denote the region of polygon $P$ that is visible from $v_i$ by $\emph{Surf}(v_i)$.
 As the next candidate to extend $s^{ps}$, we choose such a guard,  with the smallest ratio between the price and the visible surface area.
@@
 		\item structure \texttt{numberOfGuards} -- which is a map structure, where each point from $D(P)$ is mapped to the number of guards in solution which cover that point;
-		\item structure \texttt{CoveredPoints} -- which is a set structure which keeps the points from $D(P)$ that are covered by the partial solution;
+		\item structure \texttt{CoveredPoints} -- as a set structure which keeps the points from $D(P)$ that are covered by the partial solution;
 		%\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures %\texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by vertex $v$, when $v$  is being added to partial solution; %pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}.
@@
   When vertex $v$ is being added to partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by $v$.
-  When $v$ is removed from partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered only by $v$.
-These two functions allow also a fast calculation of the functions $f$ and  $incorrect_{total}$: a candidate vertex $v$ is temporary added to the partial solution, new status is checked and then being removed from the solution.
+  When $v$ is removed from partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by omitting all points which are covered only by $v$.
+These two functions allow also a fast calculation of  functions (\ref{eq:sp}) and  (\ref{eq:incorrect}): a candidate vertex $v$ is temporary added to the partial solution, new status is checked and then being removed from the solution.
 
@@
 	\begin{enumerate}
-		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $s^{ps}$ (therefore, $|s^{ps}| = K$);
+		\item Run a Greedy method up to $K$ iterations  to obtain a partial solution $s^{ps}$, where $K$ is a parameter of the algorithm.
 		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via \textsc{Cplex}:
 		\begin{itemize}
-			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model~\ref{eq:woagp-min};
-			\item a complete solution $\bar {s^p}$ is obtained;
+			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing ILP  model~(\ref{eq:woagp-min})--(\ref{eq:const-4});
+			\item a complete solution $\overline s$ is obtained;
 		\end{itemize}
-		\item Return $f(\bar {s^p})$.
+		\item Return $f(\overline s)$.
 	\end{enumerate}

### 2020-10-12 doc/paper.tex
update

@@
 In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets, which is MSCP.
-Analogously, WOAGP can be reduced to the \emph{Weighted Minimum Set Cover Problem} (WMSCP).
+Analogously, WOAGP can be reduced to the \emph{Weighted Minimum Set Cover Problem} (MWSCP).
 
@@
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
-	A comprehensive analysis of various greedy-like heuristics for the WMSCP was presented in \cite{vasko2016best}.
+	A comprehensive analysis of various greedy-like heuristics for the MWSCP was presented in \cite{vasko2016best}.
 	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
@@
 	\section{Exact methods}
-	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP  under regular grid discretization, which are used  in the rest of the paper.
+	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving MWSCP  under regular grid discretization, which are used  in the rest of the paper.
 	\subsection{Integer linear programming model}
@@
 
-The ILP  model for the WSCP is already known from the literature, where  here adapted to WOAGP  as follows:
+The ILP  model for the WSCP is already known from the literature~\cite{vazirani2013approximation}, where  here adapted to WOAGP  as follows:
 
@@
 	\section{Algorithmic Approaches for WOAGP}
+	\fxnote{Izbjegavati naslov do naslova a bez teksta izmedju...}
 	\subsection{Greedy approaches for solving WOAGP}
@@
 Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend current partial solution,  we choose one with the smallest greedy value and add it to the current solution until it becomes complete (i.e., it covers all  points from $D(P)$).
+A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}.
 
-	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}.
+	In the case of our problem, set Extend($s^{ps}$) includes those guards from set $V \setminus$ $s^{ps}$ that cover some points from $D(P)$ that are not yet covered by $s^{ps}$.
+Solution component of the problem is a guard.
+Extension of partial solution $s^{ps}$ by a vertex $v$ corresponds to adding $v$ into set $s^{ps}$.
 
@@
 
- where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set .
+ where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set.
 Let $w_{total}$ be the total sum of all weights among all vertices.
@@
 	\end{align}
-
+    where $|\emph{Surf}({v_i})|$ represents the area of surface $\emph{Surf}({v_i})$. 
 	In our experimental studies, we found out that this heuristic does not perform well on its own, but it represents a reasonable tie-breaking mechanism which boosts quality of the aforementioned greedy heuristics.
@@
 	\end{itemize}
-  When vertex $v$ is being added to partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by $v$.
+  When adding vertex $v$ into partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering only new points from $D(P)$ covered by $v$.
   When $v$ is removed from partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by omitting all points which are covered only by $v$.
@@
 
-\subsubsection{A Hybrid of the \textsc{Greedy + \textsc{Cplex}}}
+\subsubsection{A Hybrid of the \textsc{Greedy} and \textsc{Cplex}}
 	The performance of \textsc{Cplex}  sooner or later degrades w.r.t.
@@
 	\end{enumerate}
-
+    This method is, therefore, called \textsc{Greedy}+\textsc{Cplex}.
 	\begin{comment}
@@
 This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
-This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,.
+This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,.
 a higher price.
@@
         \begin{itemize}
-        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
+        	\item  exact approaches: CP and ILP approach. The later is, henceforth, called \textsc{Cplex};
             \item 4 heuristic approaches:
@@
 optimal solution is rather small.
-From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation.
+From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation w.r.t.
+optimal solutions.
      	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
@@
 Concerning the \textit{Smallarea} instances, it gets harder to cover all polygon and in allmost all cases the whole area of polygon $P$ cannot be covered.
-For these instances, we see that the solutions cover more regions of small--area polygons when weight $W1$ is involved then when $W0$ is considered ($\approx 93 \%$ vs.
+For these instances, we see that the solutions cover more regions of small--area polygons when weight $W1$ is considered then when considering $W0$ ($\approx 93 \%$ vs.
 $\approx 85\%$).
@@
 
-	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets by considering different discretizations of polygons, for example, the Delaunay triangulation~\ref{lee1980two}.
+	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets by considering different discretizations of polygons, for example, the Delaunay triangulation~\cite{lee1980two}.
 

### 2020-10-12 doc/paper.tex
Some improvements in the paper

@@
 a higher price.
-		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$.
-Based on this, we assign prices to each vertex on the following way:
+		\item \emph{point-based related weights} ($W1$): For each vertex $v_j$, based on the number of points in $D(P)$ that are visible from $v_j$, we assign prices to each vertex on the following way:
 		\begin{equation}
-		w_i = n \cdot \frac{|V(i)|}{|D(P)|},\ i=1,...,n.
+		w_i = n \cdot \frac{|S_i|}{|D(P)|},\ i=1,...,n.
 		\end{equation}
-    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher quality and thus of a higher price.
+    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher spectrum and quality, and thus are more expensive. 
 	\end{itemize}
@@
 
-    \begin{figure}
+    \begin{figure}[!ht]
     	\centering\scalebox{0.9}{
@@
 
-    \begin{figure}
+    \begin{figure}[!ht]
     	\centering

### 2020-10-12 doc/paper.tex
remarks added

@@
 The appropriate discretization should be performed in such a way that if each point from the discretized set $D(P)$ is covered, then the whole polygon $P$ is covered.
-After the discretization is made, for each vertex of the polygon $P$, a set of visible points from $D(P)$ is determined.
+After the discretization is made, for each vertex of polygon $P$, a set of visible points from $D(P)$ is determined.
 In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets, which is MSCP.
-Analogously, WOAGP can be reduced to the \emph{Weighted Minimum Set Cover Problem} (MWSCP).
+Analogously, WOAGP can be reduced to the \emph{Minimum Weighted  Set Cover Problem} (MWSCP).
 
@@
 	more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
-	Tozoni et a.
+	Tozoni et al.
 ~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact \emph{Integer Linear Programming}  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
-	A comprehensive analysis of various greedy-like heuristics for the MWSCP was presented in \cite{vasko2016best}.
+	A comprehensive analysis of various greedy-like heuristics for the MWSCP \fxnote{da li je MWSC ili MSC?} was presented in \cite{vasko2016best}.
 	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.

### 2020-10-12 doc/paper.tex
more fxnode added
minor fix

@@
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
-	A comprehensive analysis of various greedy-like heuristics for the MWSCP \fxnote{da li je MWSC ili MSC?} was presented in \cite{vasko2016best}.
+	A comprehensive analysis of various greedy-like heuristics for the MWSCP  was presented in \cite{vasko2016best}.
 	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
@@
 	All intersection points of this regular grid with polygon $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
-The pseudocode which presents the building steps of the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.
+The pseudocode which presents the building steps of the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.\fxnote{Bolji opis Alg.
+1 potreban...}
 
@@
     	\centering
-    	\includegraphics[width=\textwidth]{grafikon3.eps}
+    	 \scalebox{0.9}{
+    	\includegraphics[width=\textwidth]{grafikon3.eps}}
     	\caption{Avg. execution time of the compared algorithms.}

### 2020-10-12 doc/paper.tex
update

@@
 
-	For a given polygon $P$, the \emph{Art Gallery Problem} (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
+	Given a polygon $P$, the \emph{Art Gallery Problem} (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.
 We say that the point $y$ is covered by the point $x$, or $y$ is visible from $x$.
@@
 Kahn et al.~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.
-In this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$.
+In the course of this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$.
 This restricted problem is known to be $\mathcal{NP}$--hard~\cite{schuchardt1995two,katz2008guarding}.
@@
 	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
-In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal.
+In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal\fxnote{ovo je malo cudno receno...
+Mozda bolje da se kaze da je to aproksimacioni faktor}.
 After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the MSCP is applied.
-An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in ~\cite{tomas2003approximation}.
+An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in~\cite{tomas2003approximation}.
 A major idea of this approach is exploring dominance of visibility regions to first detect pieces that are
-	more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
-	Tozoni et al.
-~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact \emph{Integer Linear Programming}  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
+	more difficult to guard. The same problem is solved in~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
+	Tozoni et al.~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact \emph{Integer Linear Programming}  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.
 Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
 	A comprehensive analysis of various greedy-like heuristics for the MWSCP  was presented in \cite{vasko2016best}.
-	More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
+	More detailed overview of the extensive literature regarding SCP \fxnote{nema skracenice za ovo nigdje uvedene prije} and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
 
@@
 		\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
-
 		\item The  greedy algorithm from \cite{chvatal1979greedy} and the novel greedy algorithm are hybridized with the ILP.
@@
 
-     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
+     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}. \fxnote{dodati link}
 	\subsection{Results and Discussion}

### 2020-10-12 doc/paper.tex
update teksta

@@
 	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
-In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal\fxnote{ovo je malo cudno receno...
-Mozda bolje da se kaze da je to aproksimacioni faktor}.
+In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the the solution is at most $O(\log n)$ times the optimal one.
 After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the MSCP is applied.
@@
 A comprehensive analysis of various greedy-like heuristics for the MWSCP  was presented in \cite{vasko2016best}.
-	More detailed overview of the extensive literature regarding SCP \fxnote{nema skracenice za ovo nigdje uvedene prije} and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
+	More detailed overview of the extensive literature regarding MSCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
 
@@
 	\subsection{The Regular Grid Discretization of Polygon}\label{sec:regulardiscretization}
-	The discretization $D(P)$ of the polygon $P$ is built as follows.
-Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow:
+	Building of the regular grid discretization $D(P)$ of the polygon $P$ is shown in Algorithm \ref{alg:discret}.
+At the beginning, the minimum bounding rectangle (usually called \textit{bounding box}) of $P$ is created.
+Then, the  regular grid, with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ and starting at the lower left corner of the bounding box of polygon $P$, is defined as follows:
 
@@
 	\end{algorithm}
+The algorithm further forms the whole regular grid of the bounding box (line 5.
+of the pseudocode) and finally, all points of the regular grid also belonging to $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
 
-	All intersection points of this regular grid with polygon $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
-The pseudocode which presents the building steps of the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.\fxnote{Bolji opis Alg.
-1 potreban...}
-
-	\fxnote{TODO: Milan: Treba prevesti na engleski}
-
-	Treba primjetiti da iz pokrivenosti diskretizacije D(P) optimalnim skupom stražara iz Z ne mora da slijedi pokrivenost poligona P istim skupom stražara Z.
-Na slici 1 pod a) prikazano je optimalno pokrivanje crvenim tačkam diskretizacije D(P).
-Crvene i bjele tačke na poligonu su tačke iz diskretnog skupa D(P).
-Ovo optimalno rješenje ne pokriva poligon sa slike.
-Poligon na slici 1 pod b) je optimalno pokriven, ali ovo pokrivanje nije optimalno pokrivanje njegove diskretizacije D(P).
+	It should be noticed that the optimal solution of WOAGP on $D(P)$ (i.e.
+an optimal covering of $D(P)$) is not necessarily  an optimal covering of $P$.
+In the simple example shown in Figure \ref{fig:example}, one can see that the guards placed on top left and top right vertices (shown in red color) cover all points from $D(P)$ (Figure \ref{fig:example} (a)), but not the whole polygon, since the gray triangle is not visible from any of these two points.
+The optimal solution value in this case is 1.2.
+Two red vertices in Figure \ref{fig:example} (b) optimally cover the whole polygon, but this covering is not optimal for $D(P)$, since the total sum of weights is larger (1.6).
 
@@
     	\end{subfigure}
-    	\caption{Optimal coverage of discretization $D(P)$ does not imply a coverage of polygon $P$.}
+    	\caption{Optimal coverage of discretization $D(P)$ does not imply a coverage of polygon $P$.}\label{fig:example}
 	\end{figure}
 
-	Izabrana rezolucija $\bigtriangleup_{x}\times\bigtriangleup_{y}$ predstavlja kompromis izmedju brzine i tacnosti.
-Odnosno, smanjenjem rezolucije povecava se tacnost rjesenje, ali se sporije pronalazi diskretizacija.
-Povecanjem rezolucije smanjuje se tacnost rjesenja, ali i vrijeme pronalazenja diskretizacije.
+	The chosen resolution  $\bigtriangleup_{x}\times\bigtriangleup_{y}$ is a compromise between the algorithm speed and accuracy.
+More precisely,  higher resolution increases the accuracy, but also the execution time and vice versa, lower resolution decreases the algorithm accuracy, but discretization is  made faster.
 
@@
 	\section{Exact methods}
-	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving MWSCP  under regular grid discretization, which are used  in the rest of the paper.
+	In this section we present the exact ILP  initially developed for MWSCP from ~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
 	\subsection{Integer linear programming model}
@@
 The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
-	The problem is related to the known MWSC problem as follows.
+	The problem is related to the known MWSCP  as follows.
 	Family $\mathcal{F}$ of nonempty sets consists of the sets
@@
 For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
-In this way, our starting task is equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
+In this way, our starting task is equivalent of finding a  covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$ of minimum weight, that is
 	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that
@@
 
-The ILP  model for the WSCP is already known from the literature~\cite{vazirani2013approximation}, where  here adapted to WOAGP  as follows:
+The ILP  model for the MWSCP ~\cite{vazirani2013approximation}   is  adapted to WOAGP  as follows:
 
@@
 Note that CP approach works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
-	\section{Algorithmic Approaches for WOAGP}
-	\fxnote{Izbjegavati naslov do naslova a bez teksta izmedju...}
+	\section{Algorithmic Approaches for solving WOAGP}
+	In this section we present the heuristic greedy approaches for solving WOAGP and their hybridization with the exact ILP method. 
 	\subsection{Greedy approaches for solving WOAGP}
@@
 Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
-Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend current partial solution,  we choose one with the smallest greedy value and add it to the current solution until it becomes complete (i.e., it covers all  points from $D(P)$).
+In order to extend current partial solution, among all candidates (solution components for expansion, that is not-yet-considered guards),  we choose one with the smallest greedy value and add it to the current solution.
+This procedure is repeating until the current solution becomes complete (i.e., all points from $D(P)$ are covered).
+
  A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}.
-
-	In the case of our problem, set Extend($s^{ps}$) includes those guards from set $V \setminus$ $s^{ps}$ that cover some points from $D(P)$ that are not yet covered by $s^{ps}$.
+	The set Extend($s^{ps}$) includes those guards from set $V \setminus$ $s^{ps}$ that cover some points from $D(P)$ that are not yet covered by $s^{ps}$.
 Solution component of the problem is a guard.
@@
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following criterion:
+	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following criterion:
 	\begin{align}\label{eq:Lovasz}
@@
 \begin{equation}\label{eq:sp}
-    f(s^{ps}) = \left|\bigcup_{i \in s^{ps}} S_i \right|.
+    f(s^{ps}) = \left|\bigcup_{v_i \in s^{ps}} S_i \right|.
     \end{equation}
@@
 
-\subsubsection{A Hybrid of the \textsc{Greedy} and \textsc{Cplex}}
+\subsection{A Hybrid of the \textsc{Greedy} and \textsc{Cplex}}
 	The performance of \textsc{Cplex}  sooner or later degrades w.r.t.
@@
 
- We used two different kind of benchmark sets from~\cite{tomas2006visibility}:
+ We used two different kind of benchmark sets from~\cite{tomas2006visibility}\fxnote{ima jos jedna referenca Partitioning Orthogonal Polygons by Extension
+of All Edges Incident to Reflex Vertices}:
      \begin{itemize}
-     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas.
-They are specific because they have tiny interior.
-They presents a boundary case for the caardinality of set $D(P)$ which means that a very few points will be added in $D(P)$.
-     	 \item \emph{FAT} instances:  includes polygons of large areas.
-They are specific because their interior is wide.
-In this case, a large number of points of relgular grid will be included into $D(P)$.
+     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas and tiny interior.
+They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
+     	 \item \emph{FAT} instances:  includes polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
      \end{itemize}
-     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set.
-In overall, we have 194 polygons.
-	We included two kind of weights into each of (194) instances:
+     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one $n$-ogon for each $n \in\{8,10,...,200\}$ has been considered and the appropriate discretization is made, which makes 97 instances per each benchmark set.
+In overall, we have 194 instances.
+Discretization is performed by using \fxnote{nismo nigdje ubacili, a ovdje bi trebalo CGAL}.
+
+	We included two kind of weights into each of 194  instances:
 	\begin{itemize}
 		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$.
-Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$.
+Then, we set
+\begin{equation}
+w_i := \frac{l_i + l_{i+1}}{2}.
+ \end{equation}
  This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
@@
 
-     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t.
+     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~ \ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t.
 solution quality is \textsc{Greedy-2 +Cplex}.
@@
 
+	\section*{Acknowledgements}
+This research is partially supported by Ministry for Scientific and Technological
+Development, Higher Education and Information Society, Government
+of Republic of Srpska, B\&H under the Project \fxnote{ime projekta}.
+
+	\section*{References}
 	\bibliographystyle{abbrv}

### 2020-10-13 doc/paper.tex
some polishing

@@
 	\end{algorithm}
-The algorithm further forms the whole regular grid of the bounding box (line 5.
-of the pseudocode) and finally, all points of the regular grid also belonging to $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
+The algorithm further forms the whole regular grid of the bounding box (line 5 of the pseudocode) and finally, all points of the regular grid that belong to $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
 
@@
 The optimal solution value in this case is 1.2.
-Two red vertices in Figure \ref{fig:example} (b) optimally cover the whole polygon, but this covering is not optimal for $D(P)$, since the total sum of weights is larger (1.6).
+Two red vertices in Figure \ref{fig:example} (b) optimally cover the whole polygon, but this covering is not optimal w.r.t.
+discrete set $D(P)$, since the total sum of weights is larger (1.6).
 
@@
         	\includegraphics[height=1.7in]{slika1b.eps}
-        	\caption{Optimal coverage of polygon $P$}
+        	\caption{Optimal coverage of polygon $P$.}
     	\end{subfigure}
@@
 	The chosen resolution  $\bigtriangleup_{x}\times\bigtriangleup_{y}$ is a compromise between the algorithm speed and accuracy.
-More precisely,  higher resolution increases the accuracy, but also the execution time and vice versa, lower resolution decreases the algorithm accuracy, but discretization is  made faster.
+More precisely,  higher resolution increases the accuracy, but also the execution time and vice versa, lower resolution decreases the algorithm accuracy, but discretization is  generated faster.
 
@@
 	\begin{equation}
-	\bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1,
+	\bigvee_{ j=1}^n (a_{ij} \wedge x_j) = 1, \forall p_i \in D(P),
 	\end{equation}
@@
 	\section{Algorithmic Approaches for solving WOAGP}
-	In this section we present the heuristic greedy approaches for solving WOAGP and their hybridization with the exact ILP method. 
+	In this section we present the heuristic greedy approaches for solving WOAGP\fxnote{treba li ovdej w.r.t. regulagrid discrtization?} and their hybridization with the exact ILP method. 
 	\subsection{Greedy approaches for solving WOAGP}
@@
 The greedy function w.r.t.
-partial solution $s^{ps}$ and  guard $v$ is defined as follows.
+partial solution $s^{ps}$ and candidate guard $v$ is defined as follows.
 	\begin{equation}\label{eq:greedyfun2}
@@
 instance size due to the complexity of the problem.
-On the other hand, in the later stage, there is an increased chance for Greedy to worsen the obtained greedy solution.
+On the other hand, in the later stage, there is an increased chance for Greedy to worsen the obtained greedy solution due to an increased number of guards which are similar w.r.t.
+greedy value.
 So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few iterations  and only then to make use the \textsc{Cplex} to do the completion of the partial solution.
@@
 
- We used two different kind of benchmark sets from~\cite{tomas2006visibility}\fxnote{ima jos jedna referenca Partitioning Orthogonal Polygons by Extension
-of All Edges Incident to Reflex Vertices}:
+ We used two different kind of benchmark sets from~\cite{tomas2006visibility,bajuelos2004partitioning}: 
      \begin{itemize}
@@
 a specific kind of instances and a specific weight (97 instances per each group).
-Each of the tables list the considered algorithms in the first column.
+Each of the tables list the tested algorithms in the first column.
 Starting with column two,  each of the lines provide detailed statistics for respective algorithm.
 The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t.
-optimal solutions ($\sigma(Opt)$), then the number of minimal solutions w.r.t.
+optimal solutions ($\sigma(Opt)$), then the number of minimal solutions the algorithm obtained w.r.t.
 the four heuristics achieved by the respective algorithm (\#hitsMinH) and average standard deviation w.r.t.
@@
      \begin{itemize}
-     	\item  In case of the instances that include small--area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
+     	\item  In case of the instances that include small--area polygons ($MinArea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
 In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods.
@@
      	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
-Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
-As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation w.r.t.
+Note that in 81 cases (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
+As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but the obtained  average standard deviation w.r.t.
 optimal solutions is rather small.
@@
 These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime.
-The result of \textsc{Greedy-1} match just in two cases to the optimum.
+The results of \textsc{Greedy-1} match just in two cases to the optimum.
 
@@
 solution quality is \textsc{Greedy-2 +Cplex}.
-It also matches in the most cases (on 6 instances) to the optimum results w.r.t.
-other heuristic approaches.
-Its average results are within 22\% of the average of  optimal solutions.
+It also matches in more cases (on 6 instances) to the optimum result then the other heuristic approaches.
+The obtained average results are within 22\% of the average of  optimal solutions.
 The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}.
-It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}.
+It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in solutions when compared to the average number of guards of \textsc{Greedy-2}.
 The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach.
 Reason for that can be seen in the used regular discretization of the polygon.
-For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
+For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{MinArea} polygons).
      	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
@@
 Again, average standard deviation for each heuristic method is rather small w.r.t.
-optimal solutions, indicating the good quality of the proposed algorithms.
+optimal solutions, indicating good quality of the proposed algorithms.
      	\item  Concerning the percentage of covering of polygons for the best solutions (found by \textsc{Cplex}) we
      	noticed that  \textsc{FAT} instances are covered in almost all cases (see Fig.\ref{fig:covw0} and \ref{fig:covw1} and the blue curve).
-Concerning the \textit{Smallarea} instances, it gets harder to cover all polygon and in allmost all cases the whole area of polygon $P$ cannot be covered.
+Concerning the \textit{MinArea} instances, it gets harder to cover all polygon and in allmost all cases the whole area of polygon $P$ cannot be covered.
 For these instances, we see that the solutions cover more regions of small--area polygons when weight $W1$ is considered then when considering $W0$ ($\approx 93 \%$ vs.
@@
 	  In this work we have considered the Weighted Orthogonal Art Gallery Problem under regular grid discretization.
-	  We have developed a novel greedy rule which provide a trade-off between the number of guards and the cost of  guards.
+	  We have developed a novel greedy criterion which provide a trade-off between the number of guards and the cost of  guards.
 Moreover, a hybrid of a greedy method and \textsc{Cplex} was proposed to make a maximal completion of the greedy solution obtained by the greedy method supplemented by solving respective subproblem via \textsc{Cplex}.
@@
 From the computational experiments, the heuristic approaches were highly efficient in terms of obtaining solutions of reasonable quality in an order of magnitude lower runtime than the exact approaches for the small-area polygons.
-For the large--area polygons, heuristic approaches were able to reach the quality of optimal solutions in almost all cases but in cost of larger times than the ILP approach.
+For the large--area polygons, heuristic approaches were able to reach the quality of optimal solutions in almost all cases but in cost of larger times than the times of the ILP approach.
 

### 2020-10-13 doc/paper.tex
sitne izmjene i dodata jedna referenca

@@
 	\section{Algorithmic Approaches for solving WOAGP}
-	In this section we present the heuristic greedy approaches for solving WOAGP\fxnote{treba li ovdej w.r.t. regulagrid discrtization?} and their hybridization with the exact ILP method. 
+	In this section we present the heuristic greedy approaches for solving the considered problem and their hybridization with the exact ILP method.
 	\subsection{Greedy approaches for solving WOAGP}
@@
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following criterion:
+	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristics was based on the following criterion:
 	\begin{align}\label{eq:Lovasz}
-	g_1(s^{ps}, v_i) = \frac{w_{i}}{ f(s^{ps} \cup \{v_i\})  - f(s^{ps})},
+	g_1(s^{ps}, v_i) = \frac{w_{i}}{ h(s^{ps} \cup \{v_i\})  -h(s^{ps})},
 	\end{align}
@@
 \begin{equation}\label{eq:sp}
-    f(s^{ps}) = \left|\bigcup_{v_i \in s^{ps}} S_i \right|.
+    h(s^{ps}) = \left|\bigcup_{v_i \in s^{ps}} S_i \right|.
     \end{equation}
@@
  \begin{equation}\label{eq:incorrect}
- incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps}),
+ incorrect_{total}(s^{ps}) = |D(P)|-h(s^{ps}),
  \end{equation}
 
- where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set.
+ where $h(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set.
 Let $w_{total}$ be the total sum of all weights among all vertices.
@@
 		\end{itemize}
-		\item Return $f(\overline s)$.
+		\item Return $obj(\overline s)$.
 	\end{enumerate}
@@
 In overall, we have 194 instances.
-Discretization is performed by using \fxnote{nismo nigdje ubacili, a ovdje bi trebalo CGAL}.
+Discretization is performed by using CGAL \cite{cgal:eb-20b}.
 
@@
 a higher price.
-		\item \emph{point-based related weights} ($W1$): For each vertex $v_j$, based on the number of points in $D(P)$ that are visible from $v_j$, we assign prices to each vertex on the following way:
+		\item \emph{point-based related weights} ($W1$): For each vertex $v_i$, based on the number of points in $D(P)$ that are visible from $v_i$, we assign prices to each vertex on the following way:
 		\begin{equation}
@@
         \begin{itemize}
-        	\item  exact approaches: CP and ILP approach. The later is, henceforth, called \textsc{Cplex};
+        	\item  exact approaches: CP and ILP approach. The latter is, henceforth, called \textsc{Cplex};
             \item 4 heuristic approaches:
@@
 Starting with column two,  each of the lines provide detailed statistics for respective algorithm.
-The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t.
+The statistics report: the average solution quality ($\overline{obj}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t.
 optimal solutions ($\sigma(Opt)$), then the number of minimal solutions the algorithm obtained w.r.t.
@@
      	\begin{tabular}{l|lllllll}    \hline
-     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
@@
       	\begin{tabular}{l|lllllll} \hline
-      		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+      		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
       		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
@@
      	\begin{tabular}{l|lllllll} \hline
-     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
@@
  	  \begin{tabular}{l|lllllll} \hline
- 		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+ 		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & \#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
  		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
@@
         	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
-        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
+        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of \textsc{Cp} degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
         \end{itemize}
@@
      	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones.
-Note that in 81 cases (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
+Note that in 81 cases (out of 97) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches.
 As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but the obtained  average standard deviation w.r.t.
@@
 Development, Higher Education and Information Society, Government
-of Republic of Srpska, B\&H under the Project \fxnote{ime projekta}.
+of Republic of Srpska, B\&H under the Project ``Development of artificial intelligence methods for solving computer biology problems".
 

### 2020-10-13 doc/paper.tex
some fix and fxnote added

@@
      \begin{itemize}
-     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas and tiny interior.
+     	 \item \emph{MinArea} instances: include polygons with a small areas and tiny interior.
 They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
-     	 \item \emph{FAT} instances:  includes polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
+     	 \item \emph{FAT} instances:  include polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
      \end{itemize}
@@
 In overall, we have 194 instances.
-Discretization is performed by using CGAL \cite{cgal:eb-20b}.
+Discretization is performed by using CGAL \cite{cgal:eb-20b} \fxnote{verzija CGAL-a dodati}.
 
@@
      	\begin{tabular}{l|lllllll}    \hline
-     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		\textit{Algorithm}           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
@@
       	\begin{tabular}{l|lllllll} \hline
-      		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+      		\textit{Algorithm}           & $\overline{obj}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
       		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
@@
       	\end{tabular}}
-         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
+         \caption{The results on the benchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
       \end{table}
@@
      	\begin{tabular}{l|lllllll} \hline
-     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+     		\textit{Algorithm}           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
@@
  	  \begin{tabular}{l|lllllll} \hline
- 		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & \#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
+ 		\textit{Algorithm}           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & \#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
  		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
@@
     	\includegraphics[width=\textwidth]{grafikon3.eps}}
-    	\caption{Avg. execution time of the compared algorithms.}
+    	\caption{Avg. execution time of the compared algorithms. \fxnote{ujednacinit font teksta u legendi sa fontom u tekstu, dodati $[s]$ na $y$ osi, nigdje ne referenciramo ovu sliku...}}
     	\label{fig:timealg}

### 2020-10-14 doc/paper.tex
new changes

@@
 	The chosen resolution  $\bigtriangleup_{x}\times\bigtriangleup_{y}$ is a compromise between the algorithm speed and accuracy.
-More precisely,  higher resolution increases the accuracy, but also the execution time and vice versa, lower resolution decreases the algorithm accuracy, but discretization is  generated faster.
+More precisely,  higher resolution increases the accuracy, but also increases the execution time of Algorithm~\ref{alg:discret} and vice versa, lower resolution decreases the accuracy, but discretization is  generated faster.
 
@@
 	\section{Exact methods}
-	In this section we present the exact ILP  initially developed for MWSCP from ~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
+	In this section we present the exact ILP,  initially developed for MWSCP from ~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
 	\subsection{Integer linear programming model}
@@
 
- We used two different kind of benchmark sets from~\cite{tomas2006visibility,bajuelos2004partitioning}:
+ We used two different kind of benchmark sets from~\cite{bajuelos2004partitioning,tomas2006visibility}:
      \begin{itemize}
-     	 \item \emph{MinArea} instances: include polygons with a small areas and tiny interior.
+     	 \item \emph{MinArea} instances: include polygons with small areas and tiny interior.
 They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
@@
 In overall, we have 194 instances.
-Discretization is performed by using CGAL \cite{cgal:eb-20b} \fxnote{verzija CGAL-a dodati}.
+Discretization is performed by using CGAL library, version 5.0.2~\cite{cgal:eb-20b}.
 
-	We included two kind of weights into each of 194  instances:
+	We included two kinds of weights into each of 194  instances:
 	\begin{itemize}
-		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$.
-Then, we set
-\begin{equation}
-w_i := \frac{l_i + l_{i+1}}{2}.
- \end{equation}
- This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
-This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,.
-a higher price.
-		\item \emph{point-based related weights} ($W1$): For each vertex $v_i$, based on the number of points in $D(P)$ that are visible from $v_i$, we assign prices to each vertex on the following way:
+		\item \emph{point-based related weights} ($W0$): For each vertex $v_i$,  the assignment of prices is based on the number of points in $D(P)$ that are visible from $v_i$, as follows:
 		\begin{equation}
@@
 		\end{equation}
-    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher spectrum and quality, and thus are more expensive.
+    This approach can be justified by the assumption that cameras which cover larger range of points should be of a higher spectrum and quality, and thus more expensive.
+		\item \emph{topologically-based related weights} ($W1$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$ (note that indices are taken modulo $n$).
+Then, we set
+\begin{equation}
+w_i = \frac{l_i + l_{i+1}}{2}.
+ \end{equation}
+ Similarly as in the case of $W0$, if the arithmetic length of both edges that comes out of vertex $v_i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$.
+This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,.
+a higher price.
+
 	\end{itemize}
@@
      \subsection{Settings and the choice of the Parameters}
-      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB.
+      All variants of our algorithms were implemented in C++ with g++~7.4 compiler and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB.
 The maximum computation time of each of our algorithms was set to $5\ min$.
+For solving ILP and CP models, \textsc{Cplex} version 12.7 was used.
 
@@
 
-     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}. \fxnote{dodati link}
+     The benchmark sets and the executable file of our software for this project are provided at public git repository, available on \href{https://github.com/milanagrbic/WOAGP}{https://github.com/milanagrbic/WOAGP}
 	\subsection{Results and Discussion}
@@
         	\item  exact approaches: CP and ILP approach. The latter is, henceforth, called \textsc{Cplex};
-            \item 4 heuristic approaches:
+            \item four heuristic approaches:
            \begin{itemize}
@@
      \begin{itemize}
-     	\item  In case of the instances that include small--area polygons ($MinArea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature.
+     	\item  In case of the instances that include small--area polygons ($MinArea$) and weight $W0$ (Table~\ref{small_wo}): A novel \textsc{Greedy-2} was able to  outperform the \textsc{Greedy-1} from literature.
 In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods.
@@
 Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}.
+The overall average execution times of all tested algorithms are displayed in Figure \ref{fig:timealg}.
+Note that vertical axis is scaled logarithmically.
 Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t.
@@
     	\includegraphics[width=\textwidth]{grafikon3.eps}}
-    	\caption{Avg. execution time of the compared algorithms. \fxnote{ujednacinit font teksta u legendi sa fontom u tekstu, dodati $[s]$ na $y$ osi, nigdje ne referenciramo ovu sliku...}}
+    	\caption{Avg. execution time of the compared algorithms.}
     	\label{fig:timealg}
@@
 
-	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets by considering different discretizations of polygons, for example, the Delaunay triangulation~\cite{lee1980two}.
+	  For the future work, we tend to improve the results of our greedy method as well as runtimes on the $FAT$ benchmark sets by considering other types of polygon discretisations.
 

### 2020-10-14 doc/paper.tex
final changes made by Marko

@@
 This new approach and an existing greedy algorithm are further  hybridized with the Integer Linear programming (ILP), originally formulated for the well known Minimum Set Cover problem.
-Experimental results show that the proposed greedy methods can achieve most of the optimal solution for a class of large area polygons, while for small area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
+Experimental results show that the proposed greedy methods is able to achieve the optimal solutions in most cases for a class of large area polygons, while for small area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
 	\end{abstract}
@@
 This restricted problem is known to be $\mathcal{NP}$--hard~\cite{schuchardt1995two,katz2008guarding}.
-When it comes to the real situations (like installing the cameras in a building), it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting its range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
-In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP) the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
-In this paper we consider WOAGP problem under the regular grid discretization of $P$, described in Subsection~\ref{sec:regulardiscretization}.
+When it comes to real situations (like installing the cameras in a building), it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting its range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
+In the \emph{Weighted Orthogonal Art Gallery Problem} (WOAGP) the task is to place guards on some vertices of orthogonal polygon $P$ which cover all points from $P$, such that the total sum of prices assigned to the chosen vertices is minimal.
+In this paper we consider WOAGP problem under the regular grid discretization of $P$, described in Section~\ref{sec:regulardiscretization}.
 
-	It is well known that AGP can be reduced to \emph{the Minimum Set Cover Problem} (MSCP) by a discretization of the set of all points of the polygon $P$.
+	It is well known that AGP can be reduced to \emph{the Minimum Set Cover Problem} (MSCP) by a discretization of the set of all points of polygon $P$.
 The appropriate discretization should be performed in such a way that if each point from the discretized set $D(P)$ is covered, then the whole polygon $P$ is covered.
@@
 
-	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance.
-In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the the solution is at most $O(\log n)$ times the optimal one.
-After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the MSCP is applied.
-An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in~\cite{tomas2003approximation}.
-A major idea of this approach is exploring dominance of visibility regions to first detect pieces that are
+	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the discretized instance.
+In~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and this solution is at most $O(\log n)$ times the optimal one.
+After that, on these constructed sets Johnson’s approximation algorithm~\cite{johnson1974approximation} for the MSCP is applied.
+An anytime algorithm to compute successively better approximations of the optimum for Minimum Vertex Guard is proposed in~\cite{tomas2003approximation}.
+A major idea of this approach is exploring dominance of visibility regions to first detect pieces of the polygon that are
 	more difficult to guard. The same problem is solved in~\cite{tomas2006visibility} by applying successive approximations from ~\cite{tomas2003approximation}.
@@
 A comprehensive analysis of various greedy-like heuristics for the MWSCP  was presented in \cite{vasko2016best}.
-	More detailed overview of the extensive literature regarding MSCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
+	More detailed overview of the extensive literature regarding MSCP and AGP is out of the scope of this paper and for further reading we suggest review papers~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.
 
@@
 	\section{Exact methods}
-	In this section we present the exact ILP,  initially developed for MWSCP from ~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
+	In this section we present the exact ILP,  initially developed for MWSCP from~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
 	\subsection{Integer linear programming model}
@@
 	Family $\mathcal{F}$ of nonempty sets consists of the sets
-	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.
+	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$.
 For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.
@@
 
-The ILP  model for the MWSCP ~\cite{vazirani2013approximation}   is  adapted to WOAGP  as follows:
+The ILP  model for the MWSCP~\cite{vazirani2013approximation}   is  adapted to WOAGP  as follows:
 
@@
 	Set $Z = \{v_j \in V\mid x_j=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
-	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.
+	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ is visible from at least one guard from $Z$.
 
@@
 	\section{Algorithmic Approaches for solving WOAGP}
-	In this section we present the heuristic greedy approaches for solving the considered problem and their hybridization with the exact ILP method.
+	In this section we present the heuristic greedy approaches for solving the WOAGP and their hybridization with the exact ILP method.
 	\subsection{Greedy approaches for solving WOAGP}
  Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement.
-Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one.
+Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution up to its completion.
 In order to extend current partial solution, among all candidates (solution components for expansion, that is not-yet-considered guards),  we choose one with the smallest greedy value and add it to the current solution.
-This procedure is repeating until the current solution becomes complete (i.e., all points from $D(P)$ are covered).
+This procedure keeps repeating until the current solution becomes complete (i.e., all points from $D(P)$ are covered).
 
@@
 	%  \subsection{Greedy Criterion based on Price-per-Unit}
-	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristics was based on the following criterion:
+	Concerning the greedy heuristic from the literature for solving MWSCP~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristics was based on the following criterion:
 	\begin{align}\label{eq:Lovasz}
@@
 
-	In the Equation  (\ref{eq:greedyfun2}) both terms are normalized on order to achieve better balance between the total sum of guards' costs and the total number of not yet covered points from the discretization.
+	In the Equation  (\ref{eq:greedyfun2}) both terms are normalized in order to achieve better balance between the total sum of guards' costs and the total number of not yet covered points from the discretization.
 The algorithm does not  ultimately prefer any of criteria for choosing next vertex.
@@
 At the beginning, more points are uncovered and the algorithm  chooses such vertices which cover larger area of the polygon.
-At the end of algorithm, it could be expected that the first term plays more significant role, since the total number of uncovered points is small.
+At the ending stage of the algorithm's execution, it could be expected that the first term plays more significant role, since the total number of uncovered points is small.
 
@@
 	In order to enable fast calculation of greedy functions described in previous subsections, we noticed that it could be useful to allow fast updating of the number of uncovered vertices.
-Therefore, we introduced two useful structures: %and two auxiliary functions:
+Therefore, we introduced two useful structures in our calculations: %and two auxiliary functions:
 	\begin{itemize}
@@
 	\begin{enumerate}
-		\item Run a Greedy method up to $K$ iterations  to obtain a partial solution $s^{ps}$, where $K$ is a parameter of the algorithm.
+		\item Run a Greedy method up to $K$ iterations  to obtain a partial solution $s^{ps}$, where $K$ is a parameter of the algorithm;
 		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via \textsc{Cplex}:
@@
 		\end{itemize}
-		\item Return $obj(\overline s)$.
+		\item Return $obj(\overline s)= |\overline{s}|$.
 	\end{enumerate}
@@
      	 \item \emph{MinArea} instances: include polygons with small areas and tiny interior.
-They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
+They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains only a few additional points.
      	 \item \emph{FAT} instances:  include polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
@@
 		\end{equation}
-    This approach can be justified by the assumption that cameras which cover larger range of points should be of a higher spectrum and quality, and thus more expensive.
+    Introducing these weights can be justified by the assumption that cameras which cover larger range of points should be of a higher spectrum and quality, and thus more expensive.
 		\item \emph{topologically-based related weights} ($W1$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$ (note that indices are taken modulo $n$).
@@
 
-     The benchmark sets and the executable file of our software for this project are provided at public git repository, available on \href{https://github.com/milanagrbic/WOAGP}{https://github.com/milanagrbic/WOAGP}
+     The benchmark sets and the executable file of our software for this project are provided at a public git repository, available on \href{https://github.com/milanagrbic/WOAGP}{https://github.com/milanagrbic/WOAGP}
 	\subsection{Results and Discussion}
@@
 
-         Summarized numerical results for each of our 6 variants of our algorithm are displayed
+         Summarized numerical results for each of 6 variants of our algorithms are displayed
          in Tables~\ref{small_wo} -- \ref{large_w1}.
@@
         	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
-        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
+        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required for \textsc{Cplex};
         	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of \textsc{Cp} degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
@@
 Note that vertical axis is scaled logarithmically.
-Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t.
+Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristic), the average standard deviation w.r.t.
 optimal solution is rather small.
@@
      	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}.
-These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime.
+These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times lower runtime.
 The results of \textsc{Greedy-1} match just in two cases to the optimum.
@@
 For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{MinArea} polygons).
-     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t.
+     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithm w.r.t.
 solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions.
@@
      	\item  Concerning the percentage of covering of polygons for the best solutions (found by \textsc{Cplex}) we
-     	noticed that  \textsc{FAT} instances are covered in almost all cases (see Fig.\ref{fig:covw0} and \ref{fig:covw1} and the blue curve).
+     	noticed that  \textsc{FAT} instances are covered in almost all cases (see Fig.~\ref{fig:covw0} and \ref{fig:covw1} and the blue curve).
 Concerning the \textit{MinArea} instances, it gets harder to cover all polygon and in allmost all cases the whole area of polygon $P$ cannot be covered.
@@
 $\approx 85\%$).
-It can be argued by the fact that in weight $W0$ there exists many ties for weights of guards, and, therefore, more solutions with the minimum weight exist.
-     	Notice that this is not so often the case of the weight $W1$.
+%It can be argued by the fact that in weight $W0$ there exists many ties for weights of guards, and, therefore, more solutions with the minimum weight exist.
+     	%Notice that this is not so often the case of the weight $W1$.
 

### 2020-10-15 doc/paper.tex
popravljene još neke sitnice

@@
 In the course of this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$.
-This restricted problem is known to be $\mathcal{NP}$--hard~\cite{schuchardt1995two,katz2008guarding}.
+This restricted problem is known to be $\mathcal{NP}$--hard~\cite{katz2008guarding,schuchardt1995two}.
 When it comes to real situations (like installing the cameras in a building), it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting its range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).
@@
 
-	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the discretized instance.
+	Concerning the exact and heuristic techniques to solve OAGP, Couto et al.~\cite{couto2007exact} presented an exact and efficient algorithm for the OAGP based on preprocessing and refinement phases of the discretized instance.
 In~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and this solution is at most $O(\log n)$ times the optimal one.
@@
 an optimal covering of $D(P)$) is not necessarily  an optimal covering of $P$.
-In the simple example shown in Figure \ref{fig:example}, one can see that the guards placed on top left and top right vertices (shown in red color) cover all points from $D(P)$ (Figure \ref{fig:example} (a)), but not the whole polygon, since the gray triangle is not visible from any of these two points.
+In the simple example shown in Figure \ref{fig:example}, one can see that the guards placed on top left and top right vertices (shown in red color) cover all points from $D(P)$ (Figure \ref{fig:example} (a)), but not the whole polygon, since the gray triangle is not visible from any of these two vertices.
 The optimal solution value in this case is 1.2.
@@
 	\subsection{Integer linear programming model}
-	Let us suppose we are given a polygon $P$ and the discretization $D(P)$ of $P$.
+	Let us suppose we are given a polygon $P$ with weights assigned to vertices and the discretization $D(P)$ of $P$.
 The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
@@
   When $v$ is removed from partial solution, we update current \texttt{CoveredPoints} and \texttt{numberOfGuards} by omitting all points which are covered only by $v$.
-These two functions allow also a fast calculation of  functions (\ref{eq:sp}) and  (\ref{eq:incorrect}): a candidate vertex $v$ is temporary added to the partial solution, new status is checked and then being removed from the solution.
+These two functions allow also a fast calculation of  functions (\ref{eq:sp}) and  (\ref{eq:incorrect}): a candidate vertex $v$ is temporarily added to the partial solution, new status is checked and then being removed from the solution.
 
@@
 \begin{equation}
-w_i = \frac{l_i + l_{i+1}}{2}.
+w_i = \frac{l_i + l_{i+1}}{2} ,\ i=1,...,n.
  \end{equation}

### 2020-10-15 doc/paper.tex
Mićkove popravke

@@
 			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
-			\State $D(P) \gets D(BB) \cap P;$
+			\State $D(P) \gets D(BB) \cap interior(P);$
 			\State $D(P) \gets D(P) \cup V;$
@@
 	\end{algorithm}
-The algorithm further forms the whole regular grid of the bounding box (line 5 of the pseudocode) and finally, all points of the regular grid that belong to $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
+The algorithm further forms the whole regular grid of the bounding box (line 5 of the pseudocode) and finally, all points of the regular grid that belong to interior of $P$ and all vertices of $P$ are added into the discrete set $D(P)$.
 
@@
 In this way, our starting task is equivalent of finding a  covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$ of minimum weight, that is
-	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that
+	$$ \bigcup_{S \in \mathcal{C}} S = D(P),$$ such that
 
-$$f(\mathcal{C}) = \sum_{S_i \in \mathcal{C}} c(S_i)$$
+$$f(\mathcal{C}) = \sum_{S \in \mathcal{C}} c(S)$$
 
@@
       After conducting preliminary results, for
-        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$.
+        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$ in order to allow less computational time of the hybrid than the average runtime of the pure greedy method.
 

### 2020-10-15 doc/paper.tex
skracen apstrakt

@@
 	\begin{abstract}
-		In this paper we deal with the Weighted Orthogonal Art Gallery Problem under the regular grid discretization.
-We propose a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
-This new approach and an existing greedy algorithm are further  hybridized with the Integer Linear programming (ILP), originally formulated for the well known Minimum Set Cover problem.
-Experimental results show that the proposed greedy methods is able to achieve the optimal solutions in most cases for a class of large area polygons, while for small area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
+This paper considers the Weighted Orthogonal Art Gallery Problem under regular grid discretization.
+We propose a novel greedy approach, based on balancing the trade-off between the total sum of guards' costs and the number of not-yet-covered points.
+This approach is hybridized with existing ILP.
+Experimental results show that the methods can achieve optimal solutions in most cases for a class of large-area polygons.
+For small-area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
 	\end{abstract}
